\section{AEROSPACE ENGINEERING}

\textbf{Q1} Which flight instrument is used to determine an aircraft's attitude in flight?\par
\quad - a) Vertical Speed Indicator\par
\quad - b) Altimeter\par
\quad - c) Artificial Horizon\par

\textbf{Q2} What is the purpose of camber in an airfoil?\par
\quad - a) To reduce drag\par
\quad - b) To increase lift\par
\quad - c) To improve stability\par

\textbf{Q3} What type of aircraft configuration features a small forewing in front of the main wing?\par
\quad - a) Canard\par
\quad - b) Conventional\par
\quad - c) Delta\par

\textbf{Q4} Which control surface is used to control the pitch of an aircraft?\par
\quad - a) Ailerons\par
\quad - b) Elevators\par
\quad - c) Rudder\par

\textbf{Q5} What is the effect of increasing camber on an airfoil's lift coefficient?\par
\quad - a) It decreases the lift coefficient\par
\quad - b) It has no effect on the lift coefficient\par
\quad - c) It increases the lift coefficient\par

\textbf{Q6} Which type of engine is more efficient at high altitudes?\par
\quad - a) Propeller Engine\par
\quad - b) Jet Engine\par
\quad - c) Rocket Engine\par

\textbf{Q7} What is the term for the motion of an aircraft around its vertical axis?\par
\quad - a) Pitch\par
\quad - b) Roll\par
\quad - c) Yaw\par

\textbf{Q8} Which of the following statements is true about supersonic flight?\par
\quad - a) Airplanes experience less stability in pitch at supersonic speeds\par
\quad - b) Airplanes experience more stability in pitch at supersonic speeds\par
\quad - c) Pitch stability remains unchanged\par

\textbf{Q9} What is the primary force acting downward on an aircraft in flight?\par
\quad - a) Lift\par
\quad - b) Weight\par
\quad - c) Drag\par

\textbf{Q10} Which type of aircraft requires the longest runway for takeoff?\par
\quad - a) Glider\par
\quad - b) Propeller Aircraft\par
\quad - c) Jet Aircraft\par

\textbf{Q11} What is the purpose of a winglet on an aircraft?\par
\quad - a) To reduce drag\par
\quad - b) To increase lift\par
\quad - c) To improve stability\par

\textbf{Q12} Which of the following is a favorable wind condition for aircraft operation?\par
\quad - a) Tailwind in cruise and headwind in landing\par
\quad - b) Headwind in cruise and tailwind in landing\par
\quad - c) Headwind both in cruise and landing\par

\textbf{Q13} What is the term for the oscillatory motion of an aircraft in the longitudinal axis?\par
\quad - a) Phugoid Mode\par
\quad - b) Dutch Roll\par
\quad - c) Spiral Mode\par

\textbf{Q14} Which material is commonly used in aircraft structures due to its high strength-to-weight ratio?\par
\quad - a) Aluminum\par
\quad - b) Titanium\par
\quad - c) Carbon Fiber\par

\textbf{Q15} What is the term for the study of the motion of objects in space?\par
\quad - a) Astrodynamics\par
\quad - b) Aerodynamics\par
\quad - c) Hydrodynamics\par

\textbf{Q16} Which type of propulsion system uses a combination of electric motors and propellers?\par
\quad - a) Hybrid Electric\par
\quad - b) Turbojet\par
\quad - c) Rocket\par

\textbf{Q17} What is the purpose of a thrust vectoring system in an aircraft?\par
\quad - a) To improve maneuverability\par
\quad - b) To increase thrust\par
\quad - c) To reduce drag\par

\textbf{Q18} Which of the following is a type of aircraft control surface?\par
\quad - a) Flaps\par
\quad - b) Spoilers\par
\quad - c) Both a and b\par

\textbf{Q19} What is the term for the angle between the wing and the oncoming airflow?\par
\quad - a) Angle of Attack\par
\quad - b) Angle of Incidence\par
\quad - c) Cambered Surface\par

\textbf{Q20} Which type of aircraft is designed for vertical takeoff and landing?\par
\quad - a) Helicopter\par
\quad - b) VTOL Aircraft\par
\quad - c) Both a and b\par

\textbf{Q21} What is the primary function of ailerons on an aircraft?\par
\quad - a) To control roll\par
\quad - b) To control pitch\par
\quad - c) To control yaw\par

\textbf{Q22} Which of the following statements is true about the phugoid mode of an aircraft?\par
\quad - a) Frequency is directly proportional to flight speed\par
\quad - b) Frequency is inversely proportional to flight speed\par
\quad - c) Frequency is independent of flight speed\par

\textbf{Q23} What is the term for the study of the interaction between aircraft and the atmosphere?\par
\quad - a) Aerodynamics\par
\quad - b) Hydrodynamics\par
\quad - c) Thermodynamics\par

\textbf{Q24} Which type of engine is commonly used in spacecraft?\par
\quad - a) Rocket Engine\par
\quad - b) Jet Engine\par
\quad - c) Propeller Engine\par

\textbf{Q25} What is the purpose of a heat shield on a spacecraft?\par
\quad - a) To protect against extreme temperatures during re-entry\par
\quad - b) To improve propulsion efficiency\par
\quad - c) To enhance communication systems\par

\textbf{Q26} Which of the following is a type of aircraft stability?\par
\quad - a) Static Stability\par
\quad - b) Dynamic Stability\par
\quad - c) Both a and b\par

\textbf{Q27} What is the term for the motion of an aircraft around its longitudinal axis?\par
\quad - a) Roll\par
\quad - b) Pitch\par
\quad - c) Yaw\par

\textbf{Q28} Which type of material is used in rocket nozzles due to its high heat resistance?\par
\quad - a) Titanium\par
\quad - b) Ceramic\par
\quad - c) Carbon Fiber\par

\textbf{Q29} What is the purpose of a pitot tube on an aircraft?\par
\quad - a) To measure airspeed\par
\quad - b) To measure altitude\par
\quad - c) To measure temperature\par

\textbf{Q30} Which of the following is a type of aircraft navigation system?\par
\quad - a) GPS\par
\quad - b) INS\par
\quad - c) Both a and b\par

\textbf{Q31} What is the term for the study of the design and operation of spacecraft?\par
\quad - a) Space Technology\par
\quad - b) Aerospace Engineering\par
\quad - c) Astronautics\par

\textbf{Q32} Which type of propulsion system uses a combination of fuel and oxidizer?\par
\quad - a) Liquid-Fueled Rocket\par
\quad - b) Solid-Fueled Rocket\par
\quad - c) Hybrid Rocket\par

\textbf{Q33} What is the purpose of a spoiler on an aircraft?\par
\quad - a) To reduce lift\par
\quad - b) To increase drag\par
\quad - c) To improve stability\par

\textbf{Q34} Which of the following statements is true about the Dutch roll mode of an aircraft?\par
\quad - a) It involves oscillations in roll and yaw\par
\quad - b) It involves oscillations in pitch and roll\par
\quad - c) It involves oscillations in pitch and yaw\par

\textbf{Q35} What is the term for the angle between the wing's chord line and the oncoming airflow?\par
\quad - a) Angle of Attack\par
\quad - b) Angle of Incidence\par
\quad - c) Cambered Surface\par

\textbf{Q36} Which type of aircraft is designed for supersonic flight?\par
\quad - a) Fighter Jet\par
\quad - b) Commercial Airliner\par
\quad - c) Helicopter\par

\textbf{Q37} What is the primary function of the rudder on an aircraft?\par
\quad - a) To control yaw\par
\quad - b) To control pitch\par
\quad - c) To control roll\par

\textbf{Q38} Which of the following is a type of aircraft control system?\par
\quad - a) Fly-by-Wire\par
\quad - b) Fly-by-Cable\par
\quad - c) Both a and b\par

\textbf{Q39} What is the term for the study of the behavior of fluids in motion?\par
\quad - a) Aerodynamics\par
\quad - b) Hydrodynamics\par
\quad - c) Thermodynamics\par

\textbf{Q40} Which type of engine is commonly used in helicopters?\par
\quad - a) Turboshaft Engine\par
\quad - b) Turbojet Engine\par
\quad - c) Propeller Engine\par

\textbf{Q41} What is the purpose of a vortex generator on an aircraft?\par
\quad - a) To reduce drag\par
\quad - b) To increase lift\par
\quad - c) To improve stability\par

\textbf{Q42} Which of the following statements is true about the spiral mode of an aircraft?\par
\quad - a) It involves a gradual increase in bank angle\par
\quad - b) It involves a gradual decrease in bank angle\par
\quad - c) It involves oscillations in roll and yaw\par

\textbf{Q43} What is the term for the study of the interaction between aircraft and the ground?\par
\quad - a) Aerodynamics\par
\quad - b) Hydrodynamics\par
\quad - c) Ground Effect\par

\textbf{Q44} Which type of material is used in aircraft tires due to its durability?\par
\quad - a) Rubber\par
\quad - b) Kevlar\par
\quad - c) Carbon Fiber\par

\textbf{Q45} What is the purpose of a thrust reverser on an aircraft?\par
\quad - a) To reduce thrust during landing\par
\quad - b) To increase thrust during takeoff\par
\quad - c) To improve maneuverability\par

\textbf{Q46} Which of the following is a type of aircraft navigation aid?\par
\quad - a) VOR\par
\quad - b) ILS\par
\quad - c) Both a and b\par

\textbf{Q47} What is the term for the study of the design and operation of missiles?\par
\quad - a) Ballistics\par
\quad - b) Aerodynamics\par
\quad - c) Aerospace Engineering\par

\textbf{Q48} Which type of propulsion system uses a combination of solar panels and electric motors?\par
\quad - a) Solar-Electric Propulsion\par
\quad - b) Nuclear-Electric Propulsion\par
\quad - c) Hybrid Propulsion\par

\textbf{Q49} What is the purpose of a drogue parachute on an aircraft?\par
\quad - a) To reduce landing speed\par
\quad - b) To increase takeoff speed\par
\quad - c) To improve stability\par

\textbf{Q50} Which of the following statements is true about the effect of wingtip vortices on aircraft performance?\par
\quad - a) They increase drag\par
\quad - b) They reduce drag\par
\quad - c) They have no effect on drag\par