\section{ARTS MIXED BAG THREE}

\textbf{Q1} His full name was Ustad Qamruddin Bismillah Khan, and he was awarded Bharat Ratna. For which instrument did he receive the Bharat Ratna?\par
\quad - a) Tabla\par
\quad - b) Sitar\par
\quad - c) Shehnai\par

\textbf{Q2} What is the river called on the bank of which Varanasi is situated?\par
\quad - a) Ganga\par
\quad - b) Yamuna\par
\quad - c) Brahmaputra\par

\textbf{Q3} Who wrote the book "Anandmath"?\par
\quad - a) Bankim Chandra Chattopadhyay\par
\quad - b) Rabindranath Tagore\par
\quad - c) Sarat Chandra Chattopadhyay\par

\textbf{Q4} What is the folk dance of Punjab?\par
\quad - a) Kathak\par
\quad - b) Bhangra\par
\quad - c) Garba\par

\textbf{Q5} The famous Konark Sun Temple is located in which state?\par
\quad - a) Tamil Nadu\par
\quad - b) Odisha\par
\quad - c) Karnataka\par

\textbf{Q6} Who was the first woman Prime Minister of India?\par
\quad - a) Indira Gandhi\par
\quad - b) Pratibha Patil\par
\quad - c) Sarojini Naidu\par

\textbf{Q7} What is the capital of Rajasthan?\par
\quad - a) Udaipur\par
\quad - b) Jaipur\par
\quad - c) Jodhpur\par

\textbf{Q8} Which Indian city is known as the "City of Pearls"?\par
\quad - a) Mumbai\par
\quad - b) Hyderabad\par
\quad - c) Chennai\par

\textbf{Q9} The Ajanta and Ellora caves are located in which state?\par
\quad - a) Maharashtra\par
\quad - b) Gujarat\par
\quad - c) Madhya Pradesh\par

\textbf{Q10} Who wrote the Indian National Anthem?\par
\quad - a) Mahatma Gandhi\par
\quad - b) Jawaharlal Nehru\par
\quad - c) Rabindranath Tagore\par

\textbf{Q11} What is the name of the largest river in India?\par
\quad - a) Ganga\par
\quad - b) Yamuna\par
\quad - c) Brahmaputra\par

\textbf{Q12} Which Indian state is known as the "Land of Gods"?\par
\quad - a) Kerala\par
\quad - b) Uttarakhand\par
\quad - c) Himachal Pradesh\par

\textbf{Q13} What is the highest civilian award in India?\par
\quad - a) Padma Vibhushan\par
\quad - b) Bharat Ratna\par
\quad - c) Padma Bhushan\par

\textbf{Q14} Who was the first President of India?\par
\quad - a) Jawaharlal Nehru\par
\quad - b) Rajendra Prasad\par
\quad - c) Sardar Patel\par

\textbf{Q15} Which Indian city is known as the "Manchester of India"?\par
\quad - a) Mumbai\par
\quad - b) Ahmedabad\par
\quad - c) Surat\par

\textbf{Q16} The Gateway of India is located in which city?\par
\quad - a) Delhi\par
\quad - b) Mumbai\par
\quad - c) Kolkata\par

\textbf{Q17} What is the name of the longest dam in India?\par
\quad - a) Bhakra Nangal Dam\par
\quad - b) Hirakud Dam\par
\quad - c) Sardar Sarovar Dam\par

\textbf{Q18} Who wrote the book "The Discovery of India"?\par
\quad - a) Mahatma Gandhi\par
\quad - b) Jawaharlal Nehru\par
\quad - c) Sardar Patel\par

\textbf{Q19} Which Indian state is known as the "Land of Rising Sun"?\par
\quad - a) Assam\par
\quad - b) Arunachal Pradesh\par
\quad - c) Meghalaya\par

\textbf{Q20} What is the name of the largest desert in India?\par
\quad - a) Thar Desert\par
\quad - b) Rann of Kutch\par
\quad - c) Ladakh\par

\textbf{Q21} Who was the first Indian to win the Nobel Prize?\par
\quad - a) C.V. Raman\par
\quad - b) Homi J. Bhabha\par
\quad - c) Rabindranath Tagore\par

\textbf{Q22} Which Indian state is known as the "Sugar Bowl of India"?\par
\quad - a) Uttar Pradesh\par
\quad - b) Maharashtra\par
\quad - c) Karnataka\par

\textbf{Q23} What is the name of the largest mosque in India?\par
\quad - a) Jama Masjid\par
\quad - b) Mecca Masjid\par
\quad - c) Taj-ul-Masajid\par

\textbf{Q24} Who was the first Indian woman to go to space?\par
\quad - a) Kalpana Chawla\par
\quad - b) Sunita Williams\par
\quad - c) Sally Ride\par

\textbf{Q25} Which Indian city is known as the "Garden City of India"?\par
\quad - a) Delhi\par
\quad - b) Bangalore\par
\quad - c) Chennai\par

\textbf{Q26} What is the name of the highest waterfall in India?\par
\quad - a) Jog Falls\par
\quad - b) Nohkalikai Falls\par
\quad - c) Dudhsagar Falls\par

\textbf{Q27} Who wrote the book "Gitanjali"?\par
\quad - a) Mahatma Gandhi\par
\quad - b) Jawaharlal Nehru\par
\quad - c) Rabindranath Tagore\par

\textbf{Q28} Which Indian state is known as the "Land of Lakes"?\par
\quad - a) Kerala\par
\quad - b) Jammu and Kashmir\par
\quad - c) Rajasthan\par

\textbf{Q29} What is the name of the largest gurdwara in India?\par
\quad - a) Golden Temple\par
\quad - b) Gurdwara Bangla Sahib\par
\quad - c) Gurdwara Sis Ganj Sahib\par

\textbf{Q30} Who was the first Indian to win an Olympic gold medal in an individual event?\par
\quad - a) Milkha Singh\par
\quad - b) Leander Paes\par
\quad - c) Abhinav Bindra\par

\textbf{Q31} Which Indian city is known as the "Textile City of India"?\par
\quad - a) Mumbai\par
\quad - b) Surat\par
\quad - c) Kolkata\par

\textbf{Q32} What is the name of the largest museum in India?\par
\quad - a) Indian Museum\par
\quad - b) National Museum\par
\quad - c) Chhatrapati Shivaji Maharaj Vastu Sangrahalaya\par

\textbf{Q33} Who wrote the book "Arthashastra"?\par
\quad - a) Kalidasa\par
\quad - b) Chanakya\par
\quad - c) Valmiki\par

\textbf{Q34} Which Indian state is known as the "Land of Temples"?\par
\quad - a) Tamil Nadu\par
\quad - b) Odisha\par
\quad - c) Andhra Pradesh\par

\textbf{Q35} What is the name of the largest church in India?\par
\quad - a) Basilica of Bom Jesus\par
\quad - b) St. Cathedral\par
\quad - c) San Thome Basilica\par

\textbf{Q36} Who was the first Indian to win the Booker Prize?\par
\quad - a) Salman Rushdie\par
\quad - b) Arundhati Roy\par
\quad - c) V.S. Naipaul\par

\textbf{Q37} Which Indian city is known as the "Electronic City of India"?\par
\quad - a) Mumbai\par
\quad - b) Bangalore\par
\quad - c) Hyderabad\par

\textbf{Q38} What is the name of the largest zoo in India?\par
\quad - a) Arignar Anna Zoological Park\par
\quad - b) Nehru Zoological Park\par
\quad - c) Nandankanan Zoological Park\par

\textbf{Q39} Who wrote the book "Mahabharata"?\par
\quad - a) Kalidasa\par
\quad - b) Valmiki\par
\quad - c) Ved Vyasa\par

\textbf{Q40} Which Indian state is known as the "Land of Festivals"?\par
\quad - a) Kerala\par
\quad - b) Nagaland\par
\quad - c) West Bengal\par

\textbf{Q41} What is the name of the largest planetarium in India?\par
\quad - a) Birla Planetarium\par
\quad - b) Nehru Planetarium\par
\quad - c) Science City\par

\textbf{Q42} Who was the first Indian to win the Ramon Magsaysay Award?\par
\quad - a) Vinoba Bhave\par
\quad - b) Mother Teresa\par
\quad - c) Satyajit Ray\par

\textbf{Q43} Which Indian city is known as the "Diamond City of India"?\par
\quad - a) Mumbai\par
\quad - b) Surat\par
\quad - c) Kolkata\par

\textbf{Q44} What is the name of the largest cave temple in India?\par
\quad - a) Ajanta Caves\par
\quad - b) Ellora Caves\par
\quad - c) Elephanta Caves\par

\textbf{Q45} Who wrote the book "Ramayana"?\par
\quad - a) Kalidasa\par
\quad - b) Valmiki\par
\quad - c) Ved Vyasa\par

\textbf{Q46} Which Indian state is known as the "Land of Spices"?\par
\quad - a) Kerala\par
\quad - b) Karnataka\par
\quad - c) Goa\par

\textbf{Q47} What is the name of the largest suspension bridge in India?\par
\quad - a) Howrah Bridge\par
\quad - b) Rajiv Gandhi Sea Link\par
\quad - c) Vidyasagar Setu\par

\textbf{Q48} Who was the first Indian to win the Grammy Award?\par
\quad - a) Ravi Shankar\par
\quad - b) Zakir Hussain\par
\quad - c) A.R. Rahman\par

\textbf{Q49} Which Indian city is known as the "Pensioner's Paradise"?\par
\quad - a) Pune\par
\quad - b) Bangalore\par
\quad - c) Chennai\par

\textbf{Q50} What is the name of the largest wildlife sanctuary in India?\par
\quad - a) Jim Corbett National Park\par
\quad - b) Ranthambore National Park\par
\quad - c) Great Indian Bustard Sanctuary\par