\section{ARTS MIXED BAG ONE}

\textbf{Q1} Manoj Night Shyamalan's directorial debut involved him starring in his own venture. What was the title of this early film project?\par
\quad - a) The Sixth Sense\par
\quad - b) Praying with Anger\par
\quad - c) Signs\par

\textbf{Q2} The Nilgiri Biosphere Reserve, India's first international biosphere reserve, spans across which states?\par
\quad - a) Kerala, Tamil Nadu, Karnataka\par
\quad - b) Andhra Pradesh, Telangana, Odisha\par
\quad - c) Maharashtra, Gujarat, Rajasthan\par

\textbf{Q3} Before becoming a global cycle manufacturer, Hero Cycles started its operations in Ludhiana. What was the company's initial focus?\par
\quad - a) Manufacturing auto parts\par
\quad - b) Distributing bicycles\par
\quad - c) Producing steel components\par

\textbf{Q4} Mukurthi National Park, protecting the Nilgiri Tahr, is renowned for its unique ecosystem. What type of forest dominates this national park?\par
\quad - a) Tropical rainforest\par
\quad - b) Montane grasslands and shrublands\par
\quad - c) Mangrove forest\par

\textbf{Q5} Zatalli, who faced a death sentence for criticising Emperor Farukhsiyar, was known for his mastery over several languages. Besides Hindi, which other languages did he excel in?\par
\quad - a) Sanskrit and Urdu\par
\quad - b) Persian and Rekhta\par
\quad - c) Arabic and Turkish\par

\textbf{Q6} Jahanara Begum, daughter of Shah Jahan, played a significant role in Delhi's architecture. Besides Chandni Chowk, what other major project is she credited with?\par
\quad - a) Red Fort's interior design\par
\quad - b) Jama Masjid's construction\par
\quad - c) Restoration of Agra Fort\par

\textbf{Q7} Mirza Abdul Qadir, better known as Bedil, is remembered for his unique style of poetry. What is the defining characteristic of the "Sabk‑e‑Hindi" school he mastered?\par
\quad - a) Simple and straightforward language\par
\quad - b) Complex metaphors and philosophical depth\par
\quad - c) Romantic and lyrical themes\par

\textbf{Q8} Jeet Thayil's debut novel, "Narcopolis," shortlisted for the Man Booker Prize, explores which historical setting?\par
\quad - a) Colonial Calcutta\par
\quad - b) 1970s Bombay's opium dens\par
\quad - c) Rural Rajasthan's feudal society\par

\textbf{Q9} The British investment of 100 million pounds in Indian railways by 1875 led to the development of the Guaranteed System. What was the primary benefit for the investors under this system?\par
\quad - a) Guaranteed fixed interest on their investment\par
\quad - b) Ownership of railway lines\par
\quad - c) Tax exemptions on profits\par

\textbf{Q10} The coalition governments led by Rajendra Narayan Singh Deo and Bishwanath Das in Odisha had a common political party, the Swatantra Party. What was the Swatantra Party's main ideology?\par
\quad - a) Socialism and nationalisation\par
\quad - b) Free market and individual liberty\par
\quad - c) Agrarian reform and rural development\par

\textbf{Q11} The Ashokastami Mela in Tripura's Kaliashahar subdivision is a Shaiva pilgrimage. Which deity is primarily worshipped during this mela?\par
\quad - a) Lord Vishnu\par
\quad - b) Goddess Durga\par
\quad - c) Lord Shiva\par

\textbf{Q12} The Lushai Hills in Mizoram are known for biodiversity. Which type of vegetation is most common in this region?\par
\quad - a) Alpine meadows\par
\quad - b) Tropical evergreen forests\par
\quad - c) Arid scrublands\par

\textbf{Q13} Williamnagar, the headquarters of East Garo Hills in Meghalaya, is named after Captain Williamson Sangma. What was Captain Sangma's primary role in the region's history?\par
\quad - a) A British colonial officer\par
\quad - b) A freedom fighter and political leader\par
\quad - c) A renowned social reformer\par

\textbf{Q14} The Umshiang Double‑Decker Bridge in Cherrapunjee is made of living roots of Ficus elastica. How long does it typically take for such a root bridge to become fully functional?\par
\quad - a) 2‑3 years\par
\quad - b) 10‑15 years\par
\quad - c) 50‑100 years\par

\textbf{Q15} Jowai, surrounded by the Myntdu River, is known for its caves. What is unique about the cave networks in Lumshnong and Syndai?\par
\quad - a) They contain ancient rock carvings\par
\quad - b) They are among the largest cave networks in Asia\par
\quad - c) They have underground waterfalls\par

\textbf{Q16} Bomdilla, near the Eaglesnest Wildlife Sanctuary, is inhabited by several tribes. Which is the dominant tribe in this area?\par
\quad - a) Nishi\par
\quad - b) Monpa\par
\quad - c) Adi\par

\textbf{Q17} Bhogeshwar Baruah, the first Arjuna Award winner from Northeast India, excelled in which athletics event at the 1966 Bangkok Asian Games?\par
\quad - a) 100 metres sprint\par
\quad - b) 800 metres race\par
\quad - c) Long jump\par

\textbf{Q18} Dr. Talimeran Ao, captain of the Indian football team, had a long association with Mohun Bagan. In which year did he retire from professional football?\par
\quad - a) 1950\par
\quad - b) 1960\par
\quad - c) 1970\par

\textbf{Q19} Romulus Whitaker established the Agumbe Rainforest Research Station with funds from the Whitley Award. What is the primary focus of research at this station?\par
\quad - a) Elephant conservation\par
\quad - b) King cobra ecology\par
\quad - c) Tiger population dynamics\par

\textbf{Q20} Dev Anand's film "Hum Naujawan" marked Tabu's Bollywood debut. What was Tabu's role in this film?\par
\quad - a) Lead actress\par
\quad - b) Supporting role as a child artist\par
\quad - c) Background dancer\par

\textbf{Q21} The CTC process is widely used in tea production. What is the main advantage of CTC tea over orthodox tea?\par
\quad - a) Better flavour\par
\quad - b) Faster brewing and stronger colour\par
\quad - c) Higher antioxidant content\par

\textbf{Q22} MCX, or Multi‑Commodity Exchange of India Ltd, facilitates farmers' access to crop‑related information. What is the main goal of setting up Gramin Suvidha Kendras?\par
\quad - a) Providing financial assistance to farmers\par
\quad - b) Educating farmers about market prices\par
\quad - c) Promoting organic farming\par

\textbf{Q23} Santokben Jadeja, known as the "Godmother," was a controversial figure in Gujarat. What was her primary occupation?\par
\quad - a) Politician\par
\quad - b) Gang leader\par
\quad - c) Social worker\par

\textbf{Q24} Ustad Rashid Khan established the Shakhri Begum Memorial Trust in memory of his mother. What is the primary aim of this trust?\par
\quad - a) Promoting women's education\par
\quad - b) Supporting classical music\par
\quad - c) Providing healthcare to the needy\par

\textbf{Q25} General Slim is credited with winning the Battle of Imphal. Which army did he command during this battle?\par
\quad - a) British Indian Army\par
\quad - b) Japanese Army\par
\quad - c) German Army\par

\textbf{Q26} The Kerala Congress (Jacob) was formed by T.M. Jacob. What was his main political agenda?\par
\quad - a) Promoting communism\par
\quad - b) Advocating for farmers' rights\par
\quad - c) Supporting regional autonomy\par

\textbf{Q27} The Dooars region, with Siliguri as its largest city, is known for its tea gardens. Which type of tea is predominantly grown in this region?\par
\quad - a) Green tea\par
\quad - b) Black tea\par
\quad - c) White tea\par

\textbf{Q28} The O5 group of countries includes India, China, Brazil, Mexico, and South Africa. What is the primary focus of this group?\par
\quad - a) Economic cooperation and development\par
\quad - b) Military alliance\par
\quad - c) Cultural exchange\par

\textbf{Q29} The Fort St. George museum houses a statue of Lord Cornwallis depicting the surrender of Tipu Sultan's sons. In which Anglo‑Mysore War did this event occur?\par
\quad - a) First Anglo‑Mysore War\par
\quad - b) Third Anglo‑Mysore War\par
\quad - c) Fourth Anglo‑Mysore War\par

\textbf{Q30} Mark Twain's "Following the Equator" chronicles his travels. Which mode of transport did he primarily use during his travels in India?\par
\quad - a) Trains\par
\quad - b) Boats\par
\quad - c) Elephants\par

\textbf{Q31} Mansar Lake, near Jammu, is a popular tourist spot. What is the main religious significance of this lake?\par
\quad - a) It is believed to be a sacred site for Hindus\par
\quad - b) It is a major Buddhist pilgrimage site\par
\quad - c) It is a Sufi shrine\par

\textbf{Q32} Vinod Mehta's memoir "Lucknow Boy" provides insights into his life. What was his most well‑known role in Indian media?\par
\quad - a) Film director\par
\quad - b) Newspaper editor\par
\quad - c) Sports commentator\par

\textbf{Q33} Rumtek Monastery, near Gangtok, is the seat of which Buddhist sect?\par
\quad - a) Gelug\par
\quad - b) Kagyupa\par
\quad - c) Nyingma\par

\textbf{Q34} The De‑notified Tribes in India, comprising 13.51 crore people, face specific challenges. What is the main issue faced by these communities?\par
\quad - a) Lack of access to education\par
\quad - b) Social stigma and discrimination\par
\quad - c) Environmental degradation\par

\textbf{Q35} During the Mysore Dasara procession, the idol of Goddess Chamundeshwari is placed on an elephant. What is the name of the lead elephant that carries the idol?\par
\quad - a) Airavata\par
\quad - b) Balarama\par
\quad - c) Drona\par

\textbf{Q36} The 72 melakarta raga system, developed by Venkatamukhi, is fundamental to which form of music?\par
\quad - a) Hindustani classical music\par
\quad - b) Carnatic classical music\par
\quad - c) Folk music\par

\textbf{Q37} The NTCA aims to conserve tigers. Which project is primarily associated with tiger conservation in India?\par
\quad - a) Project Elephant\par
\quad - b) Project Tiger\par
\quad - c) Project Snow Leopard\par

\textbf{Q38} India First Life Insurance is a joint venture. Which is the primary focus area of this insurance company?\par
\quad - a) Rural insurance\par
\quad - b) Health insurance\par
\quad - c) Life insurance\par

\textbf{Q39} The National Research Centre for Grapes in Pune focuses on grape research. Which type of grape is primarily researched at this centre?\par
\quad - a) Wine grapes\par
\quad - b) Table grapes\par
\quad - c) Raisin grapes\par

\textbf{Q40} Khadi Pratisthan‑Sodepur ashram hosted Mahatma Gandhi during a crucial period. What was the main purpose of Gandhi's visit to Noakhali after leaving the ashram?\par
\quad - a) To promote khadi\par
\quad - b) To restore communal harmony\par
\quad - c) To protest against British rule\par

\textbf{Q41} The Grizzled Giant Squirrel is found in the Srivilliputhur area. What is the main characteristic that distinguishes this squirrel from other species?\par
\quad - a) Its size and grizzled fur\par
\quad - b) Its bright colours\par
\quad - c) Its nocturnal habits\par

\textbf{Q42} GAGAN, an ISRO‑Airport Authority of India venture, is used in aviation. What is the primary benefit of using GAGAN for airline pilots?\par
\quad - a) Improved fuel efficiency\par
\quad - b) Enhanced navigational accuracy\par
\quad - c) Better communication systems\par

\textbf{Q43} Roshanlal Vishwakarma's Bud Chipper is used for pruning sugarcane. What is the main advantage of using this tool?\par
\quad - a) Faster pruning\par
\quad - b) Reduced labour costs\par
\quad - c) Improved plant health\par

\textbf{Q44} G. Akash became the youngest winner in men's chess. Which title did he win at the national championship?\par
\quad - a) National Junior Champion\par
\quad - b) National Senior Champion\par
\quad - c) National Sub‑Junior Champion\par

\textbf{Q45} Sunil Gangopadhyay's first novel was "Atma Prakash." What is the main theme explored in this novel?\par
\quad - a) Political revolution\par
\quad - b) Self‑discovery\par
\quad - c) Social injustice\par

\textbf{Q46} The McMahon Line was laid down in 1914. Which region's border does it primarily demarcate?\par
\quad - a) Kashmir\par
\quad - b) Arunachal Pradesh\par
\quad - c) Sikkim\par

\textbf{Q47} Many Kashmiris have succeeded in the All India Civil Services Examination. What does this trend signify?\par
\quad - a) Increased educational opportunities in Kashmir\par
\quad - b) Growing political awareness\par
\quad - c) Economic prosperity\par

\textbf{Q48} Guru Arjun Dev founded Tarn Taran Sahib. What is the main significance of this town for Sikhs?\par
\quad - a) It is a major pilgrimage site\par
\quad - b) It was the birthplace of Guru Nanak\par
\quad - c) It is known for its martial arts\par

\textbf{Q49} Pandurang Khankoje, a founder of the Ghadar Party, collaborated with Tina Modotti. What was the Ghadar Party's main objective?\par
\quad - a) Promoting Indian culture abroad\par
\quad - b) Overthrowing British rule in India\par
\quad - c) Establishing trade relations\par

\textbf{Q50} Amit Saigal founded the Rock Street Journal. What type of publication is this journal?\par
\quad - a) A literary magazine\par
\quad - b) A music magazine\par
\quad - c) A political newspaper\par