\section{ARTS MIXED BAG TWO}

\textbf{Q1} Guru Ghasidas National Park is named after the founder of the Satnami sect. What were the main teachings of Guru Ghasidas?\par
\quad - a) Monotheism and social equality\par
\quad - b) Polytheism and caste hierarchy\par
\quad - c) Non‑violence and asceticism\par

\textbf{Q2} Swami Vivekananda set sail for India in 1896. Which conference is he best known for attending before this voyage?\par
\quad - a) World Parliament of Religions\par
\quad - b) Round Table Conference\par
\quad - c) Bandung Conference\par

\textbf{Q3} Ram Prasad Bismil wrote "Sarfaroshi ki Tamanna." What was the main message of this patriotic song?\par
\quad - a) Peaceful resistance\par
\quad - b) Revolutionary zeal\par
\quad - c) Social reform\par

\textbf{Q4} Mehrangarh Fort is located in Jodhpur. What is the main architectural style of this fort?\par
\quad - a) Mughal\par
\quad - b) Rajput\par
\quad - c) Dravidian\par

\textbf{Q5} Jama Masjid in Delhi houses relics of the Prophet. Which Mughal emperor commissioned the construction of this mosque?\par
\quad - a) Akbar\par
\quad - b) Shah Jahan\par
\quad - c) Aurangzeb\par

\textbf{Q6} Sain Hazrat Mian Mir laid the foundation stone of the Golden Temple. What is his main legacy?\par
\quad - a) He was a Sufi saint known for interfaith harmony\par
\quad - b) He was a Mughal courtier\par
\quad - c) He was a Sikh warrior\par

\textbf{Q7} Dachigam National Park is known for the Marsar Lake. Which animal is this park primarily known for protecting?\par
\quad - a) Snow Leopard\par
\quad - b) Hangul (Kashmiri Stag)\par
\quad - c) Red Panda\par

\textbf{Q8} Darjeeling Tea was the first Indian product to receive a GI tag. What does a GI tag primarily protect?\par
\quad - a) Manufacturing process\par
\quad - b) Geographical origin and quality\par
\quad - c) Brand name\par

\textbf{Q9} The Bishnoi sect was founded by Guru Jambeshwar. What is the core principle of this sect?\par
\quad - a) Protecting the environment and wildlife\par
\quad - b) Promoting trade and commerce\par
\quad - c) Advocating for women's rights\par

\textbf{Q10} Gopal Swarup Pathak was the first Indian Vice‑President not to become President. What was his primary profession before entering politics?\par
\quad - a) Lawyer\par
\quad - b) Doctor\par
\quad - c) Engineer\par

\textbf{Q11} Michael Madhusudan Dutta wrote "Hector Badh Kavya." What is the main theme of this play?\par
\quad - a) Romantic love\par
\quad - b) Heroic sacrifice\par
\quad - c) Political intrigue\par

\textbf{Q12} The Chocolate Bomb was invented in Kolkata. What is the main ingredient of this sweet?\par
\quad - a) Chocolate\par
\quad - b) Coconut\par
\quad - c) Khoya\par

\textbf{Q13} Khushwant Singh wrote "The Freethinker's Prayer Book." What is the main focus of his writings?\par
\quad - a) Spirituality and religion\par
\quad - b) Secularism and humanism\par
\quad - c) History and politics\par

\textbf{Q14} Kodaikanal is associated with several landmarks. What is Coaker's Walk known for?\par
\quad - a) Hiking trail with scenic views\par
\quad - b) Ancient temple\par
\quad - c) Wildlife sanctuary\par

\textbf{Q15} Union Bank of India has a tagline. What does the tagline actually mean?\par
\quad - a) They help you earn more interest\par
\quad - b) They are ethical and dependable\par
\quad - c) They will help you get high returns on stocks\par

\textbf{Q16} Guru Hargobind established Akal Takht. What is the significance of Akal Takht?\par
\quad - a) It is a place for religious ceremonies\par
\quad - b) It is a symbol of Sikh sovereignty\par
\quad - c) It is a center for learning\par

\textbf{Q17} The Indian Institute of Science‑Bangalore is ranked in the Global Employability List. What does this ranking signify?\par
\quad - a) High research output\par
\quad - b) Strong industry connections\par
\quad - c) Excellent infrastructure\par

\textbf{Q18} Catlanchimauli is the highest peak in Goa. What type of terrain characterizes this peak?\par
\quad - a) Rocky and barren\par
\quad - b) Forested and green\par
\quad - c) Snow‑covered\par

\textbf{Q19} Gabbar Singh appeared in a Britannia advertisement. Why was this character chosen for the advertisement?\par
\quad - a) To promote bravery\par
\quad - b) To create a memorable and humorous campaign\par
\quad - c) To appeal to children\par

\textbf{Q20} ISRO's Cartosat series is used for mapping. What is the main application of these satellites?\par
\quad - a) Weather forecasting\par
\quad - b) Earth observation and mapping\par
\quad - c) Telecommunications\par

\textbf{Q21} The MKSS campaigned for transparency. Which right was the focus of their campaign?\par
\quad - a) Right to Education\par
\quad - b) Right to Information\par
\quad - c) Right to Employment\par

\textbf{Q22} Leh is a predominantly Buddhist district. Which form of Buddhism is primarily practiced here?\par
\quad - a) Theravada\par
\quad - b) Mahayana\par
\quad - c) Vajrayana\par

\textbf{Q23} Franck Ribery won the UEFA Best Player in Europe Award. Which club did he play for at the time?\par
\quad - a) Real Madrid\par
\quad - b) Barcelona\par
\quad - c) Bayern Munich\par

\textbf{Q24} The first SMS was sent in 1992. What was the purpose of the first ever SMS?\par
\quad - a) It was just a way to test the new messaging system\par
\quad - b) It was to show what the new technology was capable of\par
\quad - c) It was to wish a merry Christmas\par

\textbf{Q25} The movie "Guide" was based on a novel. Which theme was prevalent in the storyline?\par
\quad - a) A guide falling in love with his tutee's wife\par
\quad - b) A guide solving a murder\par
\quad - c) A guide on a holy road\par

\textbf{Q26} Avani Chaturvedi was the first solo pilot in the Indian Air Force. What was her role?\par
\quad - a) Transport of ammunition to a different base\par
\quad - b) Fighter pilot\par
\quad - c) Surveillance pilot\par

\textbf{Q27} What is the meaning of the word "Shakti" in context with India and France?\par
\quad - a) A military pact against enemies\par
\quad - b) Power through solidarity\par
\quad - c) The army strength\par

\textbf{Q28} Who was the first to conceptualize the Indian space program?\par
\quad - a) C.V. Raman\par
\quad - b) Vikram Sarabhai\par
\quad - c) Homi Bhabha\par

\textbf{Q29} Why was the INS Arihant a turning point in the Indian Navy?\par
\quad - a) It was the biggest ship made by the Navy till then\par
\quad - b) It was the first submarine that was run by nuclear energy\par
\quad - c) It had stealth technology and could not be detected by enemy radar\par

\textbf{Q30} Why is Kerala known as the "spice garden of India"?\par
\quad - a) Its spices are mostly exported to various places in India\par
\quad - b) It is the only place in India where spices are grown\par
\quad - c) The rich soil is very conducive for growing spices\par

\textbf{Q31} Bangalore is known as the "Silicon Valley of India" because...\par
\quad - a) It is the biggest manufacturer of silicon microchips\par
\quad - b) It is the hub for all software technology companies\par
\quad - c) It is closest to the equator\par

\textbf{Q32} "The land of five rivers" is also the place that the holiest site for Sikhs is. Which state are we speaking about?\par
\quad - a) Haryana\par
\quad - b) Punjab\par
\quad - c) Himachal Pradesh\par

\textbf{Q33} What happens to the lives of the main characters in "A Suitable Boy"?\par
\quad - a) They all have tragic endings\par
\quad - b) They all end up wealthy\par
\quad - c) Their lives are intertwined and they all find some sort of fulfilment\par

\textbf{Q34} What instrument was Ustad Bismillah Khan most famous for playing?\par
\quad - a) The Sitar\par
\quad - b) The Tabla\par
\quad - c) The Shehnai\par

\textbf{Q35} Which is the highest mountain peak completely within the Indian border?\par
\quad - a) Mt. K2\par
\quad - b) Kanchenjunga\par
\quad - c) Nanda Devi\par

\textbf{Q36} What makes Jim Corbett National Park so suitable for Bengal Tigers?\par
\quad - a) Its location in the Himalayas ensures that the weather suits their fur and appetite\par
\quad - b) It has a diverse population of various animals who serve as prey for the tigers\par
\quad - c) It is the only dense forest in India\par

\textbf{Q37} What is the main industry for which the "City of Joy" is known?\par
\quad - a) Leather tanneries\par
\quad - b) Software companies\par
\quad - c) Film\par

\textbf{Q38} How does the story of "Shakuntala" end?\par
\quad - a) She dies because of heartbreak\par
\quad - b) She is reunited with her husband\par
\quad - c) She starts a revolution against her husband\par

\textbf{Q39} Andhra Pradesh has good land and abundant water because...\par
\quad - a) There are many lakes\par
\quad - b) There are good monsoons and a river delta\par
\quad - c) The black cotton soil retains water easily\par

\textbf{Q40} How is ISRO planning to use the data that they get from the satellites?\par
\quad - a) Use it for space exploration\par
\quad - b) Use the data for helping the country with agriculture and disaster relief\par
\quad - c) Use the data to spy on other countries\par

\textbf{Q41} Why is the city of Jaipur so pink?\par
\quad - a) It's the favourite colour of the royalty\par
\quad - b) All the buildings and structures were painted pink by order of the King\par
\quad - c) Pink is the cheapest paint in the region\par

\textbf{Q42} What exactly were the "Wings of Fire" that Dr. A.P.J. Abdul Kalam was talking about?\par
\quad - a) The wings of a commercial jetliner that he used to fly in often\par
\quad - b) The project that he contributed to with DRDO\par
\quad - c) The nuclear missiles that were developed\par

\textbf{Q43} How does the Damodar River cause sorrow to the state?\par
\quad - a) It causes frequent landslides\par
\quad - b) It causes frequent floods\par
\quad - c) It causes the water table to drop in the state\par

\textbf{Q44} Is the Indian Parliament bicameral or unicameral?\par
\quad - a) Bicameral\par
\quad - b) Unicameral\par
\quad - c) There is no parliament in India\par

\textbf{Q45} Why is Himachal Pradesh so suitable for orchards?\par
\quad - a) Its proximity to the ocean keeps the weather humid\par
\quad - b) Its high altitude and favourable climate is suitable for growing fruits\par
\quad - c) There is a variety of bees that keep the flowering plants pollinated\par

\textbf{Q46} Is there a specific thing that Arundhati Roy wanted to highlight in "The God of Small Things"?\par
\quad - a) It discusses the issue of forbidden love\par
\quad - b) It talks about child abuse\par
\quad - c) It shows the impact of war on small children\par

\textbf{Q47} Which of the leather cities of India has a river flowing through it?\par
\quad - a) Kanpur\par
\quad - b) Agra\par
\quad - c) Chennai\par

\textbf{Q48} Which colour of the Indian national flag is on top and is the strongest symbol of the flag?\par
\quad - a) White\par
\quad - b) Green\par
\quad - c) Saffron\par

\textbf{Q49} What does "Arunachal Pradesh" mean, when literally translated?\par
\quad - a) The land of the rising sun\par
\quad - b) The land that has a lot of mountains\par
\quad - c) The land where a lot of rain falls\par

\textbf{Q50} The story "Train to Pakistan" is about...\par
\quad - a) A person taking a train to a cricket match\par
\quad - b) The impact of partition on the lives of ordinary people\par
\quad - c) Someone who has to travel for work by train very often\par