\section{ANSWER KEY: Basic Concepts of Physics}

\textbf{Q1} b) They are in free fall, circling Earth at the same velocity as the station.\par
\textbf{Q2} b) Normal Force\par
\textbf{Q3} b) Centripetal Acceleration\par
\textbf{Q4} b) Energy, mass, and the speed of light.\par
\textbf{Q5} b) Newton's Third Law of Motion\par
\textbf{Q6} a) Its hollow design lowers its overall density.\par
\textbf{Q7} a) The object's weight would lessen.\par
\textbf{Q8} c) Both objects will touch the ground simultaneously.\par
\textbf{Q9} b) Longitudinal wave; by means of compressions and rarefactions of particles along the wave's direction.\par
\textbf{Q10} a) First Law of Thermodynamics\par
\textbf{Q11} a) The reduction in air pressure leads to the expansion of trapped air in your ears.\par
\textbf{Q12} b) To maintain angular momentum.\par
\textbf{Q13} b) Doppler Effect\par
\textbf{Q14} b) It becomes four times as much.\par
\textbf{Q15} a) Black absorbs more heat by reflecting less sunlight.\par
\textbf{Q16} b) Reflection and refraction of sunlight inside the raindrops.\par
\textbf{Q17} b) The normal force acting on you decreases.\par
\textbf{Q18} b) Gravity\par
\textbf{Q19} a) Metal is a superior heat conductor.\par
\textbf{Q20} a) Perspective diminishes their angular size.\par
\textbf{Q21} b) It converges parallel light rays to a single point.\par
\textbf{Q22} b) 35 m/s\par
\textbf{Q23} b) The tilt of Earth's axis.\par
\textbf{Q24} b) Surface tension reduces their surface area.\par
\textbf{Q25} a) The water's density slows light down, causing it to speed up again in air.\par
\textbf{Q26} a) Escape Velocity\par
\textbf{Q27} c) Objects float if they displace a volume of fluid equal to their weight.\par
\textbf{Q28} b) Refraction\par
\textbf{Q29} b) Gamma Rays\par
\textbf{Q30} a) Conduction\par
\textbf{Q31} a) Due to gyroscopic effect\par
\textbf{Q32} a) Second Law of Thermodynamics\par
\textbf{Q33} b) Through refraction and dispersion\par
\textbf{Q34} b) Frictional Force\par
\textbf{Q35} a) Due to buoyancy\par
\textbf{Q36} b) Dielectric heating\par
\textbf{Q37} b) By converging light rays\par
\textbf{Q38} b) Orbital Velocity\par
\textbf{Q39} b) Due to magnetic forces\par
\textbf{Q40} a) Stimulated emission\par
\textbf{Q41} c) By converging light rays\par
\textbf{Q42} b) Potential Energy\par
\textbf{Q43} a) Due to air resistance\par
\textbf{Q44} b) Conversion of kinetic energy to electrical energy\par
\textbf{Q45} b) Due to magnetic forces\par
\textbf{Q46} a) Conduction\par
\textbf{Q47} b) Due to reflection\par
\textbf{Q48} a) Photovoltaic effect\par
\textbf{Q49} a) Due to gyroscopic effect\par
\textbf{Q50} b) Kinetic Energy\par