\section{CHEMICAL ENGINEERING}

\textbf{Q1} What rule is used to estimate the specific heat capacity of a solid compound?\par
\quad - a) Kopp's rule\par
\quad - b) Law of Petit and Dulong\par
\quad - c) Nernst heat theorem\par

\textbf{Q2} What is the primary product obtained from controlled oxidation of LPG?\par
\quad - a) Fatty acids\par
\quad - b) Acetylene\par
\quad - c) Acetic acid\par

\textbf{Q3} What does the term "petrochemicals" signify?\par
\quad - a) Chemicals based on coal\par
\quad - b) Chemicals based on rocks\par
\quad - c) Chemicals based on atmospheric conditions\par

\textbf{Q4} Which raw material obtained from petroleum can be used in preparation of acetic acid?\par
\quad - a) Acetone\par
\quad - b) Phosphoric acid\par
\quad - c) Ethylene\par

\textbf{Q5} Which process is used to convert saturated hydrocarbons from petroleum into more reactive material?\par
\quad - a) Hydrogenation\par
\quad - b) Acidification\par
\quad - c) Chlorination\par

\textbf{Q6} Earth's crust is about what percentage of Earth's total volume?\par
\quad - a) 1%\par
\quad - b) 5%\par
\quad - c) 15%\par

\textbf{Q7} Kimberlite pipes are best known for being a primary source of:\par
\quad - a) Gold\par
\quad - b) Copper\par
\quad - c) Diamonds\par

\textbf{Q8} Kimberlite pipes are named after a town in which country?\par
\quad - a) South Africa\par
\quad - b) Brazil\par
\quad - c) Australia\par

\textbf{Q9} Kimberlite pipes are typically found in which type of geological setting?\par
\quad - a) Mid‑ocean ridges\par
\quad - b) Cratonic regions\par
\quad - c) Volcanic arcs\par

\textbf{Q10} Which of the following is a type of sedimentary rock?\par
\quad - a) Organic rock\par
\quad - b) Chemical rock\par
\quad - c) All of the above\par

\textbf{Q11} What does "DSS" stand for in petroleum engineering terminology?\par
\quad - a) Drill line system\par
\quad - b) Dogleg severity\par
\quad - c) Drill line stream\par

\textbf{Q12} What does "RIH" stand for in petroleum engineering?\par
\quad - a) Run in hole\par
\quad - b) Rip in hole\par
\quad - c) Rest in hole\par

\textbf{Q13} What is considered an "Effective Source Rock" in petroleum geology?\par
\quad - a) Any rock containing hydrocarbons\par
\quad - b) Rock that has generated and expelled hydrocarbons\par
\quad - c) Rock with potential to generate hydrocarbons\par

\textbf{Q14} In copper processing, the term "blister copper" refers to:\par
\quad - a) Refined copper\par
\quad - b) Impure copper\par
\quad - c) Processed copper\par

\textbf{Q15} What type of compounds are primarily aromatic in nature?\par
\quad - a) Aromatic compounds\par
\quad - b) Aliphatic compounds\par
\quad - c) Paraffins\par

\textbf{Q16} Which non‑petroleum source was earlier used for production of acetylene?\par
\quad - a) CaC₂\par
\quad - b) H₂S\par
\quad - c) Paraffin\par

\textbf{Q17} What is the main component of coke oven gas?\par
\quad - a) Tar\par
\quad - b) Sulphide coke\par
\quad - c) Coke oven gas\par

\textbf{Q18} Which of the following processes is used in chemical engineering for determining composition?\par
\quad - a) Cracking\par
\quad - b) Reforming\par
\quad - c) Chromatography\par

\textbf{Q19} Which field of engineering applies principles to develop medical equipment?\par
\quad - a) Mechanical Engineering\par
\quad - b) Biomedical Engineering\par
\quad - c) Electrical Engineering\par

\textbf{Q20} In biomedical engineering, what is the primary purpose of an ECG?\par
\quad - a) Measuring brain activity\par
\quad - b) Measuring heart electrical activity\par
\quad - c) Measuring muscle movement\par

\textbf{Q21} What is the primary application of mass transfer operations in chemical engineering?\par
\quad - a) Separation processes\par
\quad - b) Energy generation\par
\quad - c) Heat exchange\par

\textbf{Q22} Which of the following is a primary source of biomedical waste?\par
\quad - a) Textile industries\par
\quad - b) Hospitals\par
\quad - c) Paper mills\par

\textbf{Q23} What does "INSAT" stand for in Indian engineering achievements?\par
\quad - a) Indian National Satellite\par
\quad - b) International Satellite\par
\quad - c) Indian Navigation System and Tracking\par

\textbf{Q24} Which material is commonly used in artificial joints in biomedical engineering?\par
\quad - a) Wood\par
\quad - b) Titanium\par
\quad - c) Aluminum\par

\textbf{Q25} What is the process of breaking down larger hydrocarbon molecules into smaller ones called?\par
\quad - a) Reforming\par
\quad - b) Alkylation\par
\quad - c) Cracking\par

\textbf{Q26} Which of the following is not typically studied in Earth Sciences?\par
\quad - a) Meteorology\par
\quad - b) Oceanography\par
\quad - c) Quantum mechanics\par

\textbf{Q27} What is the primary function of fluid mechanics in chemical engineering?\par
\quad - a) Study of fluid behavior\par
\quad - b) Study of chemical reactions\par
\quad - c) Study of heat transfer\par

\textbf{Q28} Which of the following is used to measure blood oxygen levels?\par
\quad - a) Electrocardiogram\par
\quad - b) Pulse oximeter\par
\quad - c) Electroencephalogram\par

\textbf{Q29} What is the primary concern in nuclear power engineering?\par
\quad - a) Heat transfer\par
\quad - b) Radiation safety\par
\quad - c) Fluid mechanics\par

\textbf{Q30} Which of the following is a primary component of fertilizer technology?\par
\quad - a) Petroleum refining\par
\quad - b) Polymer processing\par
\quad - c) Nitrogen fixation\par

\textbf{Q31} What is the primary purpose of process control and instrumentation in chemical engineering?\par
\quad - a) Maintaining optimal operating conditions\par
\quad - b) Maximizing production costs\par
\quad - c) Minimizing product quality\par

\textbf{Q32} What type of process equipment is primarily used for solid‑liquid separation?\par
\quad - a) Distillation column\par
\quad - b) Filter press\par
\quad - c) Heat exchanger\par

\textbf{Q33} In petroleum refinery engineering, what is the primary purpose of the catalytic cracker?\par
\quad - a) To separate crude oil components\par
\quad - b) To convert heavy hydrocarbons to lighter ones\par
\quad - c) To remove sulfur compounds\par

\textbf{Q34} Which of the following is a primary area of study in thermodynamics?\par
\quad - a) Energy conversion\par
\quad - b) Fluid flow\par
\quad - c) Chemical kinetics\par

\textbf{Q35} What is stoichiometry primarily concerned with in chemical engineering?\par
\quad - a) Heat transfer rates\par
\quad - b) Quantitative relationships in chemical reactions\par
\quad - c) Fluid flow behavior\par

\textbf{Q36} Which type of reaction is most commonly studied in chemical reaction engineering?\par
\quad - a) Nuclear reactions\par
\quad - b) Catalytic reactions\par
\quad - c) Gravitational interactions\par

\textbf{Q37} What is the primary purpose of plant economics in chemical engineering?\par
\quad - a) Studying plant biology\par
\quad - b) Evaluating the economic feasibility of chemical processes\par
\quad - c) Designing plant layout\par

\textbf{Q38} Which material is most commonly used in refractory technology?\par
\quad - a) Aluminum\par
\quad - b) Ceramic\par
\quad - c) Plastic\par

\textbf{Q39} What is the primary purpose of mass transfer operations in chemical engineering?\par
\quad - a) Moving heat between systems\par
\quad - b) Moving mass between phases\par
\quad - c) Converting energy forms\par

\textbf{Q40} Which field of chemical engineering deals with the processing of crude oil?\par
\quad - a) Polymer technology\par
\quad - b) Petroleum refinery engineering\par
\quad - c) Nuclear power engineering\par

\textbf{Q41} What is the primary concern in polymer technology?\par
\quad - a) Nuclear reactions\par
\quad - b) Polymer synthesis and processing\par
\quad - c) Oil extraction\par

\textbf{Q42} Which of the following is a primary area of study in biomedical engineering?\par
\quad - a) Civil infrastructure\par
\quad - b) Medical device design\par
\quad - c) Industrial manufacturing\par

\textbf{Q43} What is the primary focus of environmental engineering within chemical engineering?\par
\quad - a) Maximizing pollution\par
\quad - b) Minimizing environmental impact\par
\quad - c) Increasing waste production\par

\textbf{Q44} Which discipline focuses on the study of Earth's oceans?\par
\quad - a) Meteorology\par
\quad - b) Geology\par
\quad - c) Oceanography\par

\textbf{Q45} What is the primary purpose of furnace technology in chemical engineering?\par
\quad - a) Cooling processes\par
\quad - b) Providing heat for processes\par
\quad - c) Filtering contaminants\par

\textbf{Q46} Which branch of Earth science studies earthquakes?\par
\quad - a) Volcanology\par
\quad - b) Seismology\par
\quad - c) Meteorology\par

\textbf{Q47} What is the primary purpose of heat transfer operations in chemical engineering?\par
\quad - a) Moving mass between phases\par
\quad - b) Converting chemical energy\par
\quad - c) Controlling temperature in processes\par

\textbf{Q48} Which of the following is a primary area of study in mechanical operations?\par
\quad - a) Fluid dynamics\par
\quad - b) Size reduction and separation\par
\quad - c) Chemical reactions\par

\textbf{Q49} What is the main focus of materials and construction in chemical engineering?\par
\quad - a) Building design\par
\quad - b) Material selection for chemical processes\par
\quad - c) Road construction\par

\textbf{Q50} Which of the following is primarily studied in fuels and combustion?\par
\quad - a) Nuclear energy\par
\quad - b) Solar power\par
\quad - c) Burning characteristics of fuels\par