\section{CIVIL ENGINEERING}

\textbf{Q1} Which civil engineer built London's first sewer network?\par
\quad - a) Sir Joseph William Bazalgette\par
\quad - b) Isambard Kingdom Brunel\par
\quad - c) John Smeaton\par

\textbf{Q2} What is the name of the ancient Indian stepwell located in Gujarat, known for its intricate architecture and water conservation techniques?\par
\quad - a) Rani Ki Vav\par
\quad - b) Chand Baori\par
\quad - c) Agrasen Ki Baoli\par

\textbf{Q3} Which famous Indian civil engineer is known as the "Father of Indian Railways"?\par
\quad - a) Mokshagundam Visvesvaraya\par
\quad - b) E. Sreedharan\par
\quad - c) Satish Dhawan\par

\textbf{Q4} What is the term for the process of strengthening soil by injecting grout into it, often used in foundation repair?\par
\quad - a) Soil nailing\par
\quad - b) Grouting\par
\quad - c) Compaction\par

\textbf{Q5} Which Indian bridge, opened in 2018, is the world's tallest rail bridge, standing 359 meters above the Chenab River?\par
\quad - a) Bandra-Worli Sea Link\par
\quad - b) Chenab Bridge\par
\quad - c) Howrah Bridge\par

\textbf{Q6} What is the name of the ancient Roman material used in construction, which is a precursor to modern concrete?\par
\quad - a) Pozzolana\par
\quad - b) Limestone\par
\quad - c) Gypsum\par

\textbf{Q7} Which Indian dam is the largest in terms of volume and is located on the Narmada River?\par
\quad - a) Bhakra Dam\par
\quad - b) Sardar Sarovar Dam\par
\quad - c) Hirakud Dam\par

\textbf{Q8} What is the term for the process of removing water from a construction site to allow excavation or foundation work?\par
\quad - a) Dewatering\par
\quad - b) Desalination\par
\quad - c) Drainage\par

\textbf{Q9} Which Indian city is home to the world's largest office building by area, the Surat Diamond Bourse?\par
\quad - a) Mumbai\par
\quad - b) Surat\par
\quad - c) Delhi\par

\textbf{Q10} What is the name of the technique used to stabilize slopes and prevent landslides by inserting steel bars into the ground?\par
\quad - a) Soil nailing\par
\quad - b) Anchoring\par
\quad - c) Grouting\par

\textbf{Q11} Which Indian civil engineer is known as the "Metro Man" for his contributions to the Delhi Metro?\par
\quad - a) E. Sreedharan\par
\quad - b) Satish Dhawan\par
\quad - c) A.P.J. Abdul Kalam\par

\textbf{Q12} What is the term for the process of compacting soil using heavy machinery to increase its density and stability?\par
\quad - a) Compaction\par
\quad - b) Consolidation\par
\quad - c) Grouting\par

\textbf{Q13} Which Indian structure is the tallest brick minaret in the world and a UNESCO World Heritage Site?\par
\quad - a) Qutub Minar\par
\quad - b) Charminar\par
\quad - c) Taj Mahal\par

\textbf{Q14} What is the name of the technique used to construct tunnels through soft ground by pushing a shield through the soil?\par
\quad - a) Tunnel boring\par
\quad - b) Shield tunneling\par
\quad - c) Cut-and-cover\par

\textbf{Q15} Which Indian city is home to the world's largest monolithic statue, the Statue of Unity?\par
\quad - a) Ahmedabad\par
\quad - b) Vadodara\par
\quad - c) Kevadia\par

\textbf{Q16} Which Indian civil engineer is known for designing the Howrah Bridge in Kolkata?\par
\quad - a) Mokshagundam Visvesvaraya\par
\quad - b) E. Sreedharan\par
\quad - c) Rendel Palmer and Tritton\par

\textbf{Q17} What is the formula for calculating the volume of a cylinder?\par
\quad - a) πr^2h\par
\quad - b) 2πrh\par
\quad - c) πr^2\par

\textbf{Q18} Which type of foundation is typically used for structures built on soft soil?\par
\quad - a) Shallow foundation\par
\quad - b) Deep foundation\par
\quad - c) Raft foundation\par

\textbf{Q19} What is the purpose of conducting a slump test in concrete?\par
\quad - a) To measure compressive strength\par
\quad - b) To determine workability\par
\quad - c) To check durability\par

\textbf{Q20} Which civil engineering structure is famous for its arch design?\par
\quad - a) Eiffel Tower\par
\quad - b) Golden Gate Bridge\par
\quad - c) Gateway of India\par

\textbf{Q21} What is the formula for calculating the moment of inertia of a rectangular beam?\par
\quad - a) (b*d^3)/12\par
\quad - b) (b*d^3)/6\par
\quad - c) (b*d^3)/4\par

\textbf{Q22} Which type of cement is used for underwater construction?\par
\quad - a) Ordinary Portland Cement\par
\quad - b) Rapid Hardening Cement\par
\quad - c) Low Heat Cement\par

\textbf{Q23} Which monument is an example of ancient civil engineering?\par
\quad - a) Great Pyramid of Giza\par
\quad - b) Colosseum\par
\quad - c) Taj Mahal\par

\textbf{Q24} What is the primary benefit of using galvanized iron sheets?\par
\quad - a) They are strong in compression\par
\quad - b) They provide corrosion resistance\par
\quad - c) They are aesthetically pleasing\par

\textbf{Q25} Which type of bridge is known for its suspension cables?\par
\quad - a) Beam bridge\par
\quad - b) Arch bridge\par
\quad - c) Suspension bridge\par

\textbf{Q26} What is the formula for calculating the flow rate in a pipe?\par
\quad - a) Q = A * v\par
\quad - b) Q = P * v\par
\quad - c) Q = A * P\par

\textbf{Q27} Which civil engineering material is known for its high tensile strength?\par
\quad - a) Steel\par
\quad - b) Concrete\par
\quad - c) Wood\par

\textbf{Q28} What is the purpose of using a water-cement ratio in concrete mix design?\par
\quad - a) To increase strength\par
\quad - b) To enhance durability\par
\quad - c) To improve workability\par

\textbf{Q29} Which monument is famous for its structural engineering?\par
\quad - a) Burj Khalifa\par
\quad - b) Eiffel Tower\par
\quad - c) Sydney Opera House\par

\textbf{Q30} What is the formula for calculating the bending moment of a beam?\par
\quad - a) M = F * L\par
\quad - b) M = F * d\par
\quad - c) M = F * r\par

\textbf{Q31} Which type of survey is used to map natural features?\par
\quad - a) Cadastral survey\par
\quad - b) Topographical survey\par
\quad - c) City survey\par

\textbf{Q32} Which type of foundation is used for high-rise buildings?\par
\quad - a) Shallow foundation\par
\quad - b) Deep foundation\par
\quad - c) Pile foundation\par

\textbf{Q33} What is the purpose of using a compaction test in soil?\par
\quad - a) To determine density\par
\quad - b) To check moisture content\par
\quad - c) To analyze soil composition\par

\textbf{Q34} Which civil engineering structure is known for its cantilever design?\par
\quad - a) Golden Gate Bridge\par
\quad - b) Eiffel Tower\par
\quad - c) Forth Bridge\par

\textbf{Q35} What is the formula for calculating the shear stress on a beam?\par
\quad - a) τ = F/A\par
\quad - b) τ = F/L\par
\quad - c) τ = V/A\par

\textbf{Q36} Which type of cement is used for rapid construction?\par
\quad - a) Ordinary Portland Cement\par
\quad - b) Rapid Hardening Cement\par
\quad - c) Low Heat Cement\par

\textbf{Q37} Which monument is an example of ancient Indian civil engineering?\par
\quad - a) Taj Mahal\par
\quad - b) Great Pyramid of Giza\par
\quad - c) Colosseum\par

\textbf{Q38} What is the purpose of using a slump test in concrete quality control?\par
\quad - a) To measure compressive strength\par
\quad - b) To determine workability\par
\quad - c) To check durability\par

\textbf{Q39} Which type of bridge is known for its beam design?\par
\quad - a) Beam bridge\par
\quad - b) Arch bridge\par
\quad - c) Suspension bridge\par

\textbf{Q40} What is the formula for calculating the volume of a rectangular prism?\par
\quad - a) l * w * h\par
\quad - b) πr^2h\par
\quad - c) 2πrh\par

\textbf{Q41} Which civil engineering material is known for its resistance to corrosion?\par
\quad - a) Steel\par
\quad - b) Concrete\par
\quad - c) Galvanized Iron\par

\textbf{Q42} What is the purpose of using a water-cement ratio in concrete durability?\par
\quad - a) To increase strength\par
\quad - b) To enhance durability\par
\quad - c) To improve workability\par

\textbf{Q43} Which monument is famous for its architectural design?\par
\quad - a) Sydney Opera House\par
\quad - b) Eiffel Tower\par
\quad - c) Burj Khalifa\par

\textbf{Q44} What is the formula for calculating the moment of inertia of a circular beam?\par
\quad - a) (πd^4)/64\par
\quad - b) (πd^4)/32\par
\quad - c) (πd^4)/16\par

\textbf{Q45} Which type of foundation is used for structures built on rocky soil?\par
\quad - a) Shallow foundation\par
\quad - b) Deep foundation\par
\quad - c) Spread foundation\par

\textbf{Q46} What is the purpose of using a sieve analysis in soil testing?\par
\quad - a) To determine density\par
\quad - b) To check moisture content\par
\quad - c) To analyze particle size distribution\par

\textbf{Q47} Which civil engineering structure is known for its tunnel design?\par
\quad - a) Channel Tunnel\par
\quad - b) Eiffel Tower\par
\quad - c) Golden Gate Bridge\par

\textbf{Q48} What is the purpose of using a compactor in soil stabilization?\par
\quad - a) To increase density\par
\quad - b) To check moisture content\par
\quad - c) To analyze soil composition\par

\textbf{Q49} Which type of bridge is known for its cable-stayed design?\par
\quad - a) Beam bridge\par
\quad - b) Arch bridge\par
\quad - c) Cable-stayed bridge\par

\textbf{Q50} Which civil engineer is famous for his work on the Great Western Railway?\par
\quad - a) Isambard Kingdom Brunel\par
\quad - b) George Stephenson\par
\quad - c) John Smeato\par