\section{COMMUNICATION TECHNOLOGY}

\textbf{Q1} What was the first commercially available smartphone with a touchscreen interface, launched in 1992?\par
\quad - a) IBM Simon Personal Communicator\par
\quad - b) Apple iPhone\par
\quad - c) Nokia 9000 Communicator\par

\textbf{Q2} Before telegram services were disbanded in 2013 in India, which public figure received the last telegram message?\par
\quad - a) Rahul Gandhi\par
\quad - b) Nandan Nilekani\par
\quad - c) President of India\par

\textbf{Q3} What was the significance of the first transatlantic telegraph cable laid in 1858?\par
\quad - a) It enabled instant communication between Europe and North America\par
\quad - b) It was the first use of Morse code\par
\quad - c) It was the first undersea cable for electricity\par

\textbf{Q4} When was the first mobile phone call made, and who made it?\par
\quad - a) 1973 – Martin Cooper of Motorola\par
\quad - b) 1981 – Steve Jobs of Apple\par
\quad - c) 1992 – Neil Papworth of Vodafone\par

\textbf{Q5} What was the name of the first commercially available handheld mobile phone launched in 1983?\par
\quad - a) Motorola DynaTAC 8000X\par
\quad - b) Nokia 1011\par
\quad - c) Ericsson GH337\par

\textbf{Q6} Which company introduced the first pocket-sized mobile phone in 1986?\par
\quad - a) Nokia\par
\quad - b) Technophone\par
\quad - c) Motorola\par

\textbf{Q7} What was the significance of Neil Papworth's SMS sent in 1992?\par
\quad - a) It was the first text message ever sent, reading "Merry Christmas"\par
\quad - b) It introduced emojis to communication\par
\quad - c) It marked the launch of GSM technology\par

\textbf{Q8} When was the first iPhone launched, and why was it revolutionary?\par
\quad - a) 2005 – It introduced touchscreen technology to phones\par
\quad - b) 2007 – It combined a phone, iPod, and internet browser in one device\par
\quad - c) 2010 – It introduced 4G connectivity\par

\textbf{Q9} What is considered the first social-networking website, launched in 1997?\par
\quad - a) MySpace\par
\quad - b) SixDegrees.com\par
\quad - c) Facebook\par

\textbf{Q10} Which company launched the world's first commercial 3G network in 2001?\par
\quad - a) AT&T (USA)\par
\quad - b) NTT DoCoMo (Japan)\par
\quad - c) Vodafone (UK)\par

\textbf{Q11} Who invented frequency-hopping spread-spectrum technology used in modern wireless communication?\par
\quad - a) Hedy Lamarr and George Antheil\par
\quad - b) Nikola Tesla\par
\quad - c) Guglielmo Marconi\par

\textbf{Q12} What is GSM technology, introduced in 1991, primarily used for?\par
\quad - a) Satellite communication\par
\quad - b) Mobile telecommunication networks\par
\quad - c) Broadband internet services\par

\textbf{Q13} When was WhatsApp launched, and what made it unique at that time?\par
\quad - a) 2007 – It introduced encrypted messaging\par
\quad - b) 2009 – It allowed free cross-platform messaging over the internet\par
\quad - c) 2011 – It supported video-calling features\par

\textbf{Q14} What milestone did South Korea achieve in mobile communication in 2019?\par
\quad - a) First country to launch nationwide 5G networks\par
\quad - b) First country to adopt LTE technology\par
\quad - c) First country to introduce foldable smartphones\par

\textbf{Q15} Who invented the World Wide Web, and when was it made publicly available?\par
\quad - a) Tim Berners-Lee – 1993\par
\quad - b) Vinton Cerf – 1989\par
\quad - c) Robert Metcalfe – 1995\par

\textbf{Q16} What was significant about IBM's Simon Personal Communicator launched in 1994?\par
\quad - a) It was the first smartphone with touchscreen capabilities\par
\quad - b) It introduced email functionality to phones\par
\quad - c) It supported video calling\par

\textbf{Q17} When was Bluetooth technology introduced, and what is its primary purpose?\par
\quad - a) 1994 – Short-range wireless data exchange between devices\par
\quad - b) 1998 – Connecting devices to Wi-Fi networks\par
\quad - c) 2000 – Enabling long-range communication for IoT devices\par

\textbf{Q18} What is considered the first search engine on the internet, launched in 1990?\par
\quad - a) Yahoo!\par
\quad - b) Archie\par
\quad - c) Google\par

\textbf{Q19} Which company launched Skype in 2003, revolutionising video calling over the internet?\par
\quad - a) Microsoft\par
\quad - b) eBay\par
\quad - c) Skype Technologies (later acquired by Microsoft)\par

\textbf{Q20} What was the primary innovation of the first Wi-Fi standard introduced in 1997?\par
\quad - a) High-speed internet connectivity over cables\par
\quad - b) Wireless local-area networking (WLAN)\par
\quad - c) Satellite internet connectivity\par

\textbf{Q21} Who developed the first email client, and when was it released?\par
\quad - a) Ray Tomlinson – 1971\par
\quad - b) Vint Cerf – 1982\par
\quad - c) Jon Postel – 1985\par

\textbf{Q22} What was the name of the first commercially successful smartphone with a physical keyboard, launched in 1996?\par
\quad - a) Nokia 9000 Communicator\par
\quad - b) BlackBerry 850\par
\quad - c) IBM Simon Personal Communicator\par

\textbf{Q23} Which company launched the first smartphone with a multi-touch interface in 2007?\par
\quad - a) Apple\par
\quad - b) Samsung\par
\quad - c) HTC\par

\textbf{Q24} What was the significance of the launch of the first 4G LTE network in 2009?\par
\quad - a) It enabled faster mobile internet speeds\par
\quad - b) It introduced Voice over LTE (VoLTE)\par
\quad - c) It marked the beginning of 5G development\par

\textbf{Q25} Who is credited with developing the first web browser, and what was its name?\par
\quad - a) Tim Berners-Lee – WorldWideWeb\par
\quad - b) Marc Andreessen – Mosaic\par
\quad - c) Vint Cerf – Netscape Navigator\par

\textbf{Q26} What was the first social-media platform to reach one billion active users?\par
\quad - a) Facebook\par
\quad - b) Twitter\par
\quad - c) Instagram\par

\textbf{Q27} Which company developed the first smartphone with a foldable display, launched in 2019?\par
\quad - a) Samsung\par
\quad - b) Huawei\par
\quad - c) Motorola\par

\textbf{Q28} What is the primary purpose of the Internet of Things (IoT)?\par
\quad - a) To connect devices for smart-home automation\par
\quad - b) To enhance cybersecurity for networks\par
\quad - c) To develop artificial-intelligence for robotics\par

\textbf{Q29} Who founded the company that developed the first commercial GPS navigation system?\par
\quad - a) John Deere\par
\quad - b) Garmin\par
\quad - c) Magellan Systems Corporation\par

\textbf{Q30} What was the name of the first satellite navigation system developed by the Soviet Union?\par
\quad - a) GLONASS\par
\quad - b) GPS\par
\quad - c) Galileo\par

\textbf{Q31} Which company launched the first commercial satellite-internet service in 1996?\par
\quad - a) Hughes Network Systems\par
\quad - b) Inmarsat\par
\quad - c) Iridium Communications\par

\textbf{Q32} What was the significance of the launch of the first fibre-optic communication system in the 1970s?\par
\quad - a) It enabled faster data transmission over long distances\par
\quad - b) It introduced wireless communication\par
\quad - c) It marked the beginning of satellite communication\par

\textbf{Q33} Who developed the first VoIP (Voice over Internet Protocol) technology?\par
\quad - a) Skype Technologies\par
\quad - b) Vonage\par
\quad - c) VocalTec\par

\textbf{Q34} What was the primary innovation of the first smartphone with a dual-camera setup, launched in 2016?\par
\quad - a) Enhanced portrait-mode photography\par
\quad - b) Improved video recording capabilities\par
\quad - c) Increased storage capacity\par

\textbf{Q35} Which company launched the first smartwatch with cellular connectivity in 2017?\par
\quad - a) Apple\par
\quad - b) Samsung\par
\quad - c) LG\par

\textbf{Q36} What is the primary purpose of the 5G network, launched in 2019?\par
\quad - a) To provide faster mobile internet speeds\par
\quad - b) To enhance IoT connectivity\par
\quad - c) To support widespread adoption of cloud computing\par

\textbf{Q37} Who founded the company that developed the first commercial virtual-reality headset, Oculus Rift?\par
\quad - a) Palmer Luckey\par
\quad - b) Mark Zuckerberg\par
\quad - c) John Carmack\par

\textbf{Q38} What was the name of the first widely used instant-messaging service launched in 1997?\par
\quad - a) ICQ\par
\quad - b) AOL Instant Messenger (AIM)\par
\quad - c) MSN Messenger\par

\textbf{Q39} Which company developed the first smartphone with an in-display fingerprint sensor, launched in 2018?\par
\quad - a) Vivo\par
\quad - b) Samsung\par
\quad - c) Huawei\par

\textbf{Q40} What was the significance of the launch of the first quantum computer by IBM in 2019?\par
\quad - a) It enabled faster processing of complex data\par
\quad - b) It introduced quantum encryption for secure communication\par
\quad - c) It marked the beginning of AI development for robotics\par