\section{COMPUTER SCIENCE ENGINEERING}

\textbf{Q1} What does the acronym "API" stand for in computer science?\par
\quad - a) Application Programming Interface\par
\quad - b) Advanced Programming Interface\par
\quad - c) Artificial Programming Interface\par

\textbf{Q2} Which programming language is known for its use in web development and is often referred to as "the language of the web?"\par
\quad - a) Java\par
\quad - b) Python\par
\quad - c) JavaScript\par

\textbf{Q3} What is the primary function of a router in a network?\par
\quad - a) To connect devices within a network\par
\quad - b) To connect multiple networks together\par
\quad - c) To provide internet access\par

\textbf{Q4} What type of algorithm is used for finding the shortest path between two nodes in a graph?\par
\quad - a) Dijkstra's Algorithm\par
\quad - b) Bellman-Ford Algorithm\par
\quad - c) Kruskal's Algorithm\par

\textbf{Q5} Which data structure is used for efficient retrieval of data based on a key?\par
\quad - a) Array\par
\quad - b) Linked List\par
\quad - c) Hash Table\par

\textbf{Q6} What is the term for the process of breaking down a complex problem into smaller, more manageable sub-problems?\par
\quad - a) Recursion\par
\quad - b) Iteration\par
\quad - c) Dynamic Programming\par

\textbf{Q7} Which operating system is known for its open-source nature and is widely used in servers?\par
\quad - a) Windows\par
\quad - b) macOS\par
\quad - c) Linux\par

\textbf{Q8} What does "SQL" stand for in database management?\par
\quad - a) Structured Query Language\par
\quad - b) Standard Query Language\par
\quad - c) System Query Language\par

\textbf{Q9} Which programming paradigm focuses on objects and their interactions?\par
\quad - a) Functional Programming\par
\quad - b) Object-Oriented Programming\par
\quad - c) Procedural Programming\par

\textbf{Q10} What is the name of the algorithm used for sorting data in ascending or descending order by repeatedly swapping adjacent elements?\par
\quad - a) Bubble Sort\par
\quad - b) Quick Sort\par
\quad - c) Merge Sort\par

\textbf{Q11} Which device is used to convert analog signals into digital signals?\par
\quad - a) Modem\par
\quad - b) Router\par
\quad - c) ADC (Analog-to-Digital Converter)\par

\textbf{Q12} What is the term for a network that spans a large geographic area, such as a city or country?\par
\quad - a) LAN (Local Area Network)\par
\quad - b) WAN (Wide Area Network)\par
\quad - c) MAN (Metropolitan Area Network)\par

\textbf{Q13} Which programming language is known for its simplicity and is often taught to beginners?\par
\quad - a) Python\par
\quad - b) Java\par
\quad - c) C++\par

\textbf{Q14} What does "CPU" stand for in computer hardware?\par
\quad - a) Central Processing Unit\par
\quad - b) Central Power Unit\par
\quad - c) Central Processing Utility\par

\textbf{Q15} Which algorithm is used for finding the minimum spanning tree of a graph?\par
\quad - a) Dijkstra's Algorithm\par
\quad - b) Kruskal's Algorithm\par
\quad - c) Prim's Algorithm\par

\textbf{Q16} What is the term for a type of malware that demands payment in exchange for restoring access to data?\par
\quad - a) Virus\par
\quad - b) Worm\par
\quad - c) Ransomware\par

\textbf{Q17} Which data structure is used for implementing recursion?\par
\quad - a) Stack\par
\quad - b) Queue\par
\quad - c) Tree\par

\textbf{Q18} What does "GUI" stand for in user interface design?\par
\quad - a) Graphical User Interface\par
\quad - b) General User Interface\par
\quad - c) Generic User Interface\par

\textbf{Q19} Which programming language is known for its use in machine learning and data science?\par
\quad - a) Python\par
\quad - b) R\par
\quad - c) Julia\par

\textbf{Q20} What is the term for the process of ensuring that data is accurate and consistent across a database?\par
\quad - a) Data Mining\par
\quad - b) Data Warehousing\par
\quad - c) Data Normalization\par

\textbf{Q21} Which algorithm is used for sorting data by dividing it into smaller sub-arrays?\par
\quad - a) Merge Sort\par
\quad - b) Quick Sort\par
\quad - c) Heap Sort\par

\textbf{Q22} What does "HTML" stand for in web development?\par
\quad - a) HyperText Markup Language\par
\quad - b) HyperText Management Language\par
\quad - c) HyperText Modeling Language\par

\textbf{Q23} Which device is used to connect multiple devices within a network?\par
\quad - a) Hub\par
\quad - b) Switch\par
\quad - c) Router\par

\textbf{Q24} What is the term for a type of network topology where all devices are connected to a central device?\par
\quad - a) Star Topology\par
\quad - b) Ring Topology\par
\quad - c) Bus Topology\par

\textbf{Q25} Which programming paradigm focuses on functions and their composition?\par
\quad - a) Object-Oriented Programming\par
\quad - b) Functional Programming\par
\quad - c) Procedural Programming\par

\textbf{Q26} What does "CSS" stand for in web development?\par
\quad - a) Cascading Style Sheets\par
\quad - b) Cascading Style Systems\par
\quad - c) Cascading Style Syntax\par

\textbf{Q27} Which algorithm is used for finding the maximum flow in a flow network?\par
\quad - a) Ford-Fulkerson Algorithm\par
\quad - b) Dijkstra's Algorithm\par
\quad - c) Bellman-Ford Algorithm\par

\textbf{Q28} What is the term for a type of malware that replicates itself?\par
\quad - a) Virus\par
\quad - b) Worm\par
\quad - c) Trojan\par

\textbf{Q29} Which data structure is used for efficient insertion and deletion of elements?\par
\quad - a) Array\par
\quad - b) Linked List\par
\quad - c) Stack\par

\textbf{Q30} What does "ISP" stand for in internet services?\par
\quad - a) Internet Service Provider\par
\quad - b) Internet Security Protocol\par
\quad - c) Internet Service Protocol\par

\textbf{Q31} Which programming language is known for its use in game development?\par
\quad - a) C++\par
\quad - b) Java\par
\quad - c) Python\par

\textbf{Q32} What is the term for a type of network attack where an attacker intercepts communication between two parties?\par
\quad - a) Man-in-the-Middle Attack\par
\quad - b) Denial-of-Service Attack\par
\quad - c) Phishing Attack\par

\textbf{Q33} Which algorithm is used for sorting data by repeatedly dividing it into smaller sub-arrays?\par
\quad - a) Quick Sort\par
\quad - b) Merge Sort\par
\quad - c) Heap Sort\par

\textbf{Q34} What does "VPN" stand for in network security?\par
\quad - a) Virtual Private Network\par
\quad - b) Virtual Public Network\par
\quad - c) Virtual Protected Network\par

\textbf{Q35} Which device is used to provide internet access to multiple devices?\par
\quad - a) Modem\par
\quad - b) Router\par
\quad - c) Switch\par

\textbf{Q36} What is the term for a type of database that stores data in tables?\par
\quad - a) Relational Database\par
\quad - b) NoSQL Database\par
\quad - c) Graph Database\par

\textbf{Q37} Which programming language is known for its use in web development frameworks like Ruby on Rails?\par
\quad - a) Ruby\par
\quad - b) Python\par
\quad - c) JavaScript\par

\textbf{Q38} What does "RAM" stand for in computer hardware?\par
\quad - a) Random Access Memory\par
\quad - b) Read-Only Memory\par
\quad - c) Read-Write Memory\par

\textbf{Q39} Which algorithm is used for finding the shortest path between two nodes in a weighted graph?\par
\quad - a) Dijkstra's Algorithm\par
\quad - b) Bellman-Ford Algorithm\par
\quad - c) Floyd-Warshall Algorithm\par

\textbf{Q40} What is the term for a type of malware that disguises itself as legitimate software?\par
\quad - a) Trojan\par
\quad - b) Virus\par
\quad - c) Worm\par

\textbf{Q41} Which data structure is used for implementing a queue?\par
\quad - a) Array\par
\quad - b) Linked List\par
\quad - c) Stack\par

\textbf{Q42} What does "DNS" stand for in network services?\par
\quad - a) Domain Name System\par
\quad - b) Domain Name Service\par
\quad - c) Domain Name Server\par

\textbf{Q43} Which programming language is known for its use in mobile app development?\par
\quad - a) Java\par
\quad - b) Swift\par
\quad - c) Kotlin\par

\textbf{Q44} What is the term for a type of network topology where devices are connected in a circular configuration?\par
\quad - a) Ring Topology\par
\quad - b) Star Topology\par
\quad - c) Bus Topology\par

\textbf{Q45} Which algorithm is used for sorting data by comparing adjacent elements?\par
\quad - a) Bubble Sort\par
\quad - b) Quick Sort\par
\quad - c) Merge Sort\par

\textbf{Q46} What does "HTTP" stand for in web protocols?\par
\quad - a) Hypertext Transfer Protocol\par
\quad - b) Hypertext Transmission Protocol\par
\quad - c) Hypertext Transfer Process\par

\textbf{Q47} Which device is used to convert digital signals into analog signals?\par
\quad - a) DAC (Digital-to-Analog Converter)\par
\quad - b) ADC (Analog-to-Digital Converter)\par
\quad - c) Modem\par

\textbf{Q48} What is the term for a type of database that stores data as key-value pairs?\par
\quad - a) Relational Database\par
\quad - b) NoSQL Database\par
\quad - c) Graph Database\par

\textbf{Q49} Which programming language is known for its use in system programming?\par
\quad - a) C\par
\quad - b) C++\par
\quad - c) Rust\par

\textbf{Q50} What does "FTP" stand for in file transfer protocols?\par
\quad - a) File Transfer Protocol\par
\quad - b) File Transmission Protocol\par
\quad - c) File Transfer Process\par