\section{ELECTRICAL AND ELECTRONICS ENGINEERING}

\textbf{Q1} Who is considered the father of electrical engineering?\par
\quad - a) Nikola Tesla\par
\quad - b) Michael Faraday\par
\quad - c) James Clerk Maxwell\par

\textbf{Q2} What is the unit of electrical resistance?\par
\quad - a) Volt\par
\quad - b) Ampere\par
\quad - c) Ohm\par

\textbf{Q3} What is the purpose of a transformer in electrical systems?\par
\quad - a) To convert AC to DC\par
\quad - b) To step up or step down voltage levels\par
\quad - c) To store electrical energy\par

\textbf{Q4} What law relates voltage, current, and resistance in a circuit?\par
\quad - a) Kirchhoff's Law\par
\quad - b) Faraday's Law\par
\quad - c) Ohm's Law\par

\textbf{Q5} The first successful electric power plant was built by Thomas Edison in 1882. What was its name?\par
\quad - a) Pearl Street Station\par
\quad - b) Niagara Power Plant\par
\quad - c) Edison Generating Station\par

\textbf{Q6} What is the primary function of a diode in an electrical circuit?\par
\quad - a) To amplify signals\par
\quad - b) To allow current to flow in one direction\par
\quad - c) To store energy\par

\textbf{Q7} What is the primary material used in the construction of semiconductors?\par
\quad - a) Copper\par
\quad - b) Silicon\par
\quad - c) Aluminum\par

\textbf{Q8} What is the principle behind the working of an electric motor?\par
\quad - a) Magnetic flux density\par
\quad - b) Electromagnetic induction\par
\quad - c) Electrostatic attraction\par

\textbf{Q9} Who discovered the principle of electromagnetic induction?\par
\quad - a) Nikola Tesla\par
\quad - b) Michael Faraday\par
\quad - c) Alessandro Volta\par

\textbf{Q10} What is the SI unit of electric charge?\par
\quad - a) Coulomb\par
\quad - b) Volt\par
\quad - c) Ampere\par

\textbf{Q11} What does the abbreviation "LED" stand for?\par
\quad - a) Light Emitting Diode\par
\quad - b) Light Energy Device\par
\quad - c) Linear Electric Display\par

\textbf{Q12} What type of current is produced by a typical battery?\par
\quad - a) Alternating Current (AC)\par
\quad - b) Direct Current (DC)\par
\quad - c) Pulsating Current\par

\textbf{Q13} What is the main advantage of using high voltage in power transmission?\par
\quad - a) Lower power loss\par
\quad - b) Faster transmission\par
\quad - c) Improved safety\par

\textbf{Q14} What is the main difference between a synchronous motor and an induction motor?\par
\quad - a) Operating speed\par
\quad - b) Magnetic field type\par
\quad - c) Rotor design\par

\textbf{Q15} Which of the following is an example of a renewable energy source used in electrical engineering?\par
\quad - a) Coal\par
\quad - b) Solar power\par
\quad - c) Natural gas\par

\textbf{Q16} What does "RMS" stand for in electrical engineering?\par
\quad - a) Root Mean Square\par
\quad - b) Residual Magnetic Strength\par
\quad - c) Reactive Magnetic Signal\par

\textbf{Q17} What is the primary function of a capacitor in an electrical circuit?\par
\quad - a) To resist current flow\par
\quad - b) To store and release energy\par
\quad - c) To amplify voltage\par

\textbf{Q18} What is the significance of the Maxwell equations in electrical engineering?\par
\quad - a) They describe the relationship between electricity and magnetism\par
\quad - b) They calculate energy loss in a circuit\par
\quad - c) They measure thermal conductivity in materials\par

\textbf{Q19} What is the name of the device that measures electric current?\par
\quad - a) Voltmeter\par
\quad - b) Ammeter\par
\quad - c) Ohmmeter\par

\textbf{Q20} What is a circuit breaker used for?\par
\quad - a) To store energy\par
\quad - b) To automatically stop current flow during overloads\par
\quad - c) To increase voltage\par

\textbf{Q21} What is the frequency of the AC power supply in most countries, including the US?\par
\quad - a) 50 Hz\par
\quad - b) 60 Hz\par
\quad - c) 100 Hz\par

\textbf{Q22} What is the primary component of a solar cell?\par
\quad - a) Silicon\par
\quad - b) Copper\par
\quad - c) Graphite\par

\textbf{Q23} Who developed the first practical alternating current (AC) generator?\par
\quad - a) Nikola Tesla\par
\quad - b) George Westinghouse\par
\quad - c) Michael Faraday\par

\textbf{Q24} What is the function of an inductor in an electrical circuit?\par
\quad - a) To block DC and pass AC\par
\quad - b) To convert voltage levels\par
\quad - c) To amplify electrical signals\par

\textbf{Q25} What does "THD" stand for in power systems?\par
\quad - a) Total Harmonic Distortion\par
\quad - b) Thermal Heat Dissipation\par
\quad - c) Transmission High Density\par

\textbf{Q26} What is the main advantage of using three-phase power over single-phase power?\par
\quad - a) Reduced voltage drop\par
\quad - b) Higher power delivery efficiency\par
\quad - c) Simpler installation\par

\textbf{Q27} What is the principle of operation of a rectifier?\par
\quad - a) Converting AC to DC\par
\quad - b) Converting DC to AC\par
\quad - c) Regulating voltage\par

\textbf{Q28} Which electrical component is often used for signal amplification?\par
\quad - a) Diode\par
\quad - b) Transistor\par
\quad - c) Resistor\par

\textbf{Q29} What is the purpose of grounding in electrical systems?\par
\quad - a) To ensure proper voltage levels\par
\quad - b) To protect against electrical shock and equipment damage\par
\quad - c) To improve circuit efficiency\par

\textbf{Q30} What is the term for the opposition to the flow of alternating current caused by capacitance or inductance?\par
\quad - a) Impedance\par
\quad - b) Resistance\par
\quad - c) Conductance\par

\textbf{Q31} What is the primary function of a fuse in an electrical circuit?\par
\quad - a) To amplify voltage\par
\quad - b) To protect against overcurrent conditions\par
\quad - c) To store energy\par

\textbf{Q32} Which type of semiconductor is used in power electronics?\par
\quad - a) P-type\par
\quad - b) N-type\par
\quad - c) Both P-type and N-type\par

\textbf{Q33} What is the term for the process of converting AC to DC?\par
\quad - a) Rectification\par
\quad - b) Amplification\par
\quad - c) Filtering\par

\textbf{Q34} What is the purpose of a thyristor in electrical systems?\par
\quad - a) To control voltage levels\par
\quad - b) To regulate current flow\par
\quad - c) To switch on/off high currents\par

\textbf{Q35} What is the principle behind the operation of a microwave oven?\par
\quad - a) Electromagnetic induction\par
\quad - b) Dielectric heating\par
\quad - c) Resistive heating\par

\textbf{Q36} What does "EMI" stand for in electrical engineering?\par
\quad - a) Electromagnetic Interference\par
\quad - b) Electronic Magnetic Interface\par
\quad - c) Energy Management Interface\par

\textbf{Q37} What is the function of a filter in an electrical circuit?\par
\quad - a) To amplify signals\par
\quad - b) To remove unwanted frequencies\par
\quad - c) To store energy\par

\textbf{Q38} Which device is used to measure electrical power?\par
\quad - a) Voltmeter\par
\quad - b) Ammeter\par
\quad - c) Wattmeter\par

\textbf{Q39} What is the term for the ratio of output power to input power in a system?\par
\quad - a) Efficiency\par
\quad - b) Effectiveness\par
\quad - c) Efficacy\par

\textbf{Q40} What is the primary material used in the construction of electrical wires?\par
\quad - a) Aluminum\par
\quad - b) Copper\par
\quad - c) Silver\par

\textbf{Q41} What is the purpose of a surge protector in electrical systems?\par
\quad - a) To regulate voltage levels\par
\quad - b) To protect against voltage spikes\par
\quad - c) To improve circuit efficiency\par

\textbf{Q42} What does "UPS" stand for in electrical engineering?\par
\quad - a) Uninterruptible Power Supply\par
\quad - b) Universal Power System\par
\quad - c) Utility Power Source\par

\textbf{Q43} What is the principle behind the operation of a DC generator?\par
\quad - a) Electromagnetic induction\par
\quad - b) Electrostatic attraction\par
\quad - c) Magnetic flux density\par

\textbf{Q44} What is the term for the opposition to current flow in a circuit?\par
\quad - a) Impedance\par
\quad - b) Resistance\par
\quad - c) Conductance\par

\textbf{Q45} What is the function of a relay in an electrical circuit?\par
\quad - a) To amplify signals\par
\quad - b) To control high currents with low currents\par
\quad - c) To store energy\par

\textbf{Q46} Which type of motor is commonly used in household appliances?\par
\quad - a) Induction motor\par
\quad - b) Synchronous motor\par
\quad - c) DC motor\par

\textbf{Q47} What is the purpose of a transformer in a power distribution system?\par
\quad - a) To convert AC to DC\par
\quad - b) To step up or step down voltage levels\par
\quad - c) To store electrical energy\par

\textbf{Q48} What does "SMPS" stand for in electrical engineering?\par
\quad - a) Switch Mode Power Supply\par
\quad - b) Static Magnetic Power Supply\par
\quad - c) Simple Modular Power Supply\par

\textbf{Q49} What is the principle behind the operation of a radio transmitter?\par
\quad - a) Electromagnetic induction\par
\quad - b) Electromagnetic radiation\par
\quad - c) Electrostatic attraction\par

\textbf{Q50} What is the term for the study of the behavior of electrons in materials?\par
\quad - a) Electronics\par
\quad - b) Electromagnetism\par
\quad - c) Solid-state physics\par