\section{HISTORY OF AI}

\textbf{Q1} Alan Turing, often called the "Father of AI," proposed the famous Turing Test in 1950. What was its purpose?\par
\quad - a) To measure a machine's processing speed\par
\quad - b) To determine if a machine could exhibit human-like intelligence\par
\quad - c) To test the efficiency of algorithms\par

\textbf{Q2} The term "Artificial Intelligence" was first coined at which significant event in 1956?\par
\quad - a) Dartmouth Conference\par
\quad - b) Turing Symposium\par
\quad - c) AI World Congress\par

\textbf{Q3} Who developed the first artificial neural network, SNARC, in 1951?\par
\quad - a) Marvin Minsky and Dean Edmonds\par
\quad - b) Alan Turing and Claude Shannon\par
\quad - c) John McCarthy and Herbert Simon\par

\textbf{Q4} What groundbreaking paper did Alan Turing publish in 1950 that laid the foundation for AI?\par
\quad - a) "Computing Machinery and Intelligence"\par
\quad - b) "The Theory of Computation"\par
\quad - c) "Cybernetics and Machine Learning"\par

\textbf{Q5} In 1961, General Motors introduced Unimate, the first industrial robot. What was its primary function?\par
\quad - a) Painting cars\par
\quad - b) Welding and transporting die castings on assembly lines\par
\quad - c) Assembling electronic components\par

\textbf{Q6} What was ELIZA, developed by Joseph Weizenbaum in 1966, primarily designed to do?\par
\quad - a) Play chess against humans\par
\quad - b) Simulate human conversation as a psychotherapist chatbot\par
\quad - c) Perform mathematical computations\par

\textbf{Q7} Shakey, developed in the 1960s, is considered the first general‑purpose mobile robot. What made it unique?\par
\quad - a) It could reason about its actions and navigate autonomously\par
\quad - b) It could perform complex surgeries\par
\quad - c) It was powered by artificial neural networks\par

\textbf{Q8} The Dartmouth Conference of 1956 is considered the birth of AI as an academic field. Who led this conference?\par
\quad - a) John McCarthy, Marvin Minsky, Nathaniel Rochester, and Claude Shannon\par
\quad - b) Alan Turing and Warren McCulloch\par
\quad - c) Edward Feigenbaum and Herbert Simon\par

\textbf{Q9} Why did the AI community experience an "AI Winter" during the 1970s and 1980s?\par
\quad - a) Lack of interest from researchers due to better opportunities elsewhere\par
\quad - b) Overpromised results that failed to materialize, leading to reduced funding and skepticism\par
\quad - c) Legal restrictions on AI development\par

\textbf{Q10} Which programming language, developed by John McCarthy in 1958, became foundational for AI research?\par
\quad - a) Python\par
\quad - b) Lisp\par
\quad - c) FORTRAN\par

\textbf{Q11} In 1997, IBM's Deep Blue defeated world chess champion Garry Kasparov. Why was this event significant?\par
\quad - a) It marked the first time AI defeated a human in a strategic game at the highest level\par
\quad - b) It demonstrated AI's ability to learn from its mistakes during gameplay\par
\quad - c) It used neural networks for decision‑making\par

\textbf{Q12} What is considered one of the earliest examples of machine learning in practice?\par
\quad - a) Arthur Samuel's checkers‑playing program in 1952 that could learn independently\par
\quad - b) IBM Watson's question‑answering system in 2011\par
\quad - c) Google's AlphaGo defeating human players\par

\textbf{Q13} The development of expert systems like MYCIN in the 1970s aimed to achieve what goal?\par
\quad - a) Diagnose diseases using knowledge‑based reasoning\par
\quad - b) Play games like chess at an expert level\par
\quad - c) Automate factory processes\par

\textbf{Q14} What was James Lighthill's criticism of AI research in his famous 1973 report to the British Science Council?\par
\quad - a) AI research had failed to deliver practical applications\par
\quad - b) AI systems were too expensive to develop\par
\quad - c) Neural networks were unreliable\par

\textbf{Q15} Which philosopher's work on logic and reasoning influenced early ideas about machine intelligence as far back as antiquity?\par
\quad - a) Aristotle\par
\quad - b) René Descartes\par
\quad - c) Immanuel Kant\par

\textbf{Q16} The Perceptron, an early neural network model developed by Frank Rosenblatt in 1958, was designed to perform what task?\par
\quad - a) Recognize patterns in visual data\par
\quad - b) Simulate human conversation\par
\quad - c) Solve mathematical equations\par

\textbf{Q17} What major advancement occurred in AI during the 1980s that reignited interest after the "AI Winter"?\par
\quad - a) Development of expert systems for real‑world applications\par
\quad - b) Introduction of generative adversarial networks (GANs)\par
\quad - c) Creation of humanoid robots capable of emotion recognition\par

\textbf{Q18} Why is Norbert Wiener's work on cybernetics considered foundational for modern AI?\par
\quad - a) He introduced feedback loops for control systems that inspired machine learning models\par
\quad - b) He created the first computer capable of reasoning logically\par
\quad - c) He developed algorithms for natural language processing\par

\textbf{Q19} In what year did Alan Turing propose his theoretical concept of "machine intelligence"?\par
\quad - a) 1943\par
\quad - b) 1950\par
\quad - c) 1965\par

\textbf{Q20} The Japanese Fifth Generation Computer Systems project (1982‑1992) focused primarily on:\par
\quad - a) Developing parallel computing systems and logic programming languages like Prolog\par
\quad - b) Building humanoid robots for industrial use\par
\quad - c) Creating neural networks capable of deep learning\par

\textbf{Q21} What was the primary contribution of AI pioneer John McCarthy to the field?\par
\quad - a) Developing the Lisp programming language\par
\quad - b) Creating the first AI‑powered robot\par
\quad - c) Proposing the concept of machine learning\par

\textbf{Q22} The first AI program, Logical Theorist, was developed by whom in 1956?\par
\quad - a) Allen Newell and Herbert Simon\par
\quad - b) Marvin Minsky and Seymour Papert\par
\quad - c) John McCarthy and Nathaniel Rochester\par

\textbf{Q23} What was the main goal of the Logical Theorist program?\par
\quad - a) To solve logical problems using reasoning\par
\quad - b) To recognize visual patterns\par
\quad - c) To simulate human conversation\par

\textbf{Q24} Which AI system, developed in the 1970s, was designed to diagnose bacterial infections?\par
\quad - a) MYCIN\par
\quad - b) DENDRAL\par
\quad - c) ELIZA\par

\textbf{Q25} What was the primary function of the DENDRAL expert system developed in the 1960s?\par
\quad - a) Diagnose diseases\par
\quad - b) Identify organic compounds\par
\quad - c) Play chess\par

\textbf{Q26} The AI Winter occurred due to which of the following reasons?\par
\quad - a) Lack of funding\par
\quad - b) Overpromised results that failed to materialize\par
\quad - c) Technological limitations\par

\textbf{Q27} Who is credited with developing the first computer game, "Tic‑Tac‑Toe," in 1951?\par
\quad - a) Alan Turing\par
\quad - b) Alexander Douglas\par
\quad - c) Marvin Minsky\par

\textbf{Q28} What was the main contribution of AI pioneer Marvin Minsky to the field?\par
\quad - a) Developing the first neural network\par
\quad - b) Creating the first AI‑powered robot\par
\quad - c) Proposing the concept of machine learning\par

\textbf{Q29} The first AI‑powered robot, Shakey, was developed at which institution?\par
\quad - a) Stanford Research Institute (SRI)\par
\quad - b) Massachusetts Institute of Technology (MIT)\par
\quad - c) Carnegie Mellon University\par

\textbf{Q30} What was the primary goal of the Shakey robot project?\par
\quad - a) Create a humanoid robot\par
\quad - b) Develop a robot that could reason and navigate autonomously\par
\quad - c) Build a robot for industrial use\par

\textbf{Q31} Which philosopher's work on logic and reasoning influenced early ideas about machine intelligence?\par
\quad - a) Aristotle\par
\quad - b) René Descartes\par
\quad - c) Immanuel Kant\par

\textbf{Q32} The Perceptron, developed by Frank Rosenblatt, was an early model of what type of AI system?\par
\quad - a) Neural Network\par
\quad - b) Expert System\par
\quad - c) Decision Tree\par

\textbf{Q33} What was the main limitation of the Perceptron model?\par
\quad - a) It could not recognize patterns in visual data\par
\quad - b) It could not learn from its mistakes\par
\quad - c) It could not handle complex problems due to the XOR problem\par

\textbf{Q34} Who introduced the concept of the "AI Winter"?\par
\quad - a) Marvin Minsky\par
\quad - b) John McCarthy\par
\quad - c) James Lighthill\par

\textbf{Q35} What was the impact of the "AI Winter" on AI research?\par
\quad - a) Increased funding and interest\par
\quad - b) Reduced funding and skepticism\par
\quad - c) No significant impact on AI research\par

\textbf{Q36} The Japanese Fifth Generation Computer Systems project aimed to develop what type of computing systems?\par
\quad - a) Parallel computing systems\par
\quad - b) Neural network‑based systems\par
\quad - c) Expert systems for real‑world applications\par

\textbf{Q37} What was the primary goal of the Japanese Fifth Generation Computer Systems project?\par
\quad - a) Develop AI systems for industrial use\par
\quad - b) Create expert systems for real‑world applications\par
\quad - c) Build humanoid robots\par

\textbf{Q38} Who developed the first expert system, DENDRAL, in AI?\par
\quad - a) Edward Feigenbaum and Joshua Lederberg\par
\quad - b) Marvin Minsky and Seymour Papert\par
\quad - c) Allen Newell and Herbert Simon\par

\textbf{Q39} What was the main contribution of the DENDRAL expert system?\par
\quad - a) Diagnose diseases\par
\quad - b) Identify organic compounds\par
\quad - c) Play chess\par

\textbf{Q40} Which AI pioneer is credited with coining the term "Artificial Intelligence"?\par
\quad - a) John McCarthy\par
\quad - b) Marvin Minsky\par
\quad - c) Alan Turing\par