\section{HONORS}

\textbf{Q1} Which esteemed scientific accolade is often referred to as the "Nobel Prize for young researchers"?\par
\quad - a) Fields Medal\par
\quad - b) Breakthrough Prize\par
\quad - c) L'Oréal‑UNESCO For Women in Science Awards\par

\textbf{Q2} Which award is solely dedicated to achievements in theoretical physics?\par
\quad - a) Fundamental Physics Prize\par
\quad - b) Breakthrough Prize in Life Sciences\par
\quad - c) Draper Prize\par

\textbf{Q3} What distinction is given each year by the Royal Swedish Academy of Sciences for remarkable accomplishments in science?\par
\quad - a) Abel Prize\par
\quad - b) Wolf Prize\par
\quad - c) Nobel Prize\par

\textbf{Q4} The Abel Prize, a significant award in mathematics, is named after which renowned mathematician?\par
\quad - a) Carl Friedrich Gauss\par
\quad - b) Niels Henrik Abel\par
\quad - c) Srinivasa Ramanujan\par

\textbf{Q5} Which award acknowledges advancements in public health and is regarded as one of the most important in this domain?\par
\quad - a) Albert Lasker Award\par
\quad - b) Shaw Prize\par
\quad - c) Breakthrough Prize in Public Health\par

\textbf{Q6} The Turing Award—"Nobel Prize of Computing"—is conferred by which organization?\par
\quad - a) Association for Computing Machinery (ACM)\par
\quad - b) IEEE\par
\quad - c) International Computer Science Organization (ICSO)\par

\textbf{Q7} Which prize was founded by Israeli scientists to honor global excellence in science and mathematics?\par
\quad - a) Wolf Prize\par
\quad - b) Weizmann Medal\par
\quad - c) Negev Science Award\par

\textbf{Q8} The Shaw Prize—often called the "Nobel Prize of Asia"—focuses on which areas?\par
\quad - a) Space exploration\par
\quad - b) Astronomy, life science & mathematics\par
\quad - c) Environmental science\par

\textbf{Q9} What sets the Fields Medal apart from other mathematics awards?\par
\quad - a) Presented biennially\par
\quad - b) Recipients must be under 40\par
\quad - c) Focus on applied mathematics only\par

\textbf{Q10} Which distinction recognises pioneering progress in biochemistry or molecular biology?\par
\quad - a) Breakthrough Prize in Life Sciences\par
\quad - b) Keilin Medal\par
\quad - c) Wolf Prize\par

\textbf{Q11} The Breakthrough Prize was established by entrepreneurs from which sectors?\par
\quad - a) Technology & film\par
\quad - b) Real estate & banking\par
\quad - c) Biotech & pharmaceuticals\par

\textbf{Q12} Which award recognises significant contributions to statistics?\par
\quad - a) Chern Medal\par
\quad - b) R.A. Fisher Award\par
\quad - c) George Box Medal\par

\textbf{Q13} The Crafoord Prize complements the Nobel Prizes by covering which fields?\par
\quad - a) Space & earth sciences\par
\quad - b) Arts & humanities\par
\quad - c) Biophysics & chemistry\par

\textbf{Q14} The Draper Prize honours advancements in which engineering areas?\par
\quad - a) Space exploration & robotics\par
\quad - b) All branches of engineering\par
\quad - c) Civil & structural engineering\par

\textbf{Q15} Which accolade celebrates noteworthy contributions to public understanding of science?\par
\quad - a) Michael Faraday Prize\par
\quad - b) UNESCO Kalinga Prize\par
\quad - c) Richard Dawkins Award\par

\textbf{Q16} The Kavli Prizes are awarded in which three disciplines?\par
\quad - a) Neuroscience, nanoscience & astronomy\par
\quad - b) Quantum physics, life sciences & chemistry\par
\quad - c) Climate science, genetics & mathematics\par

\textbf{Q17} Which global accolade for science & innovation is overseen by the European Patent Office?\par
\quad - a) Millennium Technology Prize\par
\quad - b) European Inventor Award\par
\quad - c) Breakthrough Patent Honor\par

\textbf{Q18} What is the primary goal of the Millennium Technology Prize?\par
\quad - a) Showcase innovations with wide societal impact\par
\quad - b) Recognize theoretical physics advances\par
\quad - c) Honour lifetime tech achievements\par

\textbf{Q19} The Kyoto Prize acknowledges contributions in…\par
\quad - a) Technology, philosophy & arts\par
\quad - b) Technology, applied sciences & literature\par
\quad - c) Basic sciences, arts & human progress\par

\textbf{Q20} Since its establishment, the Wolf Prize has been awarded in which fields?\par
\quad - a) Chemistry, physics, medicine & arts\par
\quad - b) Physics, mathematics, social sciences & music\par
\quad - c) Medicine, agriculture & mathematics\par

\textbf{Q21} The Blue Planet Prize honours work in…\par
\quad - a) Sustainable development\par
\quad - b) Conservation biology\par
\quad - c) Renewable energy\par

\textbf{Q22} Which award is given alongside the Nobels but focuses on peace efforts?\par
\quad - a) Right Livelihood Award\par
\quad - b) Pritzker Prize\par
\quad - c) Stockholm Peace Prize\par

\textbf{Q23} Which Royal Society medal honours achievements in biological sciences?\par
\quad - a) Darwin Medal\par
\quad - b) Copley Medal\par
\quad - c) Sylvester Medal\par

\textbf{Q24} Frances Arnold received which 2018 honour for directed enzyme evolution?\par
\quad - a) Nobel Prize in Chemistry\par
\quad - b) National Medal of Science\par
\quad - c) Priestley Medal\par

\textbf{Q25} Established in 1969, which prize recognises achievements in architecture?\par
\quad - a) Stirling Prize\par
\quad - b) Pritzker Architecture Prize\par
\quad - c) Aga Khan Award for Architecture\par

\textbf{Q26} The Holberg Prize is awarded annually for outstanding work in…\par
\quad - a) Mathematics & computer science\par
\quad - b) Arts & humanities, social sciences, law & theology\par
\quad - c) Physics & chemistry\par

\textbf{Q27} Which NAS award honours climate‑change research?\par
\quad - a) Tyler Prize for Environmental Achievement\par
\quad - b) BBVA Foundation Frontiers of Knowledge (Climate Change)\par
\quad - c) Stephen Schneider Climate Science Communications Award\par

\textbf{Q28} Which major award, named after an African‑American physician, recognises biomedical research contributions?\par
\quad - a) Canada Gairdner International Award\par
\quad - b) Dr Charles Drew World Prize in Biomedicine\par
\quad - c) Lasker Award\par

\textbf{Q29} The Dickson Prize in Science is awarded annually by…\par
\quad - a) Caltech\par
\quad - b) Carnegie Mellon University\par
\quad - c) Harvard University\par

\textbf{Q30} The U.S. National Medal of Technology & Innovation recognises exceptional achievement in…\par
\quad - a) Enhancing U.S. competitiveness\par
\quad - b) Basic science research\par
\quad - c) Creative arts\par

\textbf{Q31} Which prize honours efforts to reduce disease suffering?\par
\quad - a) Gates Foundation Global Health Award\par
\quad - b) Roux Prize\par
\quad - c) Kochon Prize\par

\textbf{Q32} Named after a pioneering aviator, which prize recognises aerospace‑engineering contributions?\par
\quad - a) Amelia Earhart Fellowship Awards\par
\quad - b) Wright Brothers Medal\par
\quad - c) Daniel Guggenheim Medal\par

\textbf{Q33} Which prize rewards environmentally sustainable innovation with economic & social impact?\par
\quad - a) Earthshot Prize\par
\quad - b) Environmental Prize\par
\quad - c) Green Tech Award\par

\textbf{Q34} The Bower Award and Prize for Achievement in Science is presented by…\par
\quad - a) MIT\par
\quad - b) The Franklin Institute\par
\quad - c) UC Berkeley\par

\textbf{Q35} Which APS prize honours theoretical & mathematical physics breakthroughs?\par
\quad - a) Dannie Heineman Prize for Mathematical Physics\par
\quad - b) Dirac Medal\par
\quad - c) Boltzmann Medal\par

\textbf{Q36} Which prize honours innovations delivering sustainable water solutions?\par
\quad - a) Stockholm Water Prize\par
\quad - b) Lee Kuan Yew Water Prize\par
\quad - c) Prince Albert II Water Award\par

\textbf{Q37} The "integration of knowledge" award recognising cross‑disciplinary science is…\par
\quad - a) Golden Goose Award\par
\quad - b) John Maddox Prize\par
\quad - c) BBVA Foundation Frontiers of Knowledge Award\par

\textbf{Q38} Often called the "Environmental Nobel," which prize honours environmental protection efforts?\par
\quad - a) Goldman Environmental Prize\par
\quad - b) Blue Planet Prize\par
\quad - c) Tyler Prize for Environmental Achievement\par

\textbf{Q39} Which literary award honours the best science/nature writing in the UK annually?\par
\quad - a) Royal Society Science Book Prize\par
\quad - b) PEN/E.O. Wilson Literary Science Award\par
\quad - c) National Book Award for Science & Literature\par

\textbf{Q40} Which NSS award recognises civil space achievements?\par
\quad - a) Space Pioneer Award\par
\quad - b) Robert A. Heinlein Award\par
\quad - c) Space Achievement Award\par

\textbf{Q41} Which award celebrates interdisciplinary work solving global development challenges?\par
\quad - a) Keeling Curve Prize\par
\quad - b) Zayed Sustainability Prize\par
\quad - c) Nestlé Creating Shared Value Prize\par

\textbf{Q42} Which science honour (VinFuture Prize) aims to solve world challenges by rewarding top work globally. Which option best describes it?\par
\quad - a) VinFuture Prize\par
\quad - b) Global Grand Challenges\par
\quad - c) Prince Mahidol Award\par

\textbf{Q43} Which award recognises long‑term scientific contributions advancing knowledge?\par
\quad - a) Dickson Prize in Medicine\par
\quad - b) Benjamin Franklin Medal\par
\quad - c) Shaw Prize\par

\textbf{Q44} Which TWAS award honours developing‑country scientists?\par
\quad - a) Kuwait Prize\par
\quad - b) TWAS Prize\par
\quad - c) Obada Prize\par

\textbf{Q45} Which 1983‑established award recognises excellence in marine biology?\par
\quad - a) A.G. Huntsman Award\par
\quad - b) Ramón Margalef Prize\par
\quad - c) Japan Prize\par

\textbf{Q46} Which prize—"Nobel Prize of Computing"—honours computer‑science contributions?\par
\quad - a) Turing Award\par
\quad - b) Kyoto Prize\par
\quad - c) Lovelace Medal\par

\textbf{Q47} What is the most prestigious honour from the American Chemical Society?\par
\quad - a) Priestley Medal\par
\quad - b) Irving Langmuir Award\par
\quad - c) Nichols Medal\par

\textbf{Q48} The Nevanlinna Prize (every 4 years) is awarded for…\par
\quad - a) Physics\par
\quad - b) Mathematics\par
\quad - c) Information technology\par

\textbf{Q49} Which IEEE award honours electrical/computer engineering contributions?\par
\quad - a) Edison Medal\par
\quad - b) Faraday Medal\par
\quad - c) James Clerk Maxwell Medal\par

\textbf{Q50} Which Paleontological Society prize recognises paleontology achievements annually?\par
\quad - a) Romer‑Simpson Medal\par
\quad - b) Mary Anning Award\par
\quad - c) G.G. Simpson Prize\par