\section{INDIA'S CONTRIBUTION TO ENGINEERING}

\textbf{Q1} When is Engineers' Day celebrated in India?\par
\quad - a) September 13\par
\quad - b) September 14\par
\quad - c) September 15\par

\textbf{Q2} Engineers' Day in India celebrates the birth anniversary of which famous engineer?\par
\quad - a) Mokshagundam Visvesvaraya\par
\quad - b) Jawaharlal Nehru\par
\quad - c) APJ Abdul Kalam\par

\textbf{Q3} Who is often referred to as the "Father of the Indian Space Program"?\par
\quad - a) C. V. Raman\par
\quad - b) Vikram Sarabhai\par
\quad - c) Homi J. Bhabha\par

\textbf{Q4} Which Indian engineer is known for designing the iconic Qutub Minar in Delhi?\par
\quad - a) Vishwakarma\par
\quad - b) Raja Raja Chola\par
\quad - c) Ustad Ahmad Lahori\par

\textbf{Q5} The famous Indian engineer Mokshagundam Visvesvaraya is best known for his contributions to which sector?\par
\quad - a) Space Technology\par
\quad - b) Civil Engineering\par
\quad - c) Information Technology\par

\textbf{Q6} Who was the chief architect behind the design and construction of the Amritsar Golden Temple (Harmandir Sahib)?\par
\quad - a) Le Corbusier\par
\quad - b) Guru Ram Das\par
\quad - c) Sir Edwin Lutyens\par

\textbf{Q7} Which Indian engineer is responsible for the design and construction of the Statue of Unity, the world's tallest statue?\par
\quad - a) E. Sreedharan\par
\quad - b) A. P. J. Abdul Kalam\par
\quad - c) Sardar Patel\par

\textbf{Q8} Who is often called the "Missile Man of India" for his contributions to the Indian defence and space programs?\par
\quad - a) Homi J. Bhabha\par
\quad - b) Satish Dhawan\par
\quad - c) A. P. J. Abdul Kalam\par

\textbf{Q9} Which Indian engineer pioneered the development of the indigenous light combat aircraft, Tejas?\par
\quad - a) Raghuram Rajan\par
\quad - b) G. Madhavan Nair\par
\quad - c) Dr. Kota Harinarayana\par

\textbf{Q10} Who is known as the "Metro Man of India" for his work on the Delhi Metro and other metro projects?\par
\quad - a) E. Sreedharan\par
\quad - b) Vikram Sarabhai\par
\quad - c) Mokshagundam Visvesvaraya\par

\textbf{Q11} What prestigious award was Mokshagundam Visvesvaraya honored with that is considered India's highest civilian award?\par
\quad - a) Padma Vibhushan\par
\quad - b) Bharat Ratna\par
\quad - c) Padma Bhushan\par

\textbf{Q12} Which dam in India was built under the guidance of Sir Mokshagundam Visvesvaraya?\par
\quad - a) Krishna Raja Sagara (KRS) Dam\par
\quad - b) Bhakra Nangal Dam\par
\quad - c) Tehri Dam\par

\textbf{Q13} Who developed India's first indigenous supercomputer, PARAM?\par
\quad - a) Vijay Bhatkar\par
\quad - b) Sam Pitroda\par
\quad - c) F. C. Kohli\par

\textbf{Q14} Which Indian engineer is credited with developing the Pentium processor while working at Intel?\par
\quad - a) Ajay Bhatt\par
\quad - b) Vinod Dham\par
\quad - c) Thomas Kurian\par

\textbf{Q15} Who is considered the "Father of Indian Industry"?\par
\quad - a) Jamsetji Tata\par
\quad - b) G. D. Birla\par
\quad - c) Dhirubhai Ambani\par

\textbf{Q16} Which female Indian engineer is known as the "Missile Woman of India"?\par
\quad - a) Tessy Thomas\par
\quad - b) Kalpana Chawla\par
\quad - c) Ritu Karidhal\par

\textbf{Q17} Which ancient Indian engineering marvel is famous for its corrosion‑resistant iron pillar?\par
\quad - a) Iron Pillar of Delhi\par
\quad - b) Sun Temple of Konark\par
\quad - c) Brihadeshwara Temple\par

\textbf{Q18} Which Indian engineer led the team that designed and built India's first satellite, Aryabhata?\par
\quad - a) U. R. Rao\par
\quad - b) Satish Dhawan\par
\quad - c) K. Kasturirangan\par

\textbf{Q19} Which ancient Indian civilization is known for its advanced urban planning and engineering?\par
\quad - a) Indus Valley Civilization\par
\quad - b) Mauryan Empire\par
\quad - c) Gupta Empire\par

\textbf{Q20} Who is credited with developing India's civilian nuclear program?\par
\quad - a) Homi J. Bhabha\par
\quad - b) Raja Ramanna\par
\quad - c) A. P. J. Abdul Kalam\par

\textbf{Q21} Which Indian engineer led the Mars Orbiter Mission (Mangalyaan) project?\par
\quad - a) K. Radhakrishnan\par
\quad - b) Mylswamy Annadurai\par
\quad - c) K. Sivan\par

\textbf{Q22} India's first indigenous automotive engine, the Revtron, was developed by which company?\par
\quad - a) Tata Motors\par
\quad - b) Mahindra & Mahindra\par
\quad - c) Maruti Suzuki\par

\textbf{Q23} Which ancient irrigation system from Tamil Nadu is still in use and is considered one of the oldest water management systems in the world?\par
\quad - a) Grand Anicut (Kallanai)\par
\quad - b) Suranga System\par
\quad - c) Kunds of Rajasthan\par

\textbf{Q24} Who is known for establishing the Indian Institute of Science (IISc) in Bangalore?\par
\quad - a) Jamsetji Tata\par
\quad - b) Mokshagundam Visvesvaraya\par
\quad - c) C. V. Raman\par

\textbf{Q25} Which Indian engineer is considered the pioneer of wireless communication?\par
\quad - a) Jagadish Chandra Bose\par
\quad - b) G. N. Ramachandran\par
\quad - c) Satyendra Nath Bose\par

\textbf{Q26} Which Indian engineer contributed to the invention of fiber optics?\par
\quad - a) Narinder Singh Kapany\par
\quad - b) C. K. N. Patel\par
\quad - c) Amar Bose\par

\textbf{Q27} Who led India's first nuclear test, Operation Smiling Buddha, in 1974?\par
\quad - a) Raja Ramanna\par
\quad - b) Homi J. Bhabha\par
\quad - c) Vikram Sarabhai\par

\textbf{Q28} Which indigenous Indian combat helicopter is named after a venomous snake?\par
\quad - a) Light Combat Helicopter\par
\quad - b) Advanced Light Helicopter\par
\quad - c) Dhruv\par

\textbf{Q29} Which dam in India is the highest gravity dam?\par
\quad - a) Bhakra Nangal Dam\par
\quad - b) Tehri Dam\par
\quad - c) Sardar Sarovar Dam\par

\textbf{Q30} Who is known for developing India's Electronic Voting Machine (EVM) system?\par
\quad - a) M. Natarajan\par
\quad - b) Sam Pitroda\par
\quad - c) T. N. Seshan\par

\textbf{Q31} Which Indian engineering achievement is the world's tallest railway bridge?\par
\quad - a) Chenab Bridge\par
\quad - b) Pamban Bridge\par
\quad - c) Bogibeel Bridge\par

\textbf{Q32} Which Indian‑born engineer is the inventor of the USB (Universal Serial Bus)?\par
\quad - a) Ajay Bhatt\par
\quad - b) Vinod Dham\par
\quad - c) Sabeer Bhatia\par

\textbf{Q33} Which structure, designed by an Indian engineer, has the world's largest single‑span stone dome?\par
\quad - a) Gol Gumbaz in Bijapur\par
\quad - b) Bibi Ka Maqbara in Aurangabad\par
\quad - c) Taj Mahal in Agra\par

\textbf{Q34} Who established the first engineering college in India?\par
\quad - a) Lord Dalhousie\par
\quad - b) James Thomason\par
\quad - c) Lord Macaulay\par

\textbf{Q35} Which Indian engineer is known for designing the structural framework of the Howrah Bridge?\par
\quad - a) Rendel Palmer & Tritton\par
\quad - b) Sir Bradford Leslie\par
\quad - c) Sir Rajendra Nath Mookerjee\par

\textbf{Q36} Which indigenous Indian tactical surface‑to‑surface missile has a range of over 5000 km?\par
\quad - a) Agni‑V\par
\quad - b) Prithvi\par
\quad - c) BrahMos\par

\textbf{Q37} Who developed India's first indigenous microprocessor, Shakti?\par
\quad - a) IIT Madras researchers\par
\quad - b) DRDO scientists\par
\quad - c) ISRO engineers\par

\textbf{Q38} Which ancient engineering marvel in India features perfect acoustics where a sound made at a specific spot can be heard throughout the structure?\par
\quad - a) Golconda Fort\par
\quad - b) Gol Gumbaz\par
\quad - c) Ranakpur Temple\par

\textbf{Q39} Which Indian transportation engineering project is the longest expressway in India?\par
\quad - a) Yamuna Expressway\par
\quad - b) Mumbai‑Pune Expressway\par
\quad - c) Delhi‑Mumbai Expressway\par

\textbf{Q40} Which indigenous Indian naval ship was the first aircraft carrier built in India?\par
\quad - a) INS Vikramaditya\par
\quad - b) INS Vikrant\par
\quad - c) INS Viraat\par

\textbf{Q41} Who established the first formal silk manufacturing industry in India?\par
\quad - a) Tipu Sultan\par
\quad - b) Jamsetji Tata\par
\quad - c) G. D. Birla\par

\textbf{Q42} Which Indian scientist‑engineer is known for developing the first operational Indian parallel supercomputer?\par
\quad - a) Vijay Bhatkar\par
\quad - b) Sam Pitroda\par
\quad - c) Faqir Chand Kohli\par

\textbf{Q43} Which ancient Indian mathematical text contains early engineering principles?\par
\quad - a) Sulba Sutras\par
\quad - b) Aryabhatiya\par
\quad - c) Lilavati\par

\textbf{Q44} Which Indian structure is known for its earthquake‑resistant design despite being built in the 13th century?\par
\quad - a) Sun Temple at Konark\par
\quad - b) Qutub Minar\par
\quad - c) Khajuraho Temples\par

\textbf{Q45} Which Indian spacecraft was the first to successfully enter Mars orbit on its first attempt?\par
\quad - a) Chandrayaan‑1\par
\quad - b) Mangalyaan\par
\quad - c) Chandrayaan‑2\par

\textbf{Q46} Which Indian institute was established first with the focus on engineering education?\par
\quad - a) IIT Kharagpur\par
\quad - b) IIT Bombay\par
\quad - c) IIT Madras\par

\textbf{Q47} Which Indian mathematician‑engineer is known for his contributions to algebra and trigonometry that later influenced engineering?\par
\quad - a) Aryabhata\par
\quad - b) Brahmagupta\par
\quad - c) Bhaskara II\par

\textbf{Q48} Which indigenous Indian missile defense system was developed to intercept ballistic missiles?\par
\quad - a) Advanced Air Defence (AAD)\par
\quad - b) Akash Missile System\par
\quad - c) Nag Missile\par

\textbf{Q49} Which ancient Indian university had extensive engineering studies as part of its curriculum?\par
\quad - a) Nalanda University\par
\quad - b) Takshashila University\par
\quad - c) Vikramashila University\par

\textbf{Q50} Who designed the Indian Parliament House in New Delhi?\par
\quad - a) Edwin Lutyens\par
\quad - b) Herbert Baker\par
\quad - c) Charles Correa\par