\section{INDIA'S CONTRIBUTION TO SCIENCE}

\textbf{Q1} What ancient Indian mathematician is credited with inventing the concept of zero, revolutionizing arithmetic and mathematics?\par
\quad - a) Aryabhata\par
\quad - b) Srinivasa Ramanujan\par
\quad - c) Brahmagupta\par

\textbf{Q2} Which Indian scientist discovered the Raman effect, a phenomenon that explains how light interacts with molecules?\par
\quad - a) C.V. Raman\par
\quad - b) Satyendra Nath Bose\par
\quad - c) Homi J. Bhabha\par

\textbf{Q3} Who is known for his contributions to quantum mechanics, particularly the Bose‑Einstein statistics?\par
\quad - a) Satyendra Nath Bose\par
\quad - b) Srinivasa Ramanujan\par
\quad - c) Meghnad Saha\par

\textbf{Q4} Which Indian scientist played a crucial role in developing India's first satellite launch vehicle?\par
\quad - a) A.P.J. Abdul Kalam\par
\quad - b) Vikram Sarabhai\par
\quad - c) Homi J. Bhabha\par

\textbf{Q5} What is the name of the equation developed by Meghnad Saha to describe chemical and physical conditions in stars?\par
\quad - a) Saha Ionization Equation\par
\quad - b) Bose‑Einstein Equation\par
\quad - c) Raman Equation\par

\textbf{Q6} Who is credited with pioneering systematic bird surveys in India and abroad?\par
\quad - a) Salim Ali\par
\quad - b) Srinivasa Ramanujan\par
\quad - c) C.V. Raman\par

\textbf{Q7} Which ancient Indian contribution revolutionized mathematics by providing a simple method for expressing numbers?\par
\quad - a) Decimal System\par
\quad - b) Binary System\par
\quad - c) Hexadecimal System\par

\textbf{Q8} Who founded the Bhabha Atomic Research Centre and led India's nuclear program?\par
\quad - a) Homi J. Bhabha\par
\quad - b) Vikram Sarabhai\par
\quad - c) A.P.J. Abdul Kalam\par

\textbf{Q9} What is the name of the compound synthesized by Sir Upendranath Brahmachari to treat kala‑azar?\par
\quad - a) Urea Stibamine\par
\quad - b) Carbostibamide\par
\quad - c) Both A and B\par

\textbf{Q10} Which Indian scientist made significant contributions to algebraic geometry?\par
\quad - a) S.S. Abhyankar\par
\quad - b) Srinivasa Ramanujan\par
\quad - c) Satyendra Nath Bose\par

\textbf{Q11} What is the name of the technique used in ancient India for producing high‑quality steel?\par
\quad - a) Wootz Steel Production\par
\quad - b) Damascus Steel Production\par
\quad - c) Stainless Steel Production\par

\textbf{Q12} Who is known for his work in artificial intelligence and technology?\par
\quad - a) Raj Reddy\par
\quad - b) Srinivasa Ramanujan\par
\quad - c) C.V. Raman\par

\textbf{Q13} Which Indian scientist was involved in the discovery of the cholera toxin?\par
\quad - a) Sambhu Nath De\par
\quad - b) Upendranath Brahmachari\par
\quad - c) Homi J. Bhabha\par

\textbf{Q14} What is the name of the first successful in vitro fertilization in India, which resulted in the birth of a 'test tube baby'?\par
\quad - a) Durga\par
\quad - b) Louise Brown\par
\quad - c) Shanti\par

\textbf{Q15} Who developed the cervical cerclage procedure in obstetrics?\par
\quad - a) V.N. Shirodkar\par
\quad - b) Sambhu Nath De\par
\quad - c) Upendranath Brahmachari\par

\textbf{Q16} What is the name of the biopharmaceutical firm founded by Kiran Mazumdar‑Shaw?\par
\quad - a) Biocon\par
\quad - b) Dr. Reddy's Laboratories\par
\quad - c) Sun Pharmaceuticals\par

\textbf{Q17} Which ancient Indian contribution is noted for its significance in astronomy and metaphysics?\par
\quad - a) Concept of Squares and Rectangles\par
\quad - b) Concept of Algebraic Formulae\par
\quad - c) Both A and B\par

\textbf{Q18} Who is credited with the discovery of post‑kala‑azar dermal leishmaniasis?\par
\quad - a) Upendranath Brahmachari\par
\quad - b) Sambhu Nath De\par
\quad - c) Homi J. Bhabha\par

\textbf{Q19} What is the name of the Indian space organization established in 1969?\par
\quad - a) ISRO\par
\quad - b) INCOSPAR\par
\quad - c) DRDO\par

\textbf{Q20} Which Indian scientist made significant contributions to mathematics, particularly in the discovery of various methods and series?\par
\quad - a) Srinivasa Ramanujan\par
\quad - b) Satyendra Nath Bose\par
\quad - c) C.V. Raman\par

\textbf{Q21} What is the name of the technique used in ancient India for distilling zinc?\par
\quad - a) Distillation Technique\par
\quad - b) Smelting Technique\par
\quad - c) Electrolysis Technique\par

\textbf{Q22} Who is known for his work in developing India's space satellites and rockets?\par
\quad - a) Vikram Sarabhai\par
\quad - b) A.P.J. Abdul Kalam\par
\quad - c) Homi J. Bhabha\par

\textbf{Q23} Which ancient Indian contribution is noted for its significance in the development of numeral notations?\par
\quad - a) Hindu‑Arabic Numerals\par
\quad - b) Roman Numerals\par
\quad - c) Egyptian Numerals\par

\textbf{Q24} What is the name of the device invented by Jagadish Chandra Bose to measure plant growth?\par
\quad - a) Crescograph\par
\quad - b) Spectrophotometer\par
\quad - c) Thermometer\par

\textbf{Q25} Who is credited with the development of NexCAR19, a treatment targeting cancer cells?\par
\quad - a) Krishnan Iyer\par
\quad - b) Satyendra Nath Bose\par
\quad - c) C.V. Raman\par

\textbf{Q26} Which Indian company manufactures the Oxford‑AstraZeneca COVID‑19 vaccine under the brand name Covishield?\par
\quad - a) Serum Institute of India\par
\quad - b) Bharat Biotech\par
\quad - c) Zydus Cadila\par

\textbf{Q27} What is the name of the Bollywood film that portrays the story of India's Mars Orbiter Mission (Mangalyaan)?\par
\quad - a) Mission Mangal\par
\quad - b) Rocket Boys\par
\quad - c) Pad Man\par

\textbf{Q28} Which Indian city is often referred to as the "Biotech Capital of India"?\par
\quad - a) Bangalore\par
\quad - b) Hyderabad\par
\quad - c) Pune\par

\textbf{Q29} What indigenous technology was used by the Indian government to manage and track the COVID‑19 vaccination drive?\par
\quad - a) Co‑WIN\par
\quad - b) Aarogya Setu\par
\quad - c) UMANG\par

\textbf{Q30} Which Indian hospital chain is known for performing the first successful liver transplant in India?\par
\quad - a) Apollo Hospitals\par
\quad - b) Christian Medical College (CMC) Vellore\par
\quad - c) All India Institute of Medical Sciences (AIIMS)\par

\textbf{Q31} What is the name of the Indian Institute of Science‑developed ventilator that was rapidly deployed during the COVID‑19 pandemic?\par
\quad - a) Praana\par
\quad - b) AgVa\par
\quad - c) Jyoti\par

\textbf{Q32} Which Indian company developed the world's first DNA plasmid‑based vaccine for COVID‑19?\par
\quad - a) Zydus Cadila\par
\quad - b) Serum Institute of India\par
\quad - c) Bharat Biotech\par

\textbf{Q33} Which Indian film featured a scientist inventing a low‑cost sanitary pad‑making machine to empower women in rural India?\par
\quad - a) Mission Mangal\par
\quad - b) Pad Man\par
\quad - c) Toilet: Ek Prem Katha\par

\textbf{Q34} What is the name of the Indian‑developed payment system that enables real‑time fund transfers between bank accounts?\par
\quad - a) Unified Payments Interface (UPI)\par
\quad - b) Immediate Payment Service (IMPS)\par
\quad - c) National Electronic Funds Transfer (NEFT)\par

\textbf{Q35} Which Indian space mission successfully placed a satellite into orbit around Mars in its first attempt?\par
\quad - a) Mangalyaan\par
\quad - b) Chandrayaan‑1\par
\quad - c) Gaganyaan\par

\textbf{Q36} What is the name of the Indian COVID‑19 vaccine developed by Bharat Biotech?\par
\quad - a) Covaxin\par
\quad - b) Covishield\par
\quad - c) Sputnik V\par

\textbf{Q37} What is the name of the Indian Institute of Science (IISc) startup that is developing a next‑generation COVID‑19 vaccine?\par
\quad - a) Mynvax\par
\quad - b) String Bio\par
\quad - c) Pandorum Technologies\par

\textbf{Q38} Which Indian company is a leading manufacturer of medical devices and equipment, including ventilators?\par
\quad - a) AgVa Healthcare\par
\quad - b) Reliance Life Sciences\par
\quad - c) Biocon\par

\textbf{Q39} What is the name of the Indian government's initiative to provide affordable and quality generic medicines to all?\par
\quad - a) Pradhan Mantri Jan Aushadhi Yojana\par
\quad - b) National Health Mission\par
\quad - c) Ayushman Bharat\par

\textbf{Q40} Which Indian city is a major hub for Information Technology (IT) and is often called the "Silicon Valley of India"?\par
\quad - a) Mumbai\par
\quad - b) Bangalore\par
\quad - c) Chennai\par

\textbf{Q41} Which Indian company is a major player in the development of biosimilars and biopharmaceuticals?\par
\quad - a) Biocon\par
\quad - b) Dr. Reddy's Laboratories\par
\quad - c) Sun Pharmaceutical Industries\par

\textbf{Q42} What is the name of the Indian government's national digital health mission to create a unified healthcare ecosystem?\par
\quad - a) Ayushman Bharat Digital Mission\par
\quad - b) National Digital Health Blueprint\par
\quad - c) National Health Stack\par

\textbf{Q43} What is the name of the Indian company developing mRNA vaccines for COVID‑19 and other infectious diseases?\par
\quad - a) Gennova Biopharmaceuticals\par
\quad - b) Panacea Biotec\par
\quad - c) Cadila Healthcare\par

\textbf{Q44} Which Indian tech company is credited with building India's first supercomputer?\par
\quad - a) Centre for Development of Advanced Computing (C‑DAC)\par
\quad - b) Tata Consultancy Services (TCS)\par
\quad - c) Infosys\par

\textbf{Q45} What is the name of the Indian railway coach factory that developed a low‑cost ventilator during the COVID‑19 pandemic?\par
\quad - a) Rail Coach Factory, Kapurthala\par
\quad - b) Integral Coach Factory, Chennai\par
\quad - c) Modern Coach Factory, Raebareli\par

\textbf{Q46} Which Indian institute has developed a biodegradable and affordable alternative to plastic?\par
\quad - a) IIT Delhi\par
\quad - b) Indian Association for the Cultivation of Science\par
\quad - c) CSIR‑National Chemical Laboratory\par

\textbf{Q47} What is the name of the Indian space agency's proposed mission to study Venus?\par
\quad - a) Shukrayaan‑1\par
\quad - b) Mangalyaan‑2\par
\quad - c) Gaganyaan‑2\par

\textbf{Q48} Which Indian AI start‑up created a robot to sanitize public spaces?\par
\quad - a) Inventus\par
\quad - b) Vistan Robotics\par
\quad - c) GreyOrange\par

\textbf{Q49} Which Indian company developed India's first indigenously designed 750 kV transformer?\par
\quad - a) Bharat Heavy Electricals Limited (BHEL)\par
\quad - b) Larsen & Toubro\par
\quad - c) Reliance Infrastructure\par

\textbf{Q50} What is the name of the Indian campaign that promotes technology adoption in rural communities?\par
\quad - a) Digital India\par
\quad - b) BharatNet\par
\quad - c) Pradhan Mantri Gramin Digital Saksharta Abhiyan (PMGDISHA)\par