\section{INDIA'S CONTRIBUTION TO TECH}

\textbf{Q1} Which Indian company is partnering with NVIDIA to build AI infrastructure in India?\par
\quad - a) Reliance Jio\par
\quad - b) Adani Group\par
\quad - c) Tata Consultancy Services\par

\textbf{Q2} Which Indian startup recently launched its IPO (Initial Public Offering)?\par
\quad - a) Ola\par
\quad - b) Delhivery\par
\quad - c) Paytm\par

\textbf{Q3} Which Indian fintech company is facing regulatory scrutiny due to compliance issues?\par
\quad - a) PhonePe\par
\quad - b) Paytm Payments Bank\par
\quad - c) BharatPe\par

\textbf{Q4} What is the name of the Indian government's initiative focused on developing the semiconductor ecosystem in India?\par
\quad - a) Make in India\par
\quad - b) Digital India\par
\quad - c) India Semiconductor Mission\par

\textbf{Q5} Which Indian company is investing heavily in the development of 6G technology?\par
\quad - a) Bharti Airtel\par
\quad - b) Reliance Jio\par
\quad - c) Vodafone Idea\par

\textbf{Q6} In 2023, which Indian city hosted the Global Partnership on Artificial Intelligence (GPAI) Summit?\par
\quad - a) Mumbai\par
\quad - b) New Delhi\par
\quad - c) Bangalore\par

\textbf{Q7} Which Indian AI startup is developing innovative solutions for agriculture and rural development?\par
\quad - a) Niramai\par
\quad - b) CropIn\par
\quad - c) SigTuple\par

\textbf{Q8} Which Indian company is building its own AI model to rival large language models like GPT‑4?\par
\quad - a) Infosys\par
\quad - b) TCS\par
\quad - c) Reliance Jio\par

\textbf{Q9} Which Indian space‑tech startup is developing reusable satellite launch vehicles?\par
\quad - a) Agnikul Cosmos\par
\quad - b) Skyroot Aerospace\par
\quad - c) Pixxel\par

\textbf{Q10} Which Indian company is collaborating with global tech giants to manufacture semiconductors in India?\par
\quad - a) Tata Group\par
\quad - b) Vedanta Group\par
\quad - c) Mahindra Group\par

\textbf{Q11} What is the name of the Indian government's initiative to promote drone technology and applications?\par
\quad - a) Drone Shakti\par
\quad - b) Drone Utsav\par
\quad - c) Drone Revolution\par

\textbf{Q12} Which Indian startup is developing advanced battery technology for electric vehicles and energy storage?\par
\quad - a) Ather Energy\par
\quad - b) Ola Electric\par
\quad - c) Log9 Materials\par

\textbf{Q13} Which Indian company is investing in the development of quantum‑computing technology?\par
\quad - a) Reliance Industries\par
\quad - b) Tata Consultancy Services\par
\quad - c) HCLTech\par

\textbf{Q14} Which Indian company offers cloud‑computing services through its JioCloud platform?\par
\quad - a) Bharti Airtel\par
\quad - b) Vodafone Idea\par
\quad - c) Reliance Jio\par

\textbf{Q15} Which Indian startup is using AI and machine learning to improve healthcare diagnostics and treatment?\par
\quad - a) Niramai\par
\quad - b) SigTuple\par
\quad - c) Practo\par

\textbf{Q16} Which Indian company is investing in the development of blockchain technology for financial services and supply‑chain management?\par
\quad - a) Infosys\par
\quad - b) TCS\par
\quad - c) Wipro\par

\textbf{Q17} Which Indian city is becoming a hub for data centers and cloud infrastructure?\par
\quad - a) Chennai\par
\quad - b) Mumbai\par
\quad - c) Hyderabad\par

\textbf{Q18} What is the name of the Indian government's initiative to create a digital‑health ecosystem in the country?\par
\quad - a) Ayushman Bharat Digital Mission\par
\quad - b) National Digital Health Mission\par
\quad - c) Digital Health India\par

\textbf{Q19} Which Indian startup is using AI to personalise education and learning experiences for students?\par
\quad - a) Byju's\par
\quad - b) Unacademy\par
\quad - c) Vedantu\par

\textbf{Q20} Which Indian company is investing in agritech solutions to improve agricultural productivity and sustainability?\par
\quad - a) Mahindra & Mahindra\par
\quad - b) ITC Limited\par
\quad - c) Tata Chemicals\par

\textbf{Q21} Which Indian startup is building an autonomous‑driving platform for vehicles?\par
\quad - a) Ather Energy\par
\quad - b) Ola Electric\par
\quad - c) Minus Zero\par

\textbf{Q22} Which Indian company is leading the development of indigenous 5G telecom equipment?\par
\quad - a) Tata Consultancy Services\par
\quad - b) Reliance Jio\par
\quad - c) Bharti Airtel\par

\textbf{Q23} Which Indian e‑commerce platform focuses on empowering small businesses and artisans?\par
\quad - a) Amazon India\par
\quad - b) Flipkart\par
\quad - c) Meesho\par

\textbf{Q24} Which Indian company is investing in space‑based internet services to connect remote areas?\par
\quad - a) Bharti Airtel\par
\quad - b) Reliance Jio\par
\quad - c) Adani Group\par

\textbf{Q25} Which Indian startup is using AI to detect and prevent financial fraud?\par
\quad - a) Cred\par
\quad - b) Razorpay\par
\quad - c) Perfios\par

\textbf{Q26} Which Indian company is renowned for its cybersecurity solutions and services?\par
\quad - a) Infosys\par
\quad - b) TCS\par
\quad - c) Wipro\par

\textbf{Q27} Which Indian startup is using AI and computer vision to improve road safety and traffic management?\par
\quad - a) Bosch India\par
\quad - b) Intel India\par
\quad - c) Staqu Technologies\par

\textbf{Q28} Which Indian company is investing in sustainable packaging solutions to reduce plastic waste?\par
\quad - a) Reliance Industries\par
\quad - b) ITC Limited\par
\quad - c) Tata Chemicals\par

\textbf{Q29} Which Indian startup is using AI to provide personalised mental‑health support and counselling?\par
\quad - a) Practo\par
\quad - b) Lybrate\par
\quad - c) Wysa\par

\textbf{Q30} Which Indian company is focusing on developing solutions for smart and sustainable cities?\par
\quad - a) Larsen & Toubro\par
\quad - b) Adani Group\par
\quad - c) Tata Projects\par

\textbf{Q31} Which Indian startup is building electric tractors and other agricultural machinery?\par
\quad - a) Mahindra & Mahindra\par
\quad - b) Sonalika Tractors\par
\quad - c) Cellestial E‑Mobility\par

\textbf{Q32} Which Indian company is investing in renewable‑energy projects such as solar and wind power?\par
\quad - a) Tata Power\par
\quad - b) Adani Green Energy\par
\quad - c) Reliance Power\par

\textbf{Q33} Which Indian startup is developing technologies for water conservation and management?\par
\quad - a) EKI Energy Services\par
\quad - b) Smart Water Technologies\par
\quad - c) Kritsnam Technologies\par

\textbf{Q34} Which Indian company offers digital‑banking services via its Paytm Payments Bank?\par
\quad - a) HDFC Bank\par
\quad - b) ICICI Bank\par
\quad - c) One97 Communications\par

\textbf{Q35} Which Indian startup is building microsatellites for Earth observation and remote sensing?\par
\quad - a) Pixxel\par
\quad - b) Skyroot Aerospace\par
\quad - c) Agnikul Cosmos\par

\textbf{Q36} Which Indian company is investing in advanced materials for aerospace and defence applications?\par
\quad - a) Tata Steel\par
\quad - b) Bharat Forge\par
\quad - c) Adani Defence & Aerospace\par

\textbf{Q37} Which Indian startup is using AI to improve supply‑chain efficiency and logistics management?\par
\quad - a) Delhivery\par
\quad - b) Ecom Express\par
\quad - c) Rivigo\par

\textbf{Q38} Which Indian company is developing solutions for smart‑grid management and energy distribution?\par
\quad - a) Tata Power\par
\quad - b) Adani Electricity\par
\quad - c) Reliance Infrastructure\par

\textbf{Q39} Which Indian startup is using AI and IoT to improve waste‑management and recycling processes?\par
\quad - a) BinClean Solutions\par
\quad - b) Waste Ventures\par
\quad - c) Dalmia Bharat Group\par

\textbf{Q40} Which Indian company is investing in virtual‑reality (VR) and augmented‑reality (AR) technologies?\par
\quad - a) Tata Elxsi\par
\quad - b) Infosys\par
\quad - c) TCS\par

\textbf{Q41} Which Indian startup is building solutions for precision agriculture and smart farming?\par
\quad - a) CropIn\par
\quad - b) AgNext Technologies\par
\quad - c) DeHaat\par

\textbf{Q42} Which Indian company is developing AI‑powered solutions for customer service and support?\par
\quad - a) Infosys BPM\par
\quad - b) Wipro BPS\par
\quad - c) TCS BPS\par

\textbf{Q43} Which Indian startup is using blockchain technology for secure and transparent land‑record management?\par
\quad - a) Veridian\par
\quad - b) CropIn\par
\quad - c) Terra.do\par

\textbf{Q44} Which Indian company is investing in sustainable transportation solutions such as electric buses and charging infrastructure?\par
\quad - a) Ashok Leyland\par
\quad - b) Tata Motors\par
\quad - c) Mahindra & Mahindra\par

\textbf{Q45} Which Indian startup is using AI and natural‑language processing to improve language translation and interpretation?\par
\quad - a) Reverie Language Technologies\par
\quad - b) Vernacular.ai\par
\quad - c) Senseforth.ai\par

\textbf{Q46} Which Indian company is developing advanced sensor technologies for environmental monitoring and pollution control?\par
\quad - a) Thermax\par
\quad - b) Ion Exchange India\par
\quad - c) Ahlstrom‑Munksjö\par

\textbf{Q47} Which Indian startup is using AI to personalise healthcare recommendations and wellness programmes?\par
\quad - a) HealthifyMe\par
\quad - b) Cure.fit\par
\quad - c) 1mg\par

\textbf{Q48} Which Indian company is developing solutions for smart water management and irrigation?\par
\quad - a) Jain Irrigation Systems\par
\quad - b) Mahindra EPC\par
\quad - c) Kirloskar Brothers Limited\par

\textbf{Q49} Which Indian startup is using AI and machine learning to improve cybersecurity threat detection and prevention?\par
\quad - a) Cyfirma\par
\quad - b) Lucideus\par
\quad - c) Quick Heal Technologies\par

\textbf{Q50} Which Indian company is investing in the development of carbon‑capture and storage technologies?\par
\quad - a) Reliance Industries\par
\quad - b) Tata Steel\par
\quad - c) Adani Group\par