\section{INVENTIONS}

\textbf{Q1} He was sued in 1455 by his business partners and ended up losing the lawsuit, which resulted in him being forced to give up on his business. He died in 1468 as a poor man. The pioneer of the printing revolution who started the first printing press in 1439. Who?\par
\quad - a) Isaac Newton\par
\quad - b) Johannes Gutenberg\par
\quad - c) James Maxwell\par

\textbf{Q2} Who was known as England's Da Vinci, a polymath who coined the term "Cell" to define the compartments in the structure of a cork using a self‑designed compound microscope?\par
\quad - a) Carl Linnaeus\par
\quad - b) Antonie van Leeuwenhoek\par
\quad - c) Robert Hooke\par

\textbf{Q3} Alfred Nobel, recognized for his link to prestigious global awards, developed which explosive compound frequently used in construction and mining?\par
\quad - a) Gunpowder\par
\quad - b) Dynamite\par
\quad - c) TNT\par

\textbf{Q4} Who is recognized for inventing the first motion‑picture camera, which laid the groundwork for modern cinema? He's also remembered with a Hollywood Walk‑of‑Fame star.\par
\quad - a) Louis Lumière\par
\quad - b) Georges Méliès\par
\quad - c) Thomas Edison\par

\textbf{Q5} Schindler, KONE, Fujitech are leading manufacturers of the machine invented by Elisha Otis—a safety mechanism that made it possible to build tall structures. What machine?\par
\quad - a) Escalator\par
\quad - b) Fire sprinkler system\par
\quad - c) Elevator\par

\textbf{Q6} He would lend money to his brother Michelangelo regularly for his musical endeavours and excursions. One of the most important figures of the Renaissance, his discoveries enabled humanity to view distant celestial objects using a telescope which was enhanced and brought into public usage by him. Who?\par
\quad - a) Johannes Kepler\par
\quad - b) Galileo Galilei\par
\quad - c) Tycho Brahe\par

\textbf{Q7} In the early 20th century, this scientist put forth the concept of continental drift, which later developed into the theory of plate tectonics. Who was he?\par
\quad - a) Alfred Wegener\par
\quad - b) Harry Hess\par
\quad - c) Charles Lyell\par

\textbf{Q8} The first successful test of this device was completed on 6 May 1960. Its invention was announced on 7 July 1960 by Theodore Maiman. Since then, it has been used for multiple purposes like light emission, dyeing, and cosmetic surgeries. What device?\par
\quad - a) LASER\par
\quad - b) UV Spectrometer\par
\quad - c) Chromatograph\par

\textbf{Q9} Who enabled the most important adjustment to the modern periodic table in the 20th century—ordering elements by atomic number rather than atomic mass—and was killed in the Battle of Gallipoli?\par
\quad - a) Ernest Rutherford\par
\quad - b) Dmitri Mendeleev\par
\quad - c) Henry Moseley\par

\textbf{Q10} Which scientific achievement in 1928 made way for the first effective anti‑tuberculosis vaccine?\par
\quad - a) Rabies vaccine by Louis Pasteur\par
\quad - b) Smallpox vaccine by Edward Jenner\par
\quad - c) BCG vaccine by Calmette and Guérin\par

\textbf{Q11} The concept of Velcro®, inspired by how burrs cling to fabric, was patented in 1955 by which Swiss inventor?\par
\quad - a) George de Mestral\par
\quad - b) Rudolf Diesel\par
\quad - c) Karl Benz\par

\textbf{Q12} The Z3, recognized as the first modern programmable computer, was designed and constructed in 1941 by which German engineer?\par
\quad - a) Alan Turing\par
\quad - b) Konrad Zuse\par
\quad - c) John Atanasoff\par

\textbf{Q13} The microwave oven, which revolutionized cooking technology, was inadvertently discovered in 1945 by a scientist involved in radar technology. What was his name?\par
\quad - a) Percy Spencer\par
\quad - b) James Clerk Maxwell\par
\quad - c) Edwin Hubble\par

\textbf{Q14} The invention of the battery in 1800 provided the first source of continuous electrical energy. Which Italian scientist was responsible for this invention?\par
\quad - a) André‑Marie Ampère\par
\quad - b) Alessandro Volta\par
\quad - c) Michael Faraday\par

\textbf{Q15} The Hubble Space Telescope, launched in 1990, has yielded groundbreaking visuals of far‑off galaxies. Who is it named after?\par
\quad - a) Carl Sagan\par
\quad - b) Galileo Galilei\par
\quad - c) Edwin Hubble\par

\textbf{Q16} William Gilbert, author of *De Magnete* (1600), coined which everyday scientific term, now also the unit of magnetomotive force?\par
\quad - a) Thermodynamics\par
\quad - b) Electricity\par
\quad - c) Radiation\par

\textbf{Q17} George Beauchamp invented a famous instrument in 1931 that is a staple of rock bands. Notable players include Jimmy Page, Slash, and Jimi Hendrix. Name the instrument.\par
\quad - a) Bass Guitar\par
\quad - b) Drums\par
\quad - c) Electric Guitar\par

\textbf{Q18} The invention of X is attributed to various people. An early prototype was built in 1828 by Hungarian priest Ányos Jedlik; 1890‑1910 was its "golden age," 1920‑1950 its "dark age," and interest revived later in the 20th century—now it's a household name. What product?\par
\quad - a) Steam Engine\par
\quad - b) Electric Vehicles\par
\quad - c) Microwave\par

\textbf{Q19} Robert Noyce, co‑founder of Intel and Fairchild Semiconductors, invented the first X—central to all modern electronics. What is X?\par
\quad - a) Transistor\par
\quad - b) Diode\par
\quad - c) IC Chip (Integrated Circuit)\par

\textbf{Q20} Recently released Google's Willow, Amazon's Majorana, and IBM Mumbai are all types of what cutting‑edge devices?\par
\quad - a) Quantum processors\par
\quad - b) Superconductors\par
\quad - c) GPUs\par