\section{LITERATURE}

\textbf{Q1} Who wrote the epic poem "The Aeneid," which tells the story of the founding of Rome?\par
\quad - a) Virgil\par
\quad - b) Homer\par
\quad - c) Ovid\par

\textbf{Q2} Which country's literature is known for haiku poetry, a form consisting of three lines with a 5‑7‑5 syllable pattern?\par
\quad - a) Japan\par
\quad - b) China\par
\quad - c) Korea\par

\textbf{Q3} Who wrote "The Divine Comedy," a narrative poem that describes the author's journey through Hell, Purgatory, and Heaven?\par
\quad - a) Dante Alighieri\par
\quad - b) Giovanni Boccaccio\par
\quad - c) Francesco Petrarch\par

\textbf{Q4} Which American writer is known for his macabre and gothic short stories, including "The Tell‑Tale Heart" and "The Fall of the House of Usher"?\par
\quad - a) Edgar Allan Poe\par
\quad - b) Nathaniel Hawthorne\par
\quad - c) Washington Irving\par

\textbf{Q5} What is the term for poetry that does not follow a regular meter or rhyme scheme?\par
\quad - a) Free Verse\par
\quad - b) Blank Verse\par
\quad - c) Concrete Poetry\par

\textbf{Q6} Which Irish poet wrote "The Ballad of Reading Gaol," inspired by his imprisonment?\par
\quad - a) Oscar Wilde\par
\quad - b) W.B. Yeats\par
\quad - c) James Joyce\par

\textbf{Q7} Which poet wrote "Ozymandias," a sonnet about the transience of power and the inevitability of decline?\par
\quad - a) Percy Bysshe Shelley\par
\quad - b) John Keats\par
\quad - c) Lord Byron\par

\textbf{Q8} In a traditional sonnet, what is the name of the first eight lines?\par
\quad - a) Octave\par
\quad - b) Sestet\par
\quad - c) Couplet\par

\textbf{Q9} Which poet is known for his unconventional use of grammar, syntax, and typography, as seen in poems like "anyone lived in a pretty how town"?\par
\quad - a) E.E. Cummings\par
\quad - b) Ezra Pound\par
\quad - c) William Carlos Williams\par

\textbf{Q10} What is the term for a poem in which the first letter of each line, when read vertically, spells out a word or phrase?\par
\quad - a) Acrostic\par
\quad - b) Concrete\par
\quad - c) Villanelle\par

\textbf{Q11} Who wrote the poem "The Charge of the Light Brigade," which commemorates a disastrous British cavalry charge during the Crimean War?\par
\quad - a) Alfred Lord Tennyson\par
\quad - b) Robert Browning\par
\quad - c) Elizabeth Barrett Browning\par

\textbf{Q12} Which playwright is often referred to as "The Bard" and is known for works such as "Hamlet," "Macbeth," and "Romeo and Juliet"?\par
\quad - a) William Shakespeare\par
\quad - b) Christopher Marlowe\par
\quad - c) Ben Jonson\par

\textbf{Q13} What is the term for the rhythmic pattern of stressed and unstressed syllables in a line of poetry?\par
\quad - a) Meter\par
\quad - b) Rhyme\par
\quad - c) Alliteration\par

\textbf{Q14} Which author is associated with the Beat Generation and wrote the novel "On the Road," a defining work of the counterculture movement?\par
\quad - a) Jack Kerouac\par
\quad - b) Allen Ginsberg\par
\quad - c) William S. Burroughs\par

\textbf{Q15} Who recited her poem "The Hill We Climb" at the 2021 U.S. presidential inauguration, becoming the youngest inaugural poet in history?\par
\quad - a) Amanda Gorman\par
\quad - b) Maya Angelou\par
\quad - c) Joy Harjo\par

\textbf{Q16} Who is the author of the famous novel "To Kill a Mockingbird"?\par
\quad - a) F. Scott Fitzgerald\par
\quad - b) Harper Lee\par
\quad - c) Jane Austen\par

\textbf{Q17} What is the term for a literary device that compares two unlike things without using "like" or "as"?\par
\quad - a) Metaphor\par
\quad - b) Simile\par
\quad - c) Personification\par

\textbf{Q18} Which poet is known for his landmark collection "Leaves of Grass"?\par
\quad - a) Walt Whitman\par
\quad - b) Emily Dickinson\par
\quad - c) Robert Frost\par

\textbf{Q19} Who wrote the poem "Do Not Go Gentle into That Good Night"?\par
\quad - a) Dylan Thomas\par
\quad - b) T.S. Eliot\par
\quad - c) W.H. Auden\par

\textbf{Q20} What is the term for a poem with 14 lines, typically written in iambic pentameter?\par
\quad - a) Sonnet\par
\quad - b) Ballad\par
\quad - c) Ode\par

\textbf{Q21} Which author wrote the dystopian novel "1984"?\par
\quad - a) George Orwell\par
\quad - b) Aldous Huxley\par
\quad - c) Ray Bradbury\par

\textbf{Q22} Who is the author of the poem "The Love Song of J. Alfred Prufrock"?\par
\quad - a) T.S. Eliot\par
\quad - b) Ezra Pound\par
\quad - c) Wallace Stevens\par

\textbf{Q23} What is the term for a literary device that gives human‑like qualities to non‑human entities?\par
\quad - a) Personification\par
\quad - b) Symbolism\par
\quad - c) Imagery\par

\textbf{Q24} Which poet is known for his reclusive life and unique style, with poems like "Because I could not stop for Death"?\par
\quad - a) Emily Dickinson\par
\quad - b) Sylvia Plath\par
\quad - c) Anne Sexton\par

\textbf{Q25} Who wrote the famous novel "Pride and Prejudice"?\par
\quad - a) Jane Austen\par
\quad - b) Charles Dickens\par
\quad - c) J.K. Rowling\par

\textbf{Q26} What is the term for a poem that tells a story, often with a folkloric theme?\par
\quad - a) Ballad\par
\quad - b) Epic\par
\quad - c) Ode\par

\textbf{Q27} Which author wrote the novel "The Great Gatsby"?\par
\quad - a) F. Scott Fitzgerald\par
\quad - b) Ernest Hemingway\par
\quad - c) William Faulkner\par

\textbf{Q28} Who is the author of the poem "The Waste Land"?\par
\quad - a) T.S. Eliot\par
\quad - b) Ezra Pound\par
\quad - c) Wallace Stevens\par

\textbf{Q29} What is the term for a literary device that uses words to imitate sounds?\par
\quad - a) Onomatopoeia\par
\quad - b) Alliteration\par
\quad - c) Assonance\par

\textbf{Q30} Which poet is known for his collection "The Canterbury Tales"?\par
\quad - a) Geoffrey Chaucer\par
\quad - b) William Shakespeare\par
\quad - c) John Milton\par

\textbf{Q31} Who wrote the novel "The Catcher in the Rye"?\par
\quad - a) J.D. Salinger\par
\quad - b) F. Scott Fitzgerald\par
\quad - c) Ernest Hemingway\par

\textbf{Q32} What is the term for a poem that expresses praise or admiration?\par
\quad - a) Ode\par
\quad - b) Elegy\par
\quad - c) Sonnet\par

\textbf{Q33} Which author wrote the epic‑fantasy trilogy "The Lord of the Rings"?\par
\quad - a) J.R.R. Tolkien\par
\quad - b) C.S. Lewis\par
\quad - c) George R.R. Martin\par

\textbf{Q34} Who is the author of the poem "The Tyger"?\par
\quad - a) William Blake\par
\quad - b) John Keats\par
\quad - c) Percy Bysshe Shelley\par

\textbf{Q35} What is the term for a literary device that uses an object to represent an abstract idea?\par
\quad - a) Symbolism\par
\quad - b) Metaphor\par
\quad - c) Allegory\par

\textbf{Q36} Which poet wrote the autobiographical epic "The Prelude"?\par
\quad - a) William Wordsworth\par
\quad - b) Samuel Taylor Coleridge\par
\quad - c) John Keats\par

\textbf{Q37} Who wrote the novel "The Picture of Dorian Gray"?\par
\quad - a) Oscar Wilde\par
\quad - b) Bram Stoker\par
\quad - c) Mary Shelley\par

\textbf{Q38} What is the term for a poem that mourns the death of someone?\par
\quad - a) Elegy\par
\quad - b) Ode\par
\quad - c) Sonnet\par

\textbf{Q39} Which author wrote the novel "The Adventures of Huckleberry Finn"?\par
\quad - a) Mark Twain\par
\quad - b) F. Scott Fitzgerald\par
\quad - c) Ernest Hemingway\par

\textbf{Q40} Who is the author of the poem "The Lady of Shalott"?\par
\quad - a) Alfred Lord Tennyson\par
\quad - b) Robert Browning\par
\quad - c) Elizabeth Barrett Browning\par

\textbf{Q41} What is the term for a literary device that repeats initial consonant sounds?\par
\quad - a) Alliteration\par
\quad - b) Assonance\par
\quad - c) Consonance\par

\textbf{Q42} Which poet is known for his poem "The Waste Land"?\par
\quad - a) T.S. Eliot\par
\quad - b) Ezra Pound\par
\quad - c) Wallace Stevens\par

\textbf{Q43} Who wrote the novel "The Scarlet Letter"?\par
\quad - a) Nathaniel Hawthorne\par
\quad - b) Herman Melville\par
\quad - c) Edgar Allan Poe\par

\textbf{Q44} What is the term for a poem that expresses sorrow or regret?\par
\quad - a) Elegy\par
\quad - b) Ode\par
\quad - c) Lament\par

\textbf{Q45} Which author wrote the novel "The Count of Monte Cristo"?\par
\quad - a) Alexandre Dumas\par
\quad - b) Victor Hugo\par
\quad - c) Gustave Flaubert\par

\textbf{Q46} Who is the author of the narrative poem "The Highwayman"?\par
\quad - a) Alfred Noyes\par
\quad - b) Robert Browning\par
\quad - c) Elizabeth Barrett Browning\par

\textbf{Q47} What is the term for a literary device that uses irony or understatement?\par
\quad - a) Irony\par
\quad - b) Sarcasm\par
\quad - c) Litotes\par

\textbf{Q48} Which poet is known for his epic "The Song of Hiawatha"?\par
\quad - a) Henry Wadsworth Longfellow\par
\quad - b) Walt Whitman\par
\quad - c) Emily Dickinson\par

\textbf{Q49} Who wrote the science‑fiction novel "The War of the Worlds"?\par
\quad - a) H.G. Wells\par
\quad - b) Jules Verne\par
\quad - c) Isaac Asimov\par

\textbf{Q50} What is the term for a poem that tells a story in verse, often with a folkloric theme?\par
\quad - a) Ballad\par
\quad - b) Epic\par
\quad - c) Narrative Poem\par