\section{MATH IN MEDIA}

\textbf{Q1} In Douglas Adams' "The Hitchhiker's Guide to the Galaxy," what is the "Answer to the Ultimate Question of Life, the Universe, and Everything"?\par
\quad - a) 24\par
\quad - b) 42\par
\quad - c) 36\par

\textbf{Q2} In the movie "A Beautiful Mind," which mathematician's life is portrayed?\par
\quad - a) Alan Turing\par
\quad - b) John Nash\par
\quad - c) Srinivasa Ramanujan\par

\textbf{Q3} In the TV show "The Big Bang Theory," which character has a PhD in Mathematics?\par
\quad - a) Howard Wolowitz\par
\quad - b) Sheldon Cooper\par
\quad - c) Leonard Hofstadter\par

\textbf{Q4} In the movie "Good Will Hunting," what mathematical field does the protagonist excel in?\par
\quad - a) Geometry\par
\quad - b) Number Theory\par
\quad - c) Calculus\par

\textbf{Q5} In "The Simpsons," which mathematical constant appears to be incorrectly calculated as 3.1416 on a blackboard?\par
\quad - a) Pi (π)\par
\quad - b) Euler's number (e)\par
\quad - c) Golden ratio (φ)\par

\textbf{Q6} In the TV show "NUMB3RS," what is the profession of the main character Charlie Eppes?\par
\quad - a) Cryptographer\par
\quad - b) Mathematician\par
\quad - c) Statistician\par

\textbf{Q7} Which mathematical concept is central to the plot of the film "Arrival"?\par
\quad - a) Non‑linear time\par
\quad - b) Game theory\par
\quad - c) Probability\par

\textbf{Q8} In the novel "Contact" by Carl Sagan, what mathematical concept helps decode the alien message?\par
\quad - a) Prime numbers\par
\quad - b) Fibonacci sequence\par
\quad - c) Fractals\par

\textbf{Q9} Which film features a scene where the protagonist uses game theory to decide how to approach women at a bar?\par
\quad - a) 21\par
\quad - b) A Beautiful Mind\par
\quad - c) The Theory of Everything\par

\textbf{Q10} In the TV series "Futurama," one character has which mathematical theorem named after him?\par
\quad - a) Fry's Conjecture\par
\quad - b) The Farnsworth Paradox\par
\quad - c) The Banach‑Tarski Paradox\par

\textbf{Q11} Which popular YouTube channel is known for mathematical animations explaining complex concepts?\par
\quad - a) MathRocks\par
\quad - b) 3Blue1Brown\par
\quad - c) NumberphileSquared\par

\textbf{Q12} In a typical Khan Academy math video, what color is usually used for drawing on the digital blackboard?\par
\quad - a) White\par
\quad - b) Green\par
\quad - c) Blue\par

\textbf{Q13} The YouTube series "Numberphile" is produced by which mathematician/filmmaker?\par
\quad - a) Brady Haran\par
\quad - b) Vi Hart\par
\quad - c) Matt Parker\par

\textbf{Q14} Which math topic has the most viewed educational videos on YouTube as of 2024?\par
\quad - a) Calculus\par
\quad - b) Algebra\par
\quad - c) Geometry\par

\textbf{Q15} What is the main topic of the popular YouTube series "Mathologer"?\par
\quad - a) Applied mathematics\par
\quad - b) Recreational mathematics\par
\quad - c) Mathematical education\par

\textbf{Q16} The YouTube creator "Stand‑up Maths" is the channel of which mathematician?\par
\quad - a) Matt Parker\par
\quad - b) Hannah Fry\par
\quad - c) James Grime\par

\textbf{Q17} Which of these YouTube channels focuses primarily on teaching mathematical proofs?\par
\quad - a) The Coding Train\par
\quad - b) MindYourDecisions\par
\quad - c) Mathologer\par

\textbf{Q18} Which mathematical topic gained popularity on YouTube during the COVID‑19 pandemic?\par
\quad - a) Calculus\par
\quad - b) Epidemiological modeling\par
\quad - c) Statistics\par

\textbf{Q19} In most math education YouTube videos, which visual aid is most commonly used?\par
\quad - a) Graphs\par
\quad - b) Animations\par
\quad - c) Real‑world examples\par

\textbf{Q20} Which math creator is known for videos explaining the Monty Hall Problem?\par
\quad - a) Vsauce\par
\quad - b) 3Blue1Brown\par
\quad - c) Veritasium\par

\textbf{Q21} Which YouTube math channel specializes in calculus tutorials?\par
\quad - a) PatrickJMT\par
\quad - b) The Organic Chemistry Tutor\par
\quad - c) Professor Leonard\par

\textbf{Q22} Which mathematical paradox has the most YouTube videos explaining it?\par
\quad - a) Banach‑Tarski Paradox\par
\quad - b) Zeno's Paradox\par
\quad - c) Russell's Paradox\par

\textbf{Q23} Which popular film includes a scene showing a mathematical equation that supposedly solves human consciousness?\par
\quad - a) Transcendence\par
\quad - b) Lucy\par
\quad - c) Ex Machina\par

\textbf{Q24} In the film "21," what card game do MIT students use mathematics to win?\par
\quad - a) Poker\par
\quad - b) Blackjack\par
\quad - c) Baccarat\par

\textbf{Q25} Which video game franchise uses mathematics puzzles as part of its gameplay?\par
\quad - a) Professor Layton\par
\quad - b) Portal\par
\quad - c) Final Fantasy\par

\textbf{Q26} Who wrote "The Elements," one of the most influential works in the history of mathematics?\par
\quad - a) Archimedes\par
\quad - b) Euclid\par
\quad - c) Pythagoras\par

\textbf{Q27} Which ancient civilization first used a place‑value system and the concept of zero?\par
\quad - a) Egyptian\par
\quad - b) Babylonian\par
\quad - c) Mayan\par

\textbf{Q28} Which mathematician is famous for the phrase "Eureka!" after discovering the principle of buoyancy?\par
\quad - a) Archimedes\par
\quad - b) Thales\par
\quad - c) Aristotle\par

\textbf{Q29} Who is considered the "Father of Modern Mathematics" for connecting algebra and geometry?\par
\quad - a) Isaac Newton\par
\quad - b) René Descartes\par
\quad - c) Gottfried Leibniz\par

\textbf{Q30} The Fibonacci sequence was first described in what book?\par
\quad - a) Liber Abaci\par
\quad - b) Principia Mathematica\par
\quad - c) *Elements*\par

\textbf{Q31} The Dresden Codex, an 11th‑century manuscript with astronomical observations, belongs to which culture?\par
\quad - a) Maya\par
\quad - b) Yoruba\par
\quad - c) Greek\par

\textbf{Q32} Who proved Fermat's Last Theorem in 1994 after it had remained unsolved for over 350 years?\par
\quad - a) Andrew Wiles\par
\quad - b) Grigori Perelman\par
\quad - c) Terence Tao\par

\textbf{Q33} Who transcribed the Rhind Papyrus, which included several fraction problems and an approximation for π?\par
\quad - a) Apophis\par
\quad - b) Khamudi\par
\quad - c) Ahmes\par

\textbf{Q34} Which female mathematician made significant contributions to abstract algebra in the early 20th century?\par
\quad - a) Sofia Kovalevskaya\par
\quad - b) Emmy Noether\par
\quad - c) Ada Lovelace\par

\textbf{Q35} Who developed calculus independently of Isaac Newton in the late 17th century?\par
\quad - a) Blaise Pascal\par
\quad - b) Pierre de Fermat\par
\quad - c) Gottfried Wilhelm Leibniz\par

\textbf{Q36} The House of Wisdom, home to mathematicians such as Al‑Khwarizmi, was located in which city?\par
\quad - a) Baghdad\par
\quad - b) Damascus\par
\quad - c) Alexandria\par

\textbf{Q37} Which Chinese mathematician gave a famous approximation of 3.14159 as π in his 3rd‑century commentary?\par
\quad - a) Hu Wang\par
\quad - b) Liu Hui\par
\quad - c) Xiao Ye\par

\textbf{Q38} Known as "The Tentmaker," which Persian polymath worked on cubic polynomials?\par
\quad - a) Al‑Kashi\par
\quad - b) Omar Khayyam\par
\quad - c) Al‑Karaji\par

\textbf{Q39} What Italian mathematician wrote *Ars Magna* (1545) detailing solutions of cubic and quartic equations?\par
\quad - a) Gerolamo Cardano\par
\quad - b) Niccolò Tartaglia\par
\quad - c) Giuseppe Peano\par

\textbf{Q40} What artist famously included the first magic square seen in Europe in his *Melancholia* (1514)?\par
\quad - a) Albrecht Dürer\par
\quad - b) Raphael\par
\quad - c) Leonardo da Vinci\par

\textbf{Q41} Which mathematical field has seen significant growth in applications for AI in 2024?\par
\quad - a) Topology\par
\quad - b) Graph theory\par
\quad - c) Differential geometry\par

\textbf{Q42} What mathematical concept is central to recent developments in quantum computing?\par
\quad - a) Linear algebra\par
\quad - b) Probability theory\par
\quad - c) Number theory\par

\textbf{Q43} Which mathematical algorithm has recently been improved to help with vaccine distribution?\par
\quad - a) Traveling salesman problem\par
\quad - b) Knapsack algorithm\par
\quad - c) Linear programming\par

\textbf{Q44} What mathematical breakthrough in 2024 has contributed to advancements in weather prediction?\par
\quad - a) Chaos theory applications\par
\quad - b) New differential equations\par
\quad - c) Statistical regression methods\par

\textbf{Q45} Which mathematical concept has recently been applied to improve social media algorithms?\par
\quad - a) Game theory\par
\quad - b) Bayesian statistics\par
\quad - c) Network theory\par

\textbf{Q46} In March 2024, which mathematical model was used to predict the impact of climate change on global economies?\par
\quad - a) Monte Carlo simulations\par
\quad - b) Markov chain analysis\par
\quad - c) Dynamic stochastic general equilibrium models\par

\textbf{Q47} Which mathematician recently won the 2024 Abel Prize for contributions to algebraic geometry?\par
\quad - a) Michel Talagrand\par
\quad - b) Claire Voisin\par
\quad - c) Peter Scholze\par

\textbf{Q48} Which mathematical technique is central to the latest breakthrough in protein folding prediction?\par
\quad - a) Topological data analysis\par
\quad - b) Deep learning with attention mechanisms\par
\quad - c) Partial differential equations\par

\textbf{Q49} In early 2024, what mathematical concept helped researchers improve cryptocurrency security?\par
\quad - a) Elliptic curve cryptography\par
\quad - b) Zero‑knowledge proofs\par
\quad - c) Lattice‑based cryptography\par

\textbf{Q50} Which mathematical model has recently been used to optimize renewable energy distribution?\par
\quad - a) Stochastic optimization\par
\quad - b) Linear programming\par
\quad - c) Genetic algorithms\par