\section{MIXED BAG #SCIENCE}

\textbf{Q1} What is the only mammal capable of true flight, and how does it achieve this remarkable ability?\par
\quad - a) Bats\par
\quad - b) Flying Squirrels\par
\quad - c) Gliding Possums\par

\textbf{Q2} Which planet in our solar system is known as the "Red Planet" due to its reddish appearance, and what causes this coloration?\par
\quad - a) Earth\par
\quad - b) Mars\par
\quad - c) Jupiter\par

\textbf{Q3} What is the chemical symbol for gold, and why is it represented by this symbol?\par
\quad - a) Ag\par
\quad - b) Au\par
\quad - c) Hg\par

\textbf{Q4} Which scientist is credited with the discovery of the concept of gravity, and how did he demonstrate this principle?\par
\quad - a) Galileo Galilei\par
\quad - b) Isaac Newton\par
\quad - c) Albert Einstein\par

\textbf{Q5} What is the largest desert in the world, covering a vast area of land, and what are its unique features?\par
\quad - a) Sahara\par
\quad - b) Gobi\par
\quad - c) Antarctica\par

\textbf{Q6} What does DNA stand for, and what is its role in living organisms?\par
\quad - a) Deoxyribonucleic acid\par
\quad - b) Ribonucleic acid\par
\quad - c) Amino acid\par

\textbf{Q7} Which type of rock is formed from the rapid cooling of lava without crystal growth, resulting in a smooth glassy texture?\par
\quad - a) Basalt\par
\quad - b) Granite\par
\quad - c) Obsidian\par

\textbf{Q8} What is the term for the point in a planet's orbit where it is closest to the Sun, and how does this affect the planet's temperature?\par
\quad - a) Perihelion\par
\quad - b) Aphelion\par
\quad - c) Equinox\par

\textbf{Q9} Which element is represented by the symbol Sb on the periodic table, and what are its common uses?\par
\quad - a) Arsenic\par
\quad - b) Antimony\par
\quad - c) Tellurium\par

\textbf{Q10} What is the largest moon of Saturn, known for its thick atmosphere and potential for life?\par
\quad - a) Titan\par
\quad - b) Enceladus\par
\quad - c) Dione\par

\textbf{Q11} Which organelle is referred to as the "powerhouse of the cell" due to its role in generating energy?\par
\quad - a) Nucleus\par
\quad - b) Mitochondria\par
\quad - c) Ribosome\par

\textbf{Q12} What is the chemical formula for water, and why is it essential for life?\par
\quad - a) H2O\par
\quad - b) CO2\par
\quad - c) O2\par

\textbf{Q13} How many chambers does the human heart have, and what is the function of each chamber?\par
\quad - a) Three\par
\quad - b) Four\par
\quad - c) Five\par

\textbf{Q14} What is the term for the study of weather, and how do meteorologists predict weather patterns?\par
\quad - a) Meteorology\par
\quad - b) Geology\par
\quad - c) Oceanography\par

\textbf{Q15} Which scientists discovered the structure of DNA, and what was their method of discovery?\par
\quad - a) James Watson and Francis Crick\par
\quad - b) Rosalind Franklin\par
\quad - c) Linus Pauling\par

\textbf{Q16} What is the largest bone in the human body, and what is its function?\par
\quad - a) Femur\par
\quad - b) Humerus\par
\quad - c) Sternum\par

\textbf{Q17} What is the only metal that remains liquid at room temperature, and what are its uses?\par
\quad - a) Mercury\par
\quad - b) Lead\par
\quad - c) Tin\par

\textbf{Q18} What is the term for the event when the Moon obstructs the Sun's light from reaching Earth, and how often does this occur?\par
\quad - a) Lunar Eclipse\par
\quad - b) Solar Eclipse\par
\quad - c) Planetary Alignment\par

\textbf{Q19} How long does it take for sunlight to reach Earth, and why is this time important?\par
\quad - a) 8 minutes\par
\quad - b) 8 hours\par
\quad - c) 8 days\par

\textbf{Q20} What is the most prevalent gas in Earth's atmosphere, and what is its role in supporting life?\par
\quad - a) Oxygen\par
\quad - b) Nitrogen\par
\quad - c) Carbon Dioxide\par

\textbf{Q21} What percentage of Earth's water is saltwater, and what are the implications of this?\par
\quad - a) 50%\par
\quad - b) 70%\par
\quad - c) 97%\par

\textbf{Q22} What is the scientific study of bees called, and what are some key findings in this field?\par
\quad - a) Entomology\par
\quad - b) Apiology\par
\quad - c) Melittology\par

\textbf{Q23} How many bones are present in the human body, and how do they contribute to overall health?\par
\quad - a) 200\par
\quad - b) 206\par
\quad - c) 250\par

\textbf{Q24} What is the term for the process by which plants convert sunlight into energy?\par
\quad - a) Respiration\par
\quad - b) Photosynthesis\par
\quad - c) Fermentation\par

\textbf{Q25} Which scientist developed the theory of relativity, and what were its key components?\par
\quad - a) Albert Einstein\par
\quad - b) Isaac Newton\par
\quad - c) Galileo Galilei\par

\textbf{Q26} What is the largest living structure on Earth, and how does it support biodiversity?\par
\quad - a) The Great Barrier Reef\par
\quad - b) The Amazon Rainforest\par
\quad - c) The Grand Canyon\par

\textbf{Q27} Which type of rock is formed from the cooling and solidification of magma deep within the Earth's crust?\par
\quad - a) Igneous\par
\quad - b) Sedimentary\par
\quad - c) Metamorphic\par

\textbf{Q28} What is the term for the movement of water from the roots to the leaves of a plant through xylem?\par
\quad - a) Respiration\par
\quad - b) Photosynthesis\par
\quad - c) Transpiration\par

\textbf{Q29} Which scientist is credited with the discovery of the first antibiotic, and how did this discovery change medicine?\par
\quad - a) Alexander Fleming\par
\quad - b) Louis Pasteur\par
\quad - c) Robert Koch\par

\textbf{Q30} What is the term for the study of the structure, behavior, and evolution of the universe?\par
\quad - a) Cosmology\par
\quad - b) Astrology\par
\quad - c) Astronomy\par

\textbf{Q31} Which type of fossil fuel is formed from the remains of ancient plants?\par
\quad - a) Coal\par
\quad - b) Oil\par
\quad - c) Natural Gas\par

\textbf{Q32} What is the term for the process by which an organism's genetic information is passed from one generation to the next?\par
\quad - a) Mutation\par
\quad - b) Genetic Drift\par
\quad - c) Heredity\par

\textbf{Q33} Which scientist developed the first successful polio vaccine, and what was the impact of this vaccine?\par
\quad - a) Jonas Salk\par
\quad - b) Edward Jenner\par
\quad - c) Louis Pasteur\par

\textbf{Q34} What is the term for the study of the properties of acids and bases?\par
\quad - a) Acid-Base Chemistry\par
\quad - b) Redox Chemistry\par
\quad - c) Equilibrium Chemistry\par

\textbf{Q35} Which type of wave is sound, and how does it propagate through the air?\par
\quad - a) Transverse Wave\par
\quad - b) Longitudinal Wave\par
\quad - c) Electromagnetic Wave\par

\textbf{Q36} What is the term for the energy transferred between objects due to a temperature difference?\par
\quad - a) Conduction\par
\quad - b) Convection\par
\quad - c) Radiation\par

\textbf{Q37} Which scientist is credited with the discovery of the structure of the atom, and what were his key findings?\par
\quad - a) Ernest Rutherford\par
\quad - b) Niels Bohr\par
\quad - c) J.J. Thomson\par

\textbf{Q38} What is the term for the process by which a solid changes directly to a gas?\par
\quad - a) Melting\par
\quad - b) Boiling\par
\quad - c) Sublimation\par

\textbf{Q39} Which type of bond involves the sharing of electrons between atoms?\par
\quad - a) Ionic Bond\par
\quad - b) Covalent Bond\par
\quad - c) Hydrogen Bond\par

\textbf{Q40} What is the term for the study of the rates of chemical reactions?\par
\quad - a) Chemical Kinetics\par
\quad - b) Chemical Thermodynamics\par
\quad - c) Chemical Equilibrium\par

\textbf{Q41} Which scientist developed the theory of continental drift, and what evidence supported this theory?\par
\quad - a) Alfred Wegener\par
\quad - b) Charles Darwin\par
\quad - c) James Hutton\par

\textbf{Q42} What is the term for the process by which water moves through a plant, from roots to leaves, and is then released into the air?\par
\quad - a) Respiration\par
\quad - b) Photosynthesis\par
\quad - c) Transpiration\par

\textbf{Q43} Which type of rock is formed from the alteration of existing rocks under high pressure and temperature?\par
\quad - a) Igneous\par
\quad - b) Sedimentary\par
\quad - c) Metamorphic\par

\textbf{Q44} What is the term for the study of the behavior of gases?\par
\quad - a) Gas Laws\par
\quad - b) Liquid Laws\par
\quad - c) Solid Laws\par

\textbf{Q45} Which scientist is credited with the discovery of the first successful vaccine, and what disease did it target?\par
\quad - a) Edward Jenner\par
\quad - b) Louis Pasteur\par
\quad - c) Jonas Salk\par

\textbf{Q46} What is the term for the process by which a liquid changes to a gas?\par
\quad - a) Evaporation\par
\quad - b) Condensation\par
\quad - c) Boiling\par

\textbf{Q47} Which type of mixture has components that are uniformly distributed?\par
\quad - a) Solution\par
\quad - b) Suspension\par
\quad - c) Colloid\par

\textbf{Q48} What is the term for the study of the equilibrium state of chemical reactions?\par
\quad - a) Chemical Equilibrium\par
\quad - b) Chemical Kinetics\par
\quad - c) Chemical Thermodynamics\par

\textbf{Q49} Which scientist developed the first successful in vitro fertilization method, and what was the significance of this achievement?\par
\quad - a) Robert Edwards\par
\quad - b) Subhash Mukhopadhyay\par
\quad - c) Sambhu Nath De\par

\textbf{Q50} What is the term for the energy released or absorbed during a phase change?\par
\quad - a) Latent Heat\par
\quad - b) Specific Heat\par
\quad - c) Heat of Reaction\par

\textbf{Q51} NASA's ambitious plan to return humans to the Moon by 2025 involves a mission named after the Greek goddess of the hunt. What is the name of this mission?\par
\quad - a) Artemis\par
\quad - b) Apollo\par
\quad - c) Orion\par

\textbf{Q52} Which company, founded by Elon Musk, has revolutionized space travel by developing reusable rockets, significantly reducing the cost of accessing space?\par
\quad - a) SpaceX\par
\quad - b) Blue Origin\par
\quad - c) Virgin Galactic\par

\textbf{Q53} The Mpemba effect is a phenomenon where hot water appears to freeze faster than cold water under certain conditions. What is the term for this unusual effect?\par
\quad - a) Mpemba Effect\par
\quad - b) Leidenfrost Effect\par
\quad - c) Joule-Thomson Effect\par

\textbf{Q54} In 2018, the Nobel Prize in Physics was awarded to Arthur Ashkin for his groundbreaking work on optical tweezers, which use laser light to manipulate small particles. Who was the primary recipient of this award?\par
\quad - a) Arthur Ashkin\par
\quad - b) Donna Strickland\par
\quad - c) Gérard Mourou\par

\textbf{Q55} Located on Mars, Olympus Mons is the largest known volcano in our solar system, standing at an impressive height of over 27 km. What is the name of this massive volcano?\par
\quad - a) Olympus Mons\par
\quad - b) Mount Everest\par
\quad - c) Mauna Kea\par

\textbf{Q56} Antimony, derived from the Latin 'stibium', is an element used in flame retardants and semiconductors. Which element is this?\par
\quad - a) Arsenic\par
\quad - b) Antimony\par
\quad - c) Tellurium\par

\textbf{Q57} Halley's Comet is one of the most famous comets, visible from Earth once every 76 years. What is the name of this periodic comet?\par
\quad - a) Halley's Comet\par
\quad - b) Comet Shoemaker-Levy 9\par
\quad - c) Hale-Bopp\par

\textbf{Q58} The triple point is a specific temperature and pressure at which water, ice, and steam coexist in equilibrium. What is the term for this unique state?\par
\quad - a) Sublimation Point\par
\quad - b) Condensation Point\par
\quad - c) Triple Point\par

\textbf{Q59} Willard F. Libby developed the carbon-14 dating technique, which revolutionized archaeology by allowing the dating of organic materials. Who developed this technique?\par
\quad - a) Willard F. Libby\par
\quad - b) Marie Curie\par
\quad - c) Albert Einstein\par

\textbf{Q60} Auroras occur in the thermosphere, a layer of the atmosphere where charged particles from the solar wind interact with atmospheric gases. What is the name of this atmospheric layer?\par
\quad - a) Troposphere\par
\quad - b) Stratosphere\par
\quad - c) Thermosphere\par

\textbf{Q61} Google has been at the forefront of quantum computing, launching processors like 'Willow' to advance quantum technology. Which organization launched this quantum processor?\par
\quad - a) Google\par
\quad - b) Amazon\par
\quad - c) Meta\par

\textbf{Q62} Echolocation is a biological sonar system used by animals like bats and dolphins to navigate and locate objects in their environment. What is the term for this process?\par
\quad - a) Echolocation\par
\quad - b) Sonar\par
\quad - c) Radar\par

\textbf{Q63} The discovery of the "hole" in the ozone layer was a pivotal moment in environmental science, highlighting the impact of human activities on the atmosphere. Who discovered this phenomenon?\par
\quad - a) Joseph Charles Farman\par
\quad - b) James Lovelock\par
\quad - c) Paul Crutzen\par

\textbf{Q64} Argon was the first noble gas to be discovered, isolated from air in 1894. What is the name of this noble gas?\par
\quad - a) Helium\par
\quad - b) Argon\par
\quad - c) Neon\par

\textbf{Q65} Malaria has been a major global health challenge for centuries. Which disease saw significant advancements in vaccine development in recent years?\par
\quad - a) COVID-19\par
\quad - b) Malaria\par
\quad - c) Tuberculosis\par

\textbf{Q66} Semiconductors are materials that can conduct electricity but not as well as metals, playing a crucial role in modern electronics. What is the term for these materials?\par
\quad - a) Conductors\par
\quad - b) Insulators\par
\quad - c) Semiconductors\par

\textbf{Q67} Wilhelm Conrad Röntgen discovered X-rays in 1895, revolutionizing medical imaging. Who is credited with this discovery?\par
\quad - a) Wilhelm Conrad Röntgen\par
\quad - b) Marie Curie\par
\quad - c) Albert Einstein\par

\textbf{Q68} The Great Barrier Reef is the largest living structure on Earth, spanning over 2,300 kilometers off the coast of Australia. What is the name of this ecosystem?\par
\quad - a) The Great Barrier Reef\par
\quad - b) The Amazon Rainforest\par
\quad - c) The Grand Canyon\par

\textbf{Q69} The top quark is the heaviest known quark, discovered in 1995 at Fermilab. Which type of quark is the heaviest?\par
\quad - a) Top Quark\par
\quad - b) Bottom Quark\par
\quad - c) Charm Quark\par

\textbf{Q70} Phagocytosis is the process by which cells engulf and digest solid particles, playing a key role in immune defense. What is the term for this process?\par
\quad - a) Phagocytosis\par
\quad - b) Pinocytosis\par
\quad - c) Endocytosis\par

\textbf{Q71} Reusable rockets have significantly reduced the cost of space travel by allowing multiple launches from the same vehicle. What technology has made space travel cheaper?\par
\quad - a) Reusable Rockets\par
\quad - b) Solar Sails\par
\quad - c) Nuclear Propulsion\par

\textbf{Q72} Albert Einstein developed the theory of general relativity, which fundamentally changed our understanding of gravity and space-time. Who developed this theory?\par
\quad - a) Galileo Galilei\par
\quad - b) Albert Einstein\par
\quad - c) Isaac Newton\par

\textbf{Q73} Drag is the force that opposes the motion of an object through a fluid, such as air or water. What is the term for this force?\par
\quad - a) Friction\par
\quad - b) Drag\par
\quad - c) Gravity\par

\textbf{Q74} NASA's Perseverance rover was sent to Mars to search for signs of past life and study the planet's geology. What is the name of this rover?\par
\quad - a) Curiosity\par
\quad - b) Perseverance\par
\quad - c) Opportunity\par

\textbf{Q75} Elastic potential energy is stored in a stretched or compressed spring, which can be released as kinetic energy when the spring returns to its original shape. What type of energy is this?\par
\quad - a) Kinetic Energy\par
\quad - b) Potential Energy\par
\quad - c) Elastic Potential Energy\par

\textbf{Q76} Covalent bonds are formed when atoms share electrons, a common type of chemical bond found in molecules. What is the term for this type of bond?\par
\quad - a) Ionic Bond\par
\quad - b) Covalent Bond\par
\quad - c) Hydrogen Bond\par

\textbf{Q77} Transpiration is the process by which water moves from the ground to the atmosphere through plants, playing a crucial role in the water cycle. What is the term for this process?\par
\quad - a) Respiration\par
\quad - b) Photosynthesis\par
\quad - c) Transpiration\par

\textbf{Q78} Tungsten is used in light bulb filaments due to its high melting point and conductivity. Which element is used in these filaments?\par
\quad - a) Silicon\par
\quad - b) Tungsten\par
\quad - c) Platinum\par

\textbf{Q79} The Tesla is the SI unit of magnetic field strength, named after Nikola Tesla, a pioneer in electrical engineering. What is the SI unit of magnetic field strength?\par
\quad - a) Ampere\par
\quad - b) Tesla\par
\quad - c) Ohm\par

\textbf{Q80} Nuclear fusion is the process by which atomic nuclei combine to form a heavier nucleus, releasing a significant amount of energy in the process. What is the term for this process?\par
\quad - a) Nuclear Fission\par
\quad - b) Nuclear Fusion\par
\quad - c) Radioactive Decay\par