\section{MIXED BAG #3}

\textbf{Q1} YouTube started supporting which high‑end video resolution?\par
\quad - a) 1080p\par
\quad - b) 4K\par
\quad - c) 8K\par

\textbf{Q2} If Amazon has Kindle, what device did Borders have?\par
\quad - a) Nook\par
\quad - b) Kobo\par
\quad - c) Reader\par

\textbf{Q3} Who topped Fortune magazine's list of "50 Smartest CEOs in Tech" at the time?\par
\quad - a) Bill Gates\par
\quad - b) Steve Jobs\par
\quad - c) Larry Page\par

\textbf{Q4} Which popular feature launched by Facebook in 2007 was closed on August 1 to improve other features?\par
\quad - a) Facebook Games\par
\quad - b) Gift Shop\par
\quad - c) Fan Pages\par

\textbf{Q5} What new feature did Sony introduce in its Cyber‑shot DSC‑TX9 and DSC‑WX5 cameras?\par
\quad - a) Ability to shoot 3D panorama photos\par
\quad - b) Enhanced zoom capabilities\par
\quad - c) Built‑in image stabilisation\par

\textbf{Q6} What was Twitter's new bargains‑alert service feed called?\par
\quad - a) @deals\par
\quad - b) @earlybird\par
\quad - c) @savings\par

\textbf{Q7} According to a Vizisense report, which was India's most‑used photo‑sharing website?\par
\quad - a) Flickr\par
\quad - b) Facebook\par
\quad - c) Picasa\par

\textbf{Q8} Which US security company started "Project Apollo" to cope with bandwidth increases and strengthen .com and .net domains?\par
\quad - a) McAfee\par
\quad - b) VeriSign\par
\quad - c) Symantec\par

\textbf{Q9} The LifeStudio family of external hard drives is associated with which electronics giant?\par
\quad - a) Western Digital\par
\quad - b) Hitachi\par
\quad - c) Seagate\par

\textbf{Q10} Which Taiwanese company produces the iPod, iPad, iPhone and Intel‑branded motherboards?\par
\quad - a) Acer\par
\quad - b) Foxconn (Hon Hai Precision)\par
\quad - c) Asus\par

\textbf{Q11} What is Microsoft's technology that lets batteries be inserted either way regardless of polarity?\par
\quad - a) InstaCharge\par
\quad - b) Instaload\par
\quad - c) PowerPlus\par

\textbf{Q12} Beginning July 1, which beverage brand offered free Wi‑Fi Internet access in all its American stores, with no time limit or registration?\par
\quad - a) McDonald's\par
\quad - b) Starbucks\par
\quad - c) Dunkin' Donuts\par

\textbf{Q13} If Google has Android, what did Samsung have?\par
\quad - a) Tizen\par
\quad - b) Bada\par
\quad - c) HarmonyOS\par

\textbf{Q14} Which company makes the M11x, touted as the world's smallest gaming laptop at the time?\par
\quad - a) Razer\par
\quad - b) Alienware\par
\quad - c) MSI\par

\textbf{Q15} Which company providing travel information to various websites was acquired by Google for $700 million?\par
\quad - a) Expedia\par
\quad - b) ITA Software\par
\quad - c) Travelocity\par

\textbf{Q16} What is the third expansion set of the MMORPG World of Warcraft called?\par
\quad - a) Wrath of the Lich King\par
\quad - b) Cataclysm\par
\quad - c) Mists of Pandaria\par

\textbf{Q17} Which pioneering cyber‑giant decided to use Firefox as the default browser for nearly 400,000 employees?\par
\quad - a) Google\par
\quad - b) IBM\par
\quad - c) Microsoft\par

\textbf{Q18} What was Google's Android 3.0 OS codename at the time?\par
\quad - a) Honeycomb\par
\quad - b) Gingerbread\par
\quad - c) Ice Cream Sandwich\par

\textbf{Q19} Suites like SunSpider, Celtic Kane's JSBenchmark and Futuremark Peacekeeper are used to test what?\par
\quad - a) Graphics‑card performance\par
\quad - b) Speed of browsers\par
\quad - c) CPU processing power\par

\textbf{Q20} Which popular P2P engine was founded by Mark Gorton?\par
\quad - a) BitTorrent\par
\quad - b) LimeWire\par
\quad - c) Napster\par

\textbf{Q21} Which actor is behind HitRecord.org, letting artists collaborate on films and share profits?\par
\quad - a) Leonardo DiCaprio\par
\quad - b) Joseph Gordon‑Levitt\par
\quad - c) James Franco\par

\textbf{Q22} To which domain name did ICANN give conditional approval?\par
\quad - a) .web\par
\quad - b) .xxx\par
\quad - c) .shop\par

\textbf{Q23} After the N8, Nokia planned to replace Symbian OS with which system on smartphones?\par
\quad - a) Windows Phone\par
\quad - b) MeeGo\par
\quad - c) Android\par

\textbf{Q24} "Etherlink", released by 3Com, was the first what?\par
\quad - a) Modem\par
\quad - b) Ethernet card\par
\quad - c) Router\par

\textbf{Q25} Expand PowerPC.\par
\quad - a) Performance‑Optimized With Enhanced RISC — Performance Computing\par
\quad - b) Power Performance Computing\par
\quad - c) Processing‑Optimized With Enhanced RISC — Personal Computing\par

\textbf{Q26} Which company was named after a creek running behind a co‑founder's Los Altos home?\par
\quad - a) Apple\par
\quad - b) Adobe\par
\quad - c) Oracle\par

\textbf{Q27} How many terabytes are there in a zettabyte?\par
\quad - a) One million\par
\quad - b) One billion\par
\quad - c) One trillion\par

\textbf{Q28} In FarmVille, what crops are initially grown on the two fully grown plots?\par
\quad - a) Corn and Wheat\par
\quad - b) Eggplant and Strawberries\par
\quad - c) Pumpkins and Sunflowers\par

\textbf{Q29} Whose tagline is "quietly brilliant"?\par
\quad - a) Apple\par
\quad - b) HTC\par
\quad - c) Samsung\par

\textbf{Q30} Which game is recognised by Guinness World Records as the world's most popular free MMORPG?\par
\quad - a) World of Warcraft\par
\quad - b) RuneScape\par
\quad - c) League of Legends\par

\textbf{Q31} "You don't get to 500 million friends without making a few enemies" was the tagline for what?\par
\quad - a) A new social‑media platform\par
\quad - b) The Social Network (film)\par
\quad - c) A privacy documentary\par

\textbf{Q32} If Honda has ASIMO, what humanoid robot does Hitachi have?\par
\quad - a) QRIO\par
\quad - b) EMIEW\par
\quad - c) NAO\par

\textbf{Q33} Microsoft's Project Natal motion‑control system for Xbox 360 was renamed what?\par
\quad - a) Xbox Motion\par
\quad - b) Kinect\par
\quad - c) HoloLens\par

\textbf{Q34} Expand CFML.\par
\quad - a) Computer Forms Markup Language\par
\quad - b) ColdFusion Markup Language\par
\quad - c) Cross‑platform Media Language\par

\textbf{Q35} A record tweets‑per‑second burst on Twitter occurred due to which sporting event?\par
\quad - a) Football World Cup final\par
\quad - b) LA Lakers retaining the NBA crown\par
\quad - c) Super Bowl\par

\textbf{Q36} Which game‑maker was producing a video game based on Michael Jackson's life?\par
\quad - a) Activision\par
\quad - b) Ubisoft\par
\quad - c) Electronic Arts\par

\textbf{Q37} Microsoft's new OS for rugged handhelds used by package handlers was called what?\par
\quad - a) Windows CE\par
\quad - b) Windows Embedded Handheld\par
\quad - c) Windows Mobile\par

\textbf{Q38} Which two Japanese majors agreed to merge their mobile‑phone divisions to become the #1 provider of phones in Japan?\par
\quad - a) Sony and Panasonic\par
\quad - b) Toshiba and Fujitsu\par
\quad - c) NEC and Sharp\par

\textbf{Q39} The acronym PNATTMBTC ("Pay No Attention To The Man Behind The Curtain") refers to which classic film?\par
\quad - a) Citizen Kane\par
\quad - b) The Wizard of Oz\par
\quad - c) Casablanca\par

\textbf{Q40} Which IBM supercomputer was scheduled to face human contestants on Jeopardy!?\par
\quad - a) Deep Blue\par
\quad - b) IBM Watson\par
\quad - c) Blue Gene\par

 