\section{MODERN TECHNOLOGY}

\textbf{Q1} What happened when one typed 'World Cup' into Google Search during the FIFA World Cup?\par
\quad - a) Google displayed the World Cup schedule.\par
\quad - b) The header at the bottom changed to 'Goooooooal' from the usual 'Goooooogle'.\par
\quad - c) A special World Cup‑themed Google Doodle appeared.\par

\textbf{Q2} What did Google end just 14 hours into a 24‑hour experiment with its home page?\par
\quad - a) A new search algorithm\par
\quad - b) Background imagery.\par
\quad - c) A social‑media integration feature\par

\textbf{Q3} What does AIR stand for in Adobe AIR?\par
\quad - a) Adobe Internet Reader\par
\quad - b) Adobe Integrated Runtime.\par
\quad - c) Adobe Interactive Renderer\par

\textbf{Q4} How did 'Caffeine' make news recently?\par
\quad - a) It was a new social‑media platform\par
\quad - b) It is Google's new Web indexing system that provides 50 % fresher results than its last index.\par
\quad - c) It was a programming language developed by Microsoft\par

\textbf{Q5} What was the iPhone OS officially rechristened as?\par
\quad - a) Apple OS\par
\quad - b) iOS\par
\quad - c) macOS\par

\textbf{Q6} Which company was founded by Diane Greene, Mendel Rosenblum, Scott Devine, Edward Wang and Edouard Bugnion in 1998?\par
\quad - a) Google\par
\quad - b) VMware\par
\quad - c) Amazon\par

\textbf{Q7} Jaguar, Nebulae and Roadrunner were the world's top three in which category?\par
\quad - a) Gaming consoles\par
\quad - b) Supercomputers.\par
\quad - c) Smartphone sales\par

\textbf{Q8} Which global superstar played Yahoo's brand ambassador at the FIFA World Cup in South Africa?\par
\quad - a) Cristiano Ronaldo\par
\quad - b) David Beckham.\par
\quad - c) Lionel Messi\par

\textbf{Q9} In the free‑software community, what is meant by a "binary blob"?\par
\quad - a) A new type of computer virus\par
\quad - b) An object file loaded into the kernel without publicly available source code\par
\quad - c) A compression algorithm\par

\textbf{Q10} What optical‑disc medium developed by Sony was used on the PlayStation Portable (PSP)?\par
\quad - a) Blu‑Ray Disc\par
\quad - b) Universal Media Disc (UMD)\par
\quad - c) MiniDisc\par

\textbf{Q11} Which Microsoft programme offered shoppers cash‑back on purchases made via its search engine before being discontinued?\par
\quad - a) Google Rewards\par
\quad - b) Bing Cashback\par
\quad - c) Yahoo! Rebates\par

\textbf{Q12} Which telecom giant introduced a phone charger powered by a bicycle's pedalling motion?\par
\quad - a) Ericsson\par
\quad - b) Nokia\par
\quad - c) Vodafone\par

\textbf{Q13} Which now‑retired basketball legend graced the cover of Take‑Two's NBA 2K basketball series?\par
\quad - a) LeBron James\par
\quad - b) Michael Jordan\par
\quad - c) Kobe Bryant\par

\textbf{Q14} Who owns the H.264 video codec?\par
\quad - a) Apple\par
\quad - b) MPEG LA consortium of 26 companies\par
\quad - c) Google\par

\textbf{Q15} Which former chief architect became the chief technology officer of Yahoo!?\par
\quad - a) Eric Schmidt\par
\quad - b) Raymie Stata\par
\quad - c) Bill Gates\par

\textbf{Q16} Which company markets the Mirasol screen technology used in some e‑readers?\par
\quad - a) E Ink Corporation\par
\quad - b) Qualcomm\par
\quad - c) Samsung\par

\textbf{Q17} Which handheld‑device manufacturer used the tagline "quietly brilliant"?\par
\quad - a) BlackBerry\par
\quad - b) HTC Corporation\par
\quad - c) Motorola\par

\textbf{Q18} What was Dell's Android‑powered smartphone with a five‑inch screen called?\par
\quad - a) Venue\par
\quad - b) Streak\par
\quad - c) XPS\par

\textbf{Q19} Which music‑subscription service was unveiled by Skype and Kazaa founders Niklas Zennström and Janus Friis?\par
\quad - a) Spotify\par
\quad - b) Rdio\par
\quad - c) Pandora\par

\textbf{Q20} Which company behind Roxio agreed to acquire codec company DivX in a $300 million deal?\par
\quad - a) Adobe\par
\quad - b) Sonic\par
\quad - c) Corel\par

\textbf{Q21} Which company recently announced a $1 billion investment in AI research to democratise its use across industries?\par
\quad - a) OpenAI\par
\quad - b) Google DeepMind\par
\quad - c) Microsoft\par

\textbf{Q22} What is the name of the AI‑powered jacket (2025) that dynamically adjusts its heating levels?\par
\quad - a) ThermoFlex AI\par
\quad - b) SmartHeat Pro\par
\quad - c) AI ComfortWear\par

\textbf{Q23} Which startup became a unicorn in 2024 by developing quantum‑computing solutions for financial risk modelling?\par
\quad - a) Q‑CTRL\par
\quad - b) IonQ\par
\quad - c) Rigetti Computing\par

\textbf{Q24} Which tech CEO stepped down after 15 years, citing a desire to focus on climate‑change initiatives?\par
\quad - a) Sundar Pichai\par
\quad - b) Tim Cook\par
\quad - c) Satya Nadella\par

\textbf{Q25} What is the name of Meta's 2024 AI chatbot launched to compete with ChatGPT?\par
\quad - a) MetaMind\par
\quad - b) LlamaBot\par
\quad - c) BlenderBot\par

\textbf{Q26} Which company recently acquired Boston Dynamics, the robotics firm behind Spot and Atlas?\par
\quad - a) Hyundai Motors\par
\quad - b) Tesla\par
\quad - c) Amazon\par

\textbf{Q27} What was the theme of the GITEX Europe 2025 event held in Berlin?\par
\quad - a) Sustainable Technologies and Green Innovations\par
\quad - b) The Future of Quantum Computing\par
\quad - c) AI‑Powered Smart Cities\par

\textbf{Q28} Which AI startup launched a tool that can generate entire websites from text prompts?\par
\quad - a) WebGenie AI\par
\quad - b) Durable AI\par
\quad - c) SiteCraft Pro\par

\textbf{Q29} What is the name of Tesla's 2025 campaign promoting its new self‑driving technology?\par
\quad - a) Drive Tomorrow Today\par
\quad - b) Full Autonomy Now\par
\quad - c) Beyond Driving\par

\textbf{Q30} Which tech giant partnered with NASA in 2025 to develop AI algorithms for space exploration and planetary mapping?\par
\quad - a) IBM\par
\quad - b) Google\par
\quad - c) SpaceX\par

\textbf{Q31} Which company created t.co, a URL shortening service widely used for sharing links on social media?\par
\quad - a) Quick Bytes\par
\quad - b) Torrentmap\par
\quad - c) Twitter\par

\textbf{Q32} The term for a spatially mapped array of bits, commonly used in computer graphics, is derived from what?\par
\quad - a) Bitmap\par
\quad - b) Elemental Biology\par
\quad - c) Encyclopaedia Britannica\par

\textbf{Q33} eb.com is the official domain name of which well‑known knowledge repository?\par
\quad - a) Encyclopaedia Britannica\par
\quad - b) Verizon\par
\quad - c) Qualcomm\par

\textbf{Q34} The Bell Telephone Company, founded by Alexander Graham Bell in 1877, is now famously known as what?\par
\quad - a) AT&T\par
\quad - b) Chacha\par
\quad - c) Alan Test\par

\textbf{Q35} What does CAPTCHA stand for in the context of online security and human verification?\par
\quad - a) Completely Automated Public Turing test to tell Computers and Humans Apart\par
\quad - b) Ethernet Protocol for Human Verification\par
\quad - c) Intelnet Secure Access\par

\textbf{Q36} Ethernet, a widely used networking technology, was originally called DIX. Why was it named so?\par
\quad - a) It was developed by DEC, Xerox, and Intel.\par
\quad - b) It was inspired by Darwin's theories.\par
\quad - c) It was an acronym for Data Information Exchange.\par

\textbf{Q37} Which open‑source operating system released by Apple in 2000 features a Platypus as its mascot?\par
\quad - a) Darwin\par
\quad - b) Tesla OS\par
\quad - c) Tegra OS\par

\textbf{Q38} What connects Tesla, Tegra, Quadro, and nForce in the world of technology?\par
\quad - a) Nvidia\par
\quad - b) AMD\par
\quad - c) Dell\par

\textbf{Q39} What is the name of Microsoft's cloud computing platform that offers services like storage and virtual machines?\par
\quad - a) Windows Azure\par
\quad - b) Windows Sky\par
\quad - c) Windows Cloud\par

\textbf{Q40} The fly Eristalis gatesi was named after which iconic tech personality as a tribute to their influence?\par
\quad - a) Bill Gates\par
\quad - b) Sergey Brin\par
\quad - c) Larry Page\par

\textbf{Q41} Apple's first PDA series, the MessagePad, ran on which operating system designed specifically for it?\par
\quad - a) Newton OS\par
\quad - b) Tesla OS\par
\quad - c) Edison OS\par

\textbf{Q42} Which tech leader and social media pioneer was named Time Magazine's Person of the Year in 2010?\par
\quad - a) Mark Zuckerberg\par
\quad - b) Steve Jobs\par
\quad - c) Julian Assange\par

\textbf{Q43} PlayBook, a tablet designed to compete with the iPad, was launched by which company in 2011?\par
\quad - a) BlackBerry\par
\quad - b) Apple\par
\quad - c) Samsung\par

\textbf{Q44} Colin Needham co‑founded this movie database in 1990, which Amazon acquired in 1998. What is it called?\par
\quad - a) IMDb\par
\quad - b) IRDb\par
\quad - c) ISDB\par

\textbf{Q45} In wireless broadband technology, what does HSPA+ stand for?\par
\quad - a) High‑Speed Packet Access Plus\par
\quad - b) High‑Speed Photon Access Plus\par
\quad - c) High‑Speed Peripheral Access Plus\par

\textbf{Q46} SVG is a popular file format in web graphics today. What does SVG stand for?\par
\quad - a) Scalable Vector Graphic\par
\quad - b) Scalable Valet Graphic\par
\quad - c) Scalable Viva Graphic\par

\textbf{Q47} OHA is an alliance of over 80 companies working on mobile standards and innovations. What does OHA stand for?\par
\quad - a) Open Handset Alliance\par
\quad - b) Open Helix Alliance\par
\quad - c) Open History Alliance\par

\textbf{Q48} Texas Instruments was founded by its parent company Geophysical Service Incorporated to manufacture transistors in 1947. What industry did this revolutionize?\par
\quad - a) Semiconductors\par
\quad - b) Telecommunications\par
\quad - c) Consumer Electronics\par

\textbf{Q49} "For those who Do" became the tagline of which computer manufacturer known for its ThinkPad series?\par
\quad - a) Lenovo\par
\quad - b) HP\par
\quad - c) Dell\par

\textbf{Q50} The first model of this device, the BlackBerry 850, debuted in Munich in 1999 as a two‑way pager. Which device was it?\par
\quad - a) BlackBerry\par
\quad - b) Motorola Pager\par
\quad - c) Garmin GPS\par

\textbf{Q51} Which company started as Galvin Manufacturing Corporation before becoming one of the biggest names in telecommunications?\par
\quad - a) Motorola\par
\quad - b) Sony Ericsson\par
\quad - c) Google\par

\textbf{Q52} Trip Hawkins founded this gaming company in 1982 under the name Amazin' Software before renaming it to what we know today. Which company is it?\par
\quad - a) Electronic Arts\par
\quad - b) Valve Corporation\par
\quad - c) Amazon Games\par

\textbf{Q53} James Hughes suggested this name as a derivative of "Torvalds' Unix." What operating system does it refer to?\par
\quad - a) Linux\par
\quad - b) Tux OS\par
\quad - c) NixOS\par

\textbf{Q54} Telecom companies originally referred to this device as "dataset." It converts digital data into analogue signals for phone‑line transmission. What is it called today?\par
\quad - a) Modem\par
\quad - b) Router\par
\quad - c) Adapter\par

\textbf{Q55} The simplified version of what was patented in 1936 by Dr. August Dvorak and Dr. William Dealey?\par
\quad - a) Keyboard Layout\par
\quad - b) Morse Code\par
\quad - c) Mobile Keypad Layout\par

\textbf{Q56} NIC is the main science & technology organisation of the Indian government's information services. What is the full form of NIC?\par
\quad - a) National Informatics Center\par
\quad - b) National Ideation Center\par
\quad - c) National Instrumentation Center\par

\textbf{Q57} John Bardeen, Walter Brattain, and William Shockley made significant contributions to the development of this technology. John Pierce coined the term.\par
\quad - a) Transistor\par
\quad - b) Resistor\par
\quad - c) Amplifier\par

\textbf{Q58} What is the name of Yahoo! Mail's mascot?\par
\quad - a) Liam\par
\quad - b) Mial\par
\quad - c) Mail\par

\textbf{Q59} Founded in 1968 as Integrated Electronics Corporation, which company is now a leading semiconductor manufacturer?\par
\quad - a) Intel\par
\quad - b) EnOcean\par
\quad - c) IEC\par

\textbf{Q60} What is the full form of .pdf, a widely used file format for documents?\par
\quad - a) Printable Document Format\par
\quad - b) Printable Document File\par
\quad - c) Portable Document Format\par

\textbf{Q61} Which Indian cricketer has been a prominent endorser of the digital‑camera giant Canon?\par
\quad - a) Sachin Tendulkar\par
\quad - b) Yuvraj Singh\par
\quad - c) Sourav Ganguly\par

\textbf{Q62} Eduardo Saverin, Dustin Moskovitz, and Chris Hughes were three of the four founders of this social‑media platform in 2004. What is it?\par
\quad - a) Facebook\par
\quad - b) Twitter\par
\quad - c) LinkedIn\par

\textbf{Q63} In video resolutions like 1080p, 720p, and 480p, what does the 'p' stand for?\par
\quad - a) Progressive Scan\par
\quad - b) Progressive Swipe\par
\quad - c) Progressive Seal\par

\textbf{Q64} What is a semiconductor device used as a switch commonly known as?\par
\quad - a) Transistor\par
\quad - b) Processor\par
\quad - c) Memistor\par

\textbf{Q65} Which head of state was the first to issue a podcasted speech, marking a new era in digital communication?\par
\quad - a) Barack Obama\par
\quad - b) Lady Gaga\par
\quad - c) Angela Merkel\par

\textbf{Q66} The Shorty Awards, also known as the Shorties, honour top content creators on which social‑media platform?\par
\quad - a) Twitter\par
\quad - b) Facebook\par
\quad - c) Tumblr\par

\textbf{Q67} In 1999, *The Old Man and the Sea* became the first animated film to be released in what format?\par
\quad - a) IMAX Animated\par
\quad - b) 3D Film\par
\quad - c) DTS\par

\textbf{Q68} What is the abbreviated form of the Institute of Electrical & Electronic Engineers?\par
\quad - a) IEEE\par
\quad - b) INEE\par
\quad - c) IEC\par

\textbf{Q69} Simon, the first smartphone, was designed by BellSouth and which other company in 1992?\par
\quad - a) IBM\par
\quad - b) Oracle\par
\quad - c) Microsoft\par

\textbf{Q70} What is the full form of PCB as in PCB Boards, commonly used in electronics manufacturing?\par
\quad - a) Printed Circuit Board\par
\quad - b) Printed Current Board\par
\quad - c) Printed Camera Board\par

 