\section{POP CULTURE}

\textbf{Q1} Which Marvel superhero is known for wielding a magical hammer called Mjolnir?\par
\quad - a) Iron Man\par
\quad - b) Captain America\par
\quad - c) Thor\par

\textbf{Q2} Who was the first winner of "The Masked Singer"?\par
\quad - a) T‑Pain\par
\quad - b) Nick Cannon\par
\quad - c) Kelly Clarkson\par

\textbf{Q3} Who wrote the "Twilight" book series?\par
\quad - a) J.K. Rowling\par
\quad - b) Stephenie Meyer\par
\quad - c) Suzanne Collins\par

\textbf{Q4} What is the name of the alternate dimension in Netflix's "Stranger Things"?\par
\quad - a) The Shadow World\par
\quad - b) The Upside Down\par
\quad - c) The Dark Side\par

\textbf{Q5} Which artist made history in 2020 as the youngest winner of the Grammys' four main categories?\par
\quad - a) Taylor Swift\par
\quad - b) Billie Eilish\par
\quad - c) Katy Perry\par

\textbf{Q6} In which year did "Keeping Up with the Kardashians" first premiere?\par
\quad - a) 2006\par
\quad - b) 2007\par
\quad - c) 2008\par

\textbf{Q7} Who was the first African‑American man to achieve EGOT status?\par
\quad - a) Denzel Washington\par
\quad - b) John Legend\par
\quad - c) Will Smith\par

\textbf{Q8} In which fictional African country is Black Panther from?\par
\quad - a) Wakanda\par
\quad - b) Azania\par
\quad - c) Kongo\par

\textbf{Q9} Who sings the song "Say So" that became a popular TikTok dance?\par
\quad - a) Doja Cat\par
\quad - b) Ariana Grande\par
\quad - c) Justin Bieber\par

\textbf{Q10} Who created the viral "Renegade" dance on TikTok?\par
\quad - a) Addison Rae\par
\quad - b) Jalaiah Harmon\par
\quad - c) Charli D'Amelio\par

\textbf{Q11} What was the name of Meghan Markle's lifestyle blog before she married into the royal family?\par
\quad - a) The Tig\par
\quad - b) The Royal Life\par
\quad - c) The Duchess Diaries\par

\textbf{Q12} Which hard seltzer did America face a shortage of in 2019?\par
\quad - a) Truly\par
\quad - b) White Claw\par
\quad - c) Bon & Viv\par

\textbf{Q13} What is Mr. Big's real name in "Sex and the City"?\par
\quad - a) John James Preston\par
\quad - b) Mike Brady\par
\quad - c) Jack Harris\par

\textbf{Q14} In the series "Arrested Development," where is there always money?\par
\quad - a) In the bank\par
\quad - b) In the banana stand\par
\quad - c) In the attic\par

\textbf{Q15} What was the name of Winston's beloved cat in the TV show "New Girl"?\par
\quad - a) Mr. Whiskers\par
\quad - b) Furguson\par
\quad - c) Snowball\par

\textbf{Q16} Taylor Swift made her acting debut in which movie?\par
\quad - a) "Valentine's Day"\par
\quad - b) "The Hunger Games"\par
\quad - c) "The Notebook"\par

\textbf{Q17} Who voices Meg Griffin on the animated show "Family Guy"?\par
\quad - a) Mila Kunis\par
\quad - b) Kristen Bell\par
\quad - c) Emma Stone\par

\textbf{Q18} Which celebrity chef is known for the catchphrase "Bam"?\par
\quad - a) Gordon Ramsay\par
\quad - b) Emeril Lagasse\par
\quad - c) Bobby Flay\par

\textbf{Q19} Which rapper is known for his friendship with Martha Stewart?\par
\quad - a) Snoop Dogg\par
\quad - b) Jay‑Z\par
\quad - c) Kanye West\par

\textbf{Q20} Taylor Swift wrote "Bad Blood" as a diss track against which other pop star?\par
\quad - a) Katy Perry\par
\quad - b) Lady Gaga\par
\quad - c) Miley Cyrus\par

\textbf{Q21} Who masterminded the movie "3 Idiots"?\par
\quad - a) Karan Johar\par
\quad - b) Rajkumar Hirani\par
\quad - c) Sanjay Leela Bhansali\par

\textbf{Q22} Which actress played the fierce female lead in the Bollywood movie "Fashion"?\par
\quad - a) Deepika Padukone\par
\quad - b) Priyanka Chopra\par
\quad - c) Katrina Kaif\par

\textbf{Q23} What is Hrithik Roshan's real surname?\par
\quad - a) Nagrath\par
\quad - b) Roshan\par
\quad - c) Khan\par

\textbf{Q24} Which Bollywood actress married American pop star Nick Jonas?\par
\quad - a) Alia Bhatt\par
\quad - b) Priyanka Chopra\par
\quad - c) Sonam Kapoor\par

\textbf{Q25} Who directed the Bollywood film "Gully Boy" about street rap?\par
\quad - a) Zoya Akhtar\par
\quad - b) Karan Johar\par
\quad - c) Anurag Kashyap\par

\textbf{Q26} What martial art does Bollywood actor Rajkummar Rao have formal training in?\par
\quad - a) Karate\par
\quad - b) Taekwondo\par
\quad - c) Judo\par

\textbf{Q27} What role does Rajkummar Rao play in the Bollywood film "Badhaai Do"?\par
\quad - a) Doctor\par
\quad - b) Teacher\par
\quad - c) Cop\par

\textbf{Q28} Who is known as the "King of Romance" in Bollywood?\par
\quad - a) Shah Rukh Khan\par
\quad - b) Salman Khan\par
\quad - c) Aamir Khan\par

\textbf{Q29} What was the little girl named in the film "Pan's Labyrinth"?\par
\quad - a) Ofelia\par
\quad - b) Sophia\par
\quad - c) Isabella\par

\textbf{Q30} Who provided the voice for the forgetful fish Dory in "Finding Nemo"?\par
\quad - a) Ellen DeGeneres\par
\quad - b) Meryl Streep\par
\quad - c) Julia Roberts\par

\textbf{Q31} Which famous jazz musician has the nickname "Satchmo"?\par
\quad - a) Louis Armstrong\par
\quad - b) Duke Ellington\par
\quad - c) Miles Davis\par

\textbf{Q32} What is the real name of British rock singer Freddie Mercury?\par
\quad - a) Farrokh Bulsara\par
\quad - b) Brian May\par
\quad - c) Roger Taylor\par

\textbf{Q33} Which "Star Wars" actor voiced the Joker in "Batman: The Animated Series"?\par
\quad - a) Mark Hamill\par
\quad - b) Harrison Ford\par
\quad - c) Ewan McGregor\par

\textbf{Q34} For which song did Lady Gaga win an Oscar in the movie "A Star Is Born"?\par
\quad - a) "Shallow"\par
\quad - b) "Bad Romance"\par
\quad - c) "Poker Face"\par

\textbf{Q35} What is the name of Michelle Obama's 2018 memoir?\par
\quad - a) "Becoming"\par
\quad - b) "The Audacity of Hope"\par
\quad - c) "Dreams from My Father"\par

\textbf{Q36} Which eminent scientist hosted the television show "Cosmos"?\par
\quad - a) Neil deGrasse Tyson\par
\quad - b) Carl Sagan\par
\quad - c) Stephen Hawking\par

\textbf{Q37} Who played the role of Fox Mulder in the television series "The X‑Files"?\par
\quad - a) David Duchovny\par
\quad - b) Gillian Anderson\par
\quad - c) Chris Carter\par

\textbf{Q38} Where does manga originate from?\par
\quad - a) China\par
\quad - b) Japan\par
\quad - c) Korea\par

\textbf{Q39} Who is considered the founder and foremost practitioner of Pop Art?\par
\quad - a) Andy Warhol\par
\quad - b) Roy Lichtenstein\par
\quad - c) Jasper Johns\par

\textbf{Q40} In which music‑video film did Britney Spears meet her husband Sam Asghari?\par
\quad - a) "Toxic"\par
\quad - b) "Slumber Party"\par
\quad - c) "Womanizer"\par

\textbf{Q41} Which "Bridgerton" star plays Fiyero in the film adaptation of "Wicked"?\par
\quad - a) Regé‑Jean Page\par
\quad - b) Jonathan Bailey\par
\quad - c) Luke Thompson\par

\textbf{Q42} Who gives the voice for the lioness Nala in the 2019 remake of Disney's "The Lion King"?\par
\quad - a) Beyoncé\par
\quad - b) Rihanna\par
\quad - c) Lady Gaga\par

\textbf{Q43} Which historical document does Nicholas Cage's character steal in "National Treasurse"?\par
\quad - a) The Constitution\par
\quad - b) The Declaration of Independence\par
\quad - c) The Bill of Rights\par

\textbf{Q44} What was the title of Justin Bieber's first single released in 2009?\par
\quad - a) "Baby"\par
\quad - b) "One Time"\par
\quad - c) "Sorry"\par

\textbf{Q45} Which famous movie contains the line "Say hello to my little friend"?\par
\quad - a) The Godfather\par
\quad - b) Scarface\par
\quad - c) Goodfellas\par

\textbf{Q46} Which rapper did Kendrick Lamar take aim at in his 2024 single "Not Like Us"?\par
\quad - a) Drake\par
\quad - b) Kanye West\par
\quad - c) J. Cole\par

\textbf{Q47} Which annual rock festival featuring music on multiple stages began in October 1999?\par
\quad - a) Lollapalooza\par
\quad - b) Coachella Valley Festival\par
\quad - c) Glastonbury Festival\par

\textbf{Q48} Which actor from "The Office" had a career as a pop musician in the 1960s?\par
\quad - a) Steve Carell\par
\quad - b) Rainn Wilson\par
\quad - c) Creed Bratton\par

\textbf{Q49} Which Sanderson sister from "Hocus Pocus" is played by Bette Midler?\par
\quad - a) Winifred\par
\quad - b) Sarah\par
\quad - c) Mary\par

\textbf{Q50} In which country was actor Saïd Taghmaoui born?\par
\quad - a) France\par
\quad - b) Morocco\par
\quad - c) Algeria\par