\section{SPACE TECHNOLOGY}

\textbf{Q1} What was the significance of the launch of Sputnik 1 by the Soviet Union in 1957?\par
\quad - a) It was the first spacecraft to land on the Moon\par
\quad - b) It was the first artificial satellite to orbit Earth\par
\quad - c) It was the first manned mission to space\par

\textbf{Q2} Who was the first human to travel into space, and what was the name of his spacecraft?\par
\quad - a) Yuri Gagarin – Vostok 1\par
\quad - b) Alan Shepard – Mercury‑Redstone 3\par
\quad - c) John Glenn – Friendship 7\par

\textbf{Q3} Which country successfully landed humans on the Moon first?\par
\quad - a) Soviet Union\par
\quad - b) United States\par
\quad - c) China\par

\textbf{Q4} What was the primary goal of NASA's Apollo program?\par
\quad - a) To explore Mars\par
\quad - b) To land humans on the Moon and return them safely to Earth\par
\quad - c) To develop reusable spacecraft\par

\textbf{Q5} When was NASA established, and what was its original purpose?\par
\quad - a) 1957 – To explore space and aeronautics\par
\quad - b) 1958 – To conduct space and aeronautics research\par
\quad - c) 1961 – To focus on military space applications\par

\textbf{Q6} What was the name of the mission that made Neil Armstrong and Buzz Aldrin the first humans to walk on the Moon?\par
\quad - a) Apollo 10\par
\quad - b) Apollo 11\par
\quad - c) Apollo 13\par

\textbf{Q7} Which space agency launched Chandrayaan‑3, India's successful lunar‑landing mission in 2023?\par
\quad - a) ESA (European Space Agency)\par
\quad - b) ISRO (Indian Space Research Organisation)\par
\quad - c) NASA\par

\textbf{Q8} What is SpaceX's primary goal as stated by its founder Elon Musk?\par
\quad - a) To colonize Mars and make humanity multi‑planetary\par
\quad - b) To develop satellites for global internet coverage\par
\quad - c) To create reusable rockets for military purposes\par

\textbf{Q9} What was the name of the first privately funded spacecraft to dock with the International Space Station (ISS)?\par
\quad - a) Crew Dragon\par
\quad - b) Dragon C2+ (SpaceX Dragon Capsule)\par
\quad - c) Cygnus\par

\textbf{Q10} Who became the first woman to travel into space in 1963?\par
\quad - a) Sally Ride\par
\quad - b) Valentina Tereshkova\par
\quad - c) Mae Jemison\par

\textbf{Q11} Which spacecraft became the first to orbit another planet (Mars)?\par
\quad - a) Mariner 4\par
\quad - b) Mariner 9\par
\quad - c) Viking 1\par

\textbf{Q12} What is the name of NASA's rover that landed on Mars in February 2021?\par
\quad - a) Opportunity\par
\quad - b) Perseverance\par
\quad - c) Curiosity\par

\textbf{Q13} Which country launched the first space station, Salyut 1, in 1971?\par
\quad - a) United States\par
\quad - b) Soviet Union\par
\quad - c) China\par

\textbf{Q14} What was the primary objective of the Hubble Space Telescope launched in 1990?\par
\quad - a) To study Earth's atmosphere\par
\quad - b) To capture high‑resolution images of distant galaxies and stars\par
\quad - c) To monitor solar activity\par

\textbf{Q15} What is the name of ISRO's Mars Orbiter Mission launched in 2013?\par
\quad - a) Mangalyaan\par
\quad - b) Chandrayaan‑2\par
\quad - c) Vikram Orbiter\par

\textbf{Q16} Who was the first American astronaut to orbit Earth in 1962?\par
\quad - a) Alan Shepard\par
\quad - b) John Glenn\par
\quad - c) Gus Grissom\par

\textbf{Q17} Which spacecraft sent back the first images of Jupiter's moons in 1979?\par
\quad - a) Pioneer 10\par
\quad - b) Voyager 1\par
\quad - c) Galileo\par

\textbf{Q18} What is Blue Origin's main focus as a private space company founded by Jeff Bezos?\par
\quad - a) Developing reusable rockets for commercial space tourism\par
\quad - b) Colonizing Mars\par
\quad - c) Building lunar bases\par

\textbf{Q19} What was the purpose of NASA's Voyager 1 mission launched in 1977?\par
\quad - a) To explore Mars\par
\quad - b) To study the outer Solar System and beyond\par
\quad - c) To land on Jupiter's moons\par

\textbf{Q20} Which space agency launched the Gaia spacecraft to create a precise 3D map of the Milky Way?\par
\quad - a) NASA\par
\quad - b) ESA (European Space Agency)\par
\quad - c) ISRO\par

\textbf{Q21} Who is credited with developing the concept of the geostationary satellite?\par
\quad - a) Arthur C. Clarke\par
\quad - b) Konstantin Tsiolkovsky\par
\quad - c) Sergei Korolev\par

\textbf{Q22} What was the name of the first commercial satellite launched into space?\par
\quad - a) Intelsat 1\par
\quad - b) Telstar 1\par
\quad - c) Syncom 2\par

\textbf{Q23} Which space mission is known for discovering water on Mars?\par
\quad - a) NASA's Curiosity Rover\par
\quad - b) NASA's Perseverance Rover\par
\quad - c) ESA's Mars Express\par

\textbf{Q24} What is the primary purpose of SpaceX's Starlink project?\par
\quad - a) To provide global satellite internet coverage\par
\quad - b) To develop reusable rockets for space tourism\par
\quad - c) To establish a lunar base\par

\textbf{Q25} Who was the first person to spend over a year in space continuously?\par
\quad - a) Scott Kelly\par
\quad - b) Gennady Padalka\par
\quad - c) Valeri Polyakov\par

\textbf{Q26} Which spacecraft is the farthest human‑made object from Earth?\par
\quad - a) Voyager 1\par
\quad - b) Pioneer 10\par
\quad - c) New Horizons\par

\textbf{Q27} What is the name of China's space station launched in 2020?\par
\quad - a) Tiangong‑1\par
\quad - b) Tiangong‑2\par
\quad - c) Tiangong Space Station (TSS)\par

\textbf{Q28} Who founded Virgin Galactic, a company focused on commercial spaceflight?\par
\quad - a) Richard Branson\par
\quad - b) Elon Musk\par
\quad - c) Jeff Bezos\par

\textbf{Q29} What was the purpose of NASA's Skylab space station launched in 1973?\par
\quad - a) To conduct long‑duration spaceflight experiments\par
\quad - b) To study the Sun and its effects on Earth\par
\quad - c) To develop reusable spacecraft\par

\textbf{Q30} Which space agency launched the Rosetta mission to study Comet 67P/Churyumov‑Gerasimenko?\par
\quad - a) NASA\par
\quad - b) ESA (European Space Agency)\par
\quad - c) ISRO\par

\textbf{Q31} Who was the first person to walk in space?\par
\quad - a) Alexei Leonov\par
\quad - b) Ed White\par
\quad - c) Neil Armstrong\par

\textbf{Q32} What is the name of NASA's Artemis program aimed at returning humans to the Moon by 2025?\par
\quad - a) Artemis\par
\quad - b) Apollo\par
\quad - c) Orion\par

\textbf{Q33} Which private space company developed the Falcon 9 rocket?\par
\quad - a) SpaceX\par
\quad - b) Blue Origin\par
\quad - c) Virgin Galactic\par

\textbf{Q34} What was the primary objective of the Mars Curiosity Rover launched in 2011?\par
\quad - a) To search for signs of life on Mars\par
\quad - b) To study the geology of Mars\par
\quad - c) To prepare for human missions to Mars\par

\textbf{Q35} Who is credited with developing the first liquid‑fueled rocket?\par
\quad - a) Robert Goddard\par
\quad - b) Konstantin Tsiolkovsky\par
\quad - c) Sergei Korolev\par

\textbf{Q36} Which spacecraft is known for being the first to visit Pluto?\par
\quad - a) New Horizons\par
\quad - b) Voyager 1\par
\quad - c) Pioneer 10\par

\textbf{Q37} What is the name of ISRO's 2023 mission to study the solar atmosphere?\par
\quad - a) Chandrayaan‑1\par
\quad - b) ADITYA‑L1\par
\quad - c) ANTRIX\par

\textbf{Q38} Who was the first astronaut to spend over 500 days in space?\par
\quad - a) Gennady Padalka\par
\quad - b) Scott Kelly\par
\quad - c) Valeri Polyakov\par

\textbf{Q39} Which space agency launched the Cassini‑Huygens mission to explore Saturn and its moons?\par
\quad - a) NASA\par
\quad - b) ESA (European Space Agency)\par
\quad - c) NASA and ESA collaboration\par

\textbf{Q40} What is the primary goal of NASA's Europa Clipper mission?\par
\quad - a) To explore Jupiter's moon Europa for signs of life\par
\quad - b) To study the geology of Mars\par
\quad - c) To develop reusable spacecraft for lunar missions\par