\section{STATISTICS, DATA INTERPRETATION & GEOMETRY}

\textbf{Q1} What is the primary purpose of hypothesis testing in statistics?\par
   A) To estimate population parameters  
   B) To determine the significance of a relationship  
   C) To predict future outcomes

\textbf{Q2} Which statistical measure is most sensitive to outliers?\par
   A) Mean  
   B) Median  
   C) Mode

\textbf{Q3} In baseball, what statistical measure is used to evaluate a player's batting performance?\par
   A) Batting average  
   B) On‑base percentage  
   C) Slugging percentage

\textbf{Q4} What type of data analysis involves examining the relationship between two variables?\par
   A) Descriptive statistics  
   B) Inferential statistics  
   C) Correlation analysis

\textbf{Q5} Which data visualization tool is best for showing the distribution of a single variable?\par
   A) Bar chart  
   B) Histogram  
   C) Scatter plot

\textbf{Q6} How does data analytics contribute to public health policy‑making?\par
   A) By predicting disease outbreaks  
   B) By analyzing vaccination rates  
   C) Both A and B

\textbf{Q7} What is the formula for the area of a circle?\par
   A) πr  
   B) πr²  
   C) 2πr

\textbf{Q8} In basketball, what statistical measure is used to evaluate a team's defensive performance?\par
   A) Points per game  
   B) Defensive efficiency  
   C) Rebound margin

\textbf{Q9} Which geometric shape has all sides of equal length and all angles equal to 60°?\par
   A) Square  
   B) Rectangle  
   C) Equilateral triangle

\textbf{Q10} What is the purpose of stratification in survey sampling?\par
    A) To increase sample size  
    B) To reduce bias  
    C) To improve precision

\textbf{Q11} How does data normalization help in machine learning models?\par
    A) By reducing the impact of outliers  
    B) By improving model interpretability  
    C) By scaling features to a common range

\textbf{Q12} Which statistical test is used to compare means between two groups?\par
    A) T‑test  
    B) ANOVA  
    C) Chi‑square test

\textbf{Q13} In football, what statistical measure is used to evaluate a quarterback's performance?\par
    A) Passing yards  
    B) Touchdowns  
    C) Quarterback rating

\textbf{Q14} What is the formula for the volume of a sphere?\par
    A) (4/3)πr³  
    B) (2/3)πr³  
    C) (1/3)πr³

\textbf{Q15} Which geometric concept describes the shortest distance between two points?\par
    A) Line segment  
    B) Perpendicular bisector  
    C) Straight line

\textbf{Q16} How does data analytics help in managing supply chains during global crises?\par
    A) By predicting demand fluctuations  
    B) By optimizing logistics routes  
    C) Both A and B

\textbf{Q17} Which statistical method is used to handle missing data in datasets?\par
    A) Imputation  
    B) Regression analysis  
    C) Time series analysis

\textbf{Q18} In tennis, what statistical measure is used to evaluate a player's serve performance?\par
    A) Ace percentage  
    B) First‑serve percentage  
    C) Break‑point conversion

\textbf{Q19} What is the term for a polygon with five sides?\par
    A) Pentagon  
    B) Hexagon  
    C) Heptagon

\textbf{Q20} Which data visualization technique is commonly used to represent complex data in news reports?\par
    A) Bar charts  
    B) Scatter plots  
    C) Infographics

\textbf{Q21} What is the formula for calculating the standard deviation of a sample?\par
    A) √[(Σ(xᵢ − μ)²)/(n−1)]  
    B) √[(Σ(xᵢ − μ)²)/n]  
    C) √[(Σ(xᵢ − μ)²)/(n+1)]

\textbf{Q22} In cricket, what statistical measure is used to evaluate a bowler's performance?\par
    A) Bowling average  
    B) Strike rate  
    C) Economy rate

\textbf{Q23} Which geometric concept describes a shape that remains unchanged under rotation?\par
    A) Symmetry  
    B) Congruence  
    C) Similarity

\textbf{Q24} What is the purpose of bootstrapping in statistical analysis?\par
    A) To estimate population parameters  
    B) To assess the variability of estimates  
    C) To test hypotheses

\textbf{Q25} Which statistical technique is used to identify patterns in large datasets?\par
    A) Cluster analysis  
    B) Factor analysis  
    C) Principal component analysis

\textbf{Q26} How does data analytics improve educational outcomes by analyzing student performance?\par
    A) By identifying learning gaps  
    B) By predicting student success  
    C) Both A and B

\textbf{Q27} In golf, what statistical measure evaluates a player's overall performance?\par
    A) Stroke average  
    B) Greens in regulation  
    C) Scrambling percentage

\textbf{Q28} What is the formula for the surface area of a sphere?\par
    A) 4πr²  
    B) 2πr²  
    C) πr²

\textbf{Q29} Which geometric shape has all internal angles equal to 90°?\par
    A) Square  
    B) Rectangle  
    C) Rhombus

\textbf{Q30} What is the term for a line that intersects two parallel lines?\par
    A) Transversal  
    B) Perpendicular  
    C) Bisector

\textbf{Q31} How does data mining help in marketing strategies?\par
    A) By identifying customer segments  
    B) By predicting consumer behavior  
    C) Both A and B

\textbf{Q32} In volleyball, what statistical measure evaluates a team's blocking performance?\par
    A) Blocks per set  
    B) Hitting percentage  
    C) Digs per set

\textbf{Q33} Which statistical model is used in climate science to predict future temperature changes?\par
    A) Linear regression  
    B) Generalized linear model  
    C) General circulation model

\textbf{Q34} What is the formula for the area of a triangle with base b and height h?\par
    A) (1/2)bh  
    B) bh  
    C) (2/3)bh

\textbf{Q35} Which geometric technique is used in computer graphics to create realistic models?\par
    A) Ray tracing  
    B) Polygon meshing  
    C) Texture mapping

\textbf{Q36} How does geometry influence the design of electronic circuits?\par
    A) By optimizing component placement  
    B) By minimizing signal delay  
    C) Both A and B

\textbf{Q37} In rugby, what statistical measure evaluates a team's defensive performance?\par
    A) Tackles made  
    B) Turnovers won  
    C) Defensive efficiency

\textbf{Q38} What is the formula for the volume of a rectangular prism with dimensions l, w, h?\par
    A) lwh  
    B) l + w + h  
    C) l² + w² + h²

\textbf{Q39} Which geometric concept is used in urban planning to optimize traffic flow?\par
    A) Network theory  
    B) Graph theory  
    C) Topology

\textbf{Q40} What is the purpose of cross‑validation in machine learning models?\par
    A) To evaluate model performance  
    B) To select model parameters  
    C) To reduce overfitting

\textbf{Q41} How does data analytics contribute to financial decision‑making?\par
    A) By predicting stock prices  
    B) By analyzing market trends  
    C) Both A and B

\textbf{Q42} In hockey, what statistical measure evaluates a goalie's performance?\par
    A) Save percentage  
    B) Goals against average  
    C) Shutouts

\textbf{Q43} Which statistical method analyzes the relationship between a dependent variable and one or more independent variables?\par
    A) Regression analysis  
    B) Correlation analysis  
    C) Time‑series analysis

\textbf{Q44} What is the formula for the perimeter of a square with side length s?\par
    A) 4s  
    B) 2s  
    C) s²

\textbf{Q45} Which geometric shape is often used in the design of satellite dishes?\par
    A) Parabola  
    B) Ellipse  
    C) Hyperbola

\textbf{Q46} How does geometry influence the design of wind turbines for efficiency?\par
    A) By optimizing blade shape  
    B) By minimizing drag  
    C) Both A and B

\textbf{Q47} In cycling, what statistical measure evaluates a rider's performance?\par
    A) Average speed  
    B) Power output  
    C) Time‑trial performance

\textbf{Q48} What is the term for the bias introduced by non‑response in surveys?\par
    A) Selection bias  
    B) Information bias  
    C) Non‑response bias

\textbf{Q49} Which statistical technique analyzes the relationship between two categorical variables?\par
    A) Chi‑square test  
    B) T‑test  
    C) ANOVA

\textbf{Q50} How does data analytics help in optimizing supply‑chain logistics?\par
    A) By predicting demand fluctuations  
    B) By optimizing routes  
    C) Both A and B 