\section{TECH COMPANIES AND PEOPLE}

\textbf{Q1} Which company is credited with creating the first microprocessor in 1971?\par
\quad - a) Intel\par
\quad - b) IBM\par
\quad - c) Texas Instruments\par

\textbf{Q2} What was the original name of IBM when it was founded in 1911?\par
\quad - a) Computing‑Tabulating‑Recording Company (CTR)\par
\quad - b) International Business Machines\par
\quad - c) Bell Systems\par

\textbf{Q3} Which company was founded by Steve Jobs, Steve Wozniak, and Ronald Wayne in 1976?\par
\quad - a) Microsoft\par
\quad - b) Apple\par
\quad - c) Xerox\par

\textbf{Q4} What was the first product released by Microsoft in 1975?\par
\quad - a) Windows Operating System\par
\quad - b) BASIC Interpreter for the Altair 8800\par
\quad - c) MS‑DOS\par

\textbf{Q5} Jeff Bezos founded Amazon in 1994 as an online platform to sell what?\par
\quad - a) Electronics\par
\quad - b) Books\par
\quad - c) Music CDs\par

\textbf{Q6} Which company developed the UNIX operating system in the 1970s?\par
\quad - a) Bell Labs\par
\quad - b) Microsoft\par
\quad - c) IBM\par

\textbf{Q7} Who co‑founded Google in 1998?\par
\quad - a) Mark Zuckerberg and Sheryl Sandberg\par
\quad - b) Larry Page and Sergey Brin\par
\quad - c) Jeff Bezos and Andy Jassy\par

\textbf{Q8} What was the name of Elon Musk's first startup, sold for $307 million in 1999?\par
\quad - a) Tesla Motors\par
\quad - b) PayPal (formerly X.com)\par
\quad - c) Zip2\par

\textbf{Q9} Which tech company introduced the first graphical web browser, Mosaic, in 1993?\par
\quad - a) Netscape Communications Corporation\par
\quad - b) Microsoft Corporation\par
\quad - c) NCSA\par

\textbf{Q10} What was the first product launched by Apple in 1976?\par
\quad - a) Apple II Computer\par
\quad - b) Macintosh Computer\par
\quad - c) Apple I Microcomputer\par

\textbf{Q11} Which company revolutionised online advertising with AdWords in 2000?\par
\quad - a) Yahoo!\par
\quad - b) Google\par
\quad - c) Facebook\par

\textbf{Q12} Who founded Facebook in 2004 while studying at Harvard University?\par
\quad - a) Jack Dorsey\par
\quad - b) Mark Zuckerberg\par
\quad - c) Evan Spiegel\par

\textbf{Q13} What was Tesla Motors' primary innovation when it launched the Roadster in 2008?\par
\quad - a) Autonomous‑driving capabilities\par
\quad - b) All‑electric sports car with long‑range capability\par
\quad - c) Solar‑powered battery systems\par

\textbf{Q14} Which company introduced the first commercially successful smartphone, the BlackBerry, in 1999?\par
\quad - a) Nokia\par
\quad - b) Research In Motion (RIM), now BlackBerry Limited\par
\quad - c) Motorola\par

\textbf{Q15} Who is credited with founding Alibaba Group in 1999?\par
\quad - a) Lei Jun\par
\quad - b) Jack Ma\par
\quad - c) Pony Ma\par

\textbf{Q16} Which startup popularised ride‑sharing services worldwide?\par
\quad - a) Lyft\par
\quad - b) Uber\par
\quad - c) BlaBlaCar\par

\textbf{Q17} What was the original purpose of PayPal when founded in 1998?\par
\quad - a) Peer‑to‑peer money transfer for Palm Pilot devices\par
\quad - b) Online shopping platform\par
\quad - c) Cryptocurrency exchange\par

\textbf{Q18} Which company launched AWS (Amazon Web Services) in 2006, revolutionising cloud computing?\par
\quad - a) Google\par
\quad - b) Amazon\par
\quad - c) Microsoft\par

\textbf{Q19} What is SpaceX's stated primary mission?\par
\quad - a) Develop electric vehicles for space exploration\par
\quad - b) Colonise Mars and make humanity multi‑planetary\par
\quad - c) Create reusable rockets for military purposes\par

\textbf{Q20} Which brand introduced the first widely adopted personal computer with a GUI?\par
\quad - a) IBM PC\par
\quad - b) Apple Macintosh\par
\quad - c) Commodore PET\par

\textbf{Q21} What was Netflix's original business model when it launched in 1997?\par
\quad - a) Online streaming of movies\par
\quad - b) DVD rental‑by‑mail service\par
\quad - c) Cable‑TV subscription\par

\textbf{Q22} Who co‑founded Twitter alongside Biz Stone and Jack Dorsey in 2006?\par
\quad - a) Evan Williams\par
\quad - b) Reid Hoffman\par
\quad - c) Larry Page\par

\textbf{Q23} Which company acquired LinkedIn for $26 billion in 2016?\par
\quad - a) Amazon\par
\quad - b) Microsoft\par
\quad - c) Google\par

\textbf{Q24} What is the name of Google's parent company formed in 2015?\par
\quad - a) Alphabet Inc.\par
\quad - b) Waymo Inc.\par
\quad - c) DeepMind Technologies\par

\textbf{Q25} Which startup pioneered short‑form video content leading to TikTok's popularity?\par
\quad - a) Musical.ly\par
\quad - b) Snapchat\par
\quad - c) Instagram Reels\par

\textbf{Q26} Who co‑founded Airbnb in 2008?\par
\quad - a) Brian Chesky, Joe Gebbia, and Nathan Blecharczyk\par
\quad - b) Travis Kalanick and Garrett Camp\par
\quad - c) Mark Zuckerberg and Dustin Moskovitz\par

\textbf{Q27} Which company developed the first smartphone with a touchscreen interface (iPhone) in 2007?\par
\quad - a) Samsung\par
\quad - b) Apple\par
\quad - c) Google\par

\textbf{Q28} What was the name of the first web browser created by Tim Berners‑Lee in 1990?\par
\quad - a) WorldWideWeb\par
\quad - b) Netscape Navigator\par
\quad - c) Internet Explorer\par

\textbf{Q29} Who founded Dropbox in 2007?\par
\quad - a) Drew Houston and Arash Ferdowsi\par
\quad - b) Mark Zuckerberg and Eduardo Saverin\par
\quad - c) Reid Hoffman and Lee Hower\par

\textbf{Q30} Which company bought Instagram in 2012 for $1 billion?\par
\quad - a) Facebook\par
\quad - b) Twitter\par
\quad - c) Google\par

\textbf{Q31} What was the primary innovation of the PalmPilot released in 1996?\par
\quad - a) First smartphone with internet capabilities\par
\quad - b) First handheld personal digital assistant (PDA)\par
\quad - c) First device with a touchscreen interface\par

\textbf{Q32} Who co‑founded LinkedIn in 2002?\par
\quad - a) Reid Hoffman, Lee Hower, Jean‑Luc Vaillant, Eric Lee, and Konstantin Guericke\par
\quad - b) Mark Zuckerberg and Dustin Moskovitz\par
\quad - c) Jack Dorsey and Biz Stone\par

\textbf{Q33} Which company developed the first successful tablet computer, the iPad, in 2010?\par
\quad - a) Microsoft\par
\quad - b) Apple\par
\quad - c) Samsung\par

\textbf{Q34} What was YouTube's original purpose when founded in 2005?\par
\quad - a) Video‑sharing platform for personal videos\par
\quad - b) Online education platform\par
\quad - c) Live‑streaming service for events\par

\textbf{Q35} Who founded Reddit in 2005?\par
\quad - a) Steve Huffman and Alexis Ohanian\par
\quad - b) Mark Zuckerberg and Eduardo Saverin\par
\quad - c) Jack Dorsey and Biz Stone\par

\textbf{Q36} Which company acquired WhatsApp in 2014 for $19 billion?\par
\quad - a) Google\par
\quad - b) Facebook\par
\quad - c) Microsoft\par

\textbf{Q37} What was the first social‑media platform launched by SixDegrees.com in 1997?\par
\quad - a) Facebook\par
\quad - b) MySpace\par
\quad - c) SixDegrees.com\par

\textbf{Q38} Who co‑founded Slack in 2009?\par
\quad - a) Stewart Butterfield, Eric Costello, Cal Henderson, and Serguei Mourachov\par
\quad - b) Mark Zuckerberg and Dustin Moskovitz\par
\quad - c) Jack Dorsey and Biz Stone\par

\textbf{Q39} Which company created the first smartwatch, the Pebble Watch, in 2012?\par
\quad - a) Apple\par
\quad - b) Fitbit\par
\quad - c) Pebble Technology Corporation\par

\textbf{Q40} Who founded Stripe in 2010?\par
\quad - a) Patrick Collison and John Collison\par
\quad - b) Mark Zuckerberg and Eduardo Saverin\par
\quad - c) Jack Dorsey and Biz Stone\par