\section{VISUAL ARTS AND PAINTINGS}

\textbf{Q1} Which art movement, characterized by dream‑like imagery and irrational scenes, is exemplified by Salvador Dalí's "The Persistence of Memory," featuring melting clocks?\par
\quad - a) Impressionism\par
\quad - b) Surrealism\par
\quad - c) Cubism\par

\textbf{Q2} "Guernica," a powerful anti‑war painting depicting the bombing of a Basque town, was created by which influential Spanish artist?\par
\quad - a) Diego Rivera\par
\quad - b) Francisco Goya\par
\quad - c) Pablo Picasso\par

\textbf{Q3} Which artistic style—using small, distinct dots of colour applied in patterns to form an image—is famously employed in Georges Seurat's "A Sunday on La Grande Jatte"?\par
\quad - a) Pointillism\par
\quad - b) Fauvism\par
\quad - c) Expressionism\par

\textbf{Q4} Jan van Eyck's "Arnolfini Portrait" is renowned for its realistic detail and symbolism. What innovation in painting technique is he often credited with pioneering?\par
\quad - a) Sfumato\par
\quad - b) Oil paint\par
\quad - c) Fresco\par

\textbf{Q5} Often referred to as the greatest Mughal painter, which artist is renowned for his naturalistic depictions of animals and court scenes, as seen in the "Baburnama"?\par
\quad - a) Basawan\par
\quad - b) Daswanth\par
\quad - c) Mansur\par

\textbf{Q6} Known for capturing fleeting moments and atmospheric conditions, which French movement is exemplified by Claude Monet's "Impression, Sunrise"?\par
\quad - a) Realism\par
\quad - b) Impressionism\par
\quad - c) Romanticism\par

\textbf{Q7} Which artist—known for expressive brush‑strokes and emotional intensity—created "The Starry Night," a depiction of the view from his asylum window?\par
\quad - a) Paul Cézanne\par
\quad - b) Vincent van Gogh\par
\quad - c) Edvard Munch\par

\textbf{Q8} "The Birth of Venus," a masterpiece of the Italian Renaissance, was painted by which Florentine artist noted for elegant and graceful figures?\par
\quad - a) Leonardo da Vinci\par
\quad - b) Michelangelo\par
\quad - c) Sandro Botticelli\par

\textbf{Q9} Raja Ravi Varma, a pioneer of modern Indian art, is famous for his paintings depicting scenes from which Indian epics and mythology?\par
\quad - a) Ramayana and Mahabharata\par
\quad - b) Jataka Tales and Vedas\par
\quad - c) Sangam literature\par

\textbf{Q10} Which art style—breaking objects into fragments and re‑assembling them abstractly—is seen in Pablo Picasso's "Les Demoiselles d'Avignon"?\par
\quad - a) Expressionism\par
\quad - b) Cubism\par
\quad - c) Futurism\par

\textbf{Q11} Leonardo da Vinci's "Mona Lisa" is famed for its enigmatic smile and mastery of sfumato. What does "sfumato" refer to?\par
\quad - a) Use of vibrant colours\par
\quad - b) Blurring of outlines\par
\quad - c) Detailed textures\par

\textbf{Q12} Known for bold colour and simplified forms, which movement is associated with Henri Matisse—as seen in "The Dance"?\par
\quad - a) Surrealism\par
\quad - b) Fauvism\par
\quad - c) Dadaism\par

\textbf{Q13} "The Night Watch," a large and dramatic group portrait, is a signature work by which Dutch Baroque painter renowned for his use of light and shadow?\par
\quad - a) Johannes Vermeer\par
\quad - b) Rembrandt van Rijn\par
\quad - c) Peter Paul Rubens\par

\textbf{Q14} The Bengal School of Art, which promoted indigenous techniques and themes, was led by which influential Indian artist known for the painting "Bharat Mata"?\par
\quad - a) Nandalal Bose\par
\quad - b) Abanindranath Tagore\par
\quad - c) Jamini Roy\par

\textbf{Q15} Which art movement—emerging in early‑20th‑century Italy—celebrated technology, speed and modern dynamism, as seen in Umberto Boccioni's "Unique Forms of Continuity in Space"?\par
\quad - a) Constructivism\par
\quad - b) Futurism\par
\quad - c) Suprematism\par

\textbf{Q16} Michelangelo's "The Creation of Adam," part of the Sistine Chapel ceiling, depicts which biblical figures?\par
\quad - a) Adam and Eve\par
\quad - b) God and Adam\par
\quad - c) Jesus and John the Baptist\par

\textbf{Q17} Known for her self‑portraits exploring identity, pain and the human body, which Mexican artist is celebrated for surrealist and deeply personal works?\par
\quad - a) Remedios Varo\par
\quad - b) Frida Kahlo\par
\quad - c) Leonora Carrington\par

\textbf{Q18} Which Japanese wood‑block printing art form—popular during the Edo period—influenced Impressionists like Edgar Degas and Mary Cassatt?\par
\quad - a) Sumi‑e\par
\quad - b) Ukiyo‑e\par
\quad - c) Origami\par

\textbf{Q19} Amrita Sher‑Gil blended Western and Indian styles in paintings of rural India. Which themes did she often explore?\par
\quad - a) Nationalism and patriotism\par
\quad - b) Poverty and social inequality\par
\quad - c) Love and romance\par

\textbf{Q20} Which Russian movement—characterised by geometric shapes and abstraction—was founded by Kazimir Malevich, known for "Black Square"?\par
\quad - a) Constructivism\par
\quad - b) Suprematism\par
\quad - c) Realism\par

\textbf{Q21} Raphael's "The School of Athens" celebrates knowledge. Which ancient philosophers are centred prominently?\par
\quad - a) Socrates and Plato\par
\quad - b) Plato and Aristotle\par
\quad - c) Aristotle and Pythagoras\par

\textbf{Q22} The Pop‑Art movement embracing consumer culture found one of its leaders in which American artist who immortalised Campbell's soup cans?\par
\quad - a) Jackson Pollock\par
\quad - b) Andy Warhol\par
\quad - c) Roy Lichtenstein\par

\textbf{Q23} Leonardo da Vinci's "Last Supper" fresco is housed in which building?\par
\quad - a) St Peter's Basilica\par
\quad - b) Santa Maria delle Grazie\par
\quad - c) Basilica di San Marco\par

\textbf{Q24} The Fauvist movement is known for its vivid colour—who pioneered it?\par
\quad - a) Henri Matisse\par
\quad - b) Pablo Picasso\par
\quad - c) Vincent van Gogh\par

\textbf{Q25} Which Indian painting style is noted for bright colours and Hindu mythological themes?\par
\quad - a) Tanjore\par
\quad - b) Madhubani\par
\quad - c) Pahari\par

\textbf{Q26} Vincent van Gogh was not always an artist—which occupation preceded his art career?\par
\quad - a) Teacher\par
\quad - b) Preacher\par
\quad - c) Doctor\par

\textbf{Q27} Mughal paintings are especially known for what primary trait?\par
\quad - a) Use of vibrant colour\par
\quad - b) Depiction of court life\par
\quad - c) Intricate brushwork\par

\textbf{Q28} Who painted "Girl with a Pearl Earring"?\par
\quad - a) Rembrandt\par
\quad - b) Johannes Vermeer\par
\quad - c) Leonardo da Vinci\par

\textbf{Q29} Which art movement aimed to depict the world as it is—eschewing romanticism?\par
\quad - a) Dadaism\par
\quad - b) Realism\par
\quad - c) Surrealism\par

\textbf{Q30} What is the primary subject of "The Starry Night"?\par
\quad - a) Van Gogh's self‑portrait\par
\quad - b) Landscape and scenery\par
\quad - c) His family\par

\textbf{Q31} Which style was pioneered by Jackson Pollock?\par
\quad - a) Abstract Expressionism\par
\quad - b) Cubism\par
\quad - c) Surrealism\par

\textbf{Q32} How did Diego Rivera highlight Mexican values in his art?\par
\quad - a) By painting war scenes\par
\quad - b) By painting daily life\par
\quad - c) By painting portraits\par

\textbf{Q33} Which Indian painting form is traditionally done on cloth?\par
\quad - a) Tanjore\par
\quad - b) Warli\par
\quad - c) Phad\par

\textbf{Q34} Which movement is best known for its focus on motion and movement?\par
\quad - a) Futurism\par
\quad - b) Cubism\par
\quad - c) Dadaism\par

\textbf{Q35} "The Scream" by Edvard Munch belongs to which style?\par
\quad - a) Surrealism\par
\quad - b) Expressionism\par
\quad - c) Cubism\par

\textbf{Q36} Which country is considered the birthplace of Impressionism?\par
\quad - a) Italy\par
\quad - b) France\par
\quad - c) Spain\par

\textbf{Q37} Leonardo da Vinci produced few attributed paintings—why?\par
\quad - a) He always signed "Anonymous"\par
\quad - b) He often abandoned projects mid‑way\par
\quad - c) He couldn't paint at all\par

\textbf{Q38} Which technique allows appreciation of Indian miniature paintings?\par
\quad - a) Fresco\par
\quad - b) Tempera\par
\quad - c) Oil\par

\textbf{Q39} Which Indian folk art uses geometric patterns and shapes?\par
\quad - a) Warli\par
\quad - b) Madhubani\par
\quad - c) Kerala Mural\par

\textbf{Q40} What connects Andy Warhol and Roy Lichtenstein?\par
\quad - a) They inspired one another\par
\quad - b) They pioneered Pop Art\par
\quad - c) They hated each other\par

\textbf{Q41} Known for symbolic use of colour and simplified forms, which artist painted "The Kiss," an Art‑Nouveau masterpiece?\par
\quad - a) Edvard Munch\par
\quad - b) Gustav Klimt\par
\quad - c) Egon Schiele\par

\textbf{Q42} The Hudson River School focused on which scenery type, capturing American grandeur?\par
\quad - a) Cityscapes\par
\quad - b) Landscapes\par
\quad - c) Portraits\par

\textbf{Q43} Bengal School artists Jamini Roy and Zainul Abedin are known for depicting what?\par
\quad - a) Vincent van Gogh\par
\quad - b) Chughtai and Abanindranath\par
\quad - c) Jamini Roy and Zainul Abedin\par

\textbf{Q44} Which ancient painting style is associated with geometric shapes and patterns?\par
\quad - a) Egyptian style\par
\quad - b) Roman style\par
\quad - c) Greek style\par

\textbf{Q45} Dadaism rejected logic and embraced nonsense—which artist epitomised the movement?\par
\quad - a) Marcel Duchamp\par
\quad - b) Monet\par
\quad - c) Raphael\par

\textbf{Q46} Which artist was an Impressionist master?\par
\quad - a) Leonardo da Vinci\par
\quad - b) Monet\par
\quad - c) Michelangelo\par

\textbf{Q47} The style employing bold colours to represent subjects was pioneered by whom?\par
\quad - a) Raphael\par
\quad - b) Da Vinci\par
\quad - c) Matisse\par

\textbf{Q48} Francisco Goya's "Saturn Devouring His Son" is associated with which painting style?\par
\quad - a) Gothic\par
\quad - b) Romanticism\par
\quad - c) Black painting\par

\textbf{Q49} Ancient Byzantine art is best known for which medium?\par
\quad - a) Mosaics\par
\quad - b) Fresco\par
\quad - c) Miniatures\par

\textbf{Q50} Surrealist René Magritte is best known for what?\par
\quad - a) Still‑life\par
\quad - b) Portraits\par
\quad - c) Images challenging viewers' perception of reality\par